### 2013-07-24 paper2.tex
first commit

\documentclass[useAMS,usenatbib]{mn2e}                                  
%
%\def\del#1{{\bf  [deleted text] }} \def\new#1{{\bf #1}} \def\remark#1{{\bf  [remark: #1]}}
%\def\del#1{} \def\new#1{#1} \def\remark#1{}

\def\del#1{{}}
%\def\del#1{{\bf (DELETED TEXT)}}
\def\C#1{{\bf #1}}
%\def\C#1{#1}

%\newcommand{\rmn}{\mathrm}
\newcommand{\CR}{\mathrm{CR}}
\newcommand{\expval}[1]{\left\langle #1 \right\rangle}
\newcommand{\RA}[3]{#1$^{\mathrm{h}}$#2$^{\mathrm{m}}$#3$^{\mathrm{s}}$}
\newcommand{\Dec}[3]{#1$^{\circ}$#2\arcmin#3\arcsec}
\newcommand{\dps}{\displaystyle}
\newcommand{\eps}{\varepsilon}
\newcommand{\dd}{\mathrm{d}}
\newcommand{\vel}{\upsilon}
%
\usepackage{graphicx}
\usepackage{natbib}
%
\usepackage{txfonts}

%\voffset-0.5in

%MNRAS
\title[On the Physics of Radio Halos in Galaxy Clusters]{On the Physics of Radio Halos in Galaxy Clusters: Scaling Relations and Luminosity Functions}
\author[F. Zandanel, C. Pfrommer and F. Prada]{
Fabio Zandanel$^{1,2 *}$, Christoph Pfrommer$^{3 \dagger}$ and Francisco Prada$^{4,5,1 \S}$\\
$^{1}$Instituto de Astrof\'{\i}sica de Andaluc\'{\i}a (CSIC), Glorieta de la Astronom\'{\i}a, E-18080 Granada, Spain\\
$^{2}$now at GRAPPA Institute, University of Amsterdam, Science Park 904, 1098XH Amsterdam, Netherlands\\
$^{3}$Heidelberg Institute for Theoretical Studies, Schloss-Wolfsbrunnenweg 35, D-69118 Heidelberg, Germany\\
$^{4}$Campus of International Excellence UAM+CSIC, Cantoblanco, E-28049 Madrid, Spain\\
$^{5}$Instituto de F\'{\i}sica Te\'orica, (UAM/CSIC), Universidad Aut\'onoma de Madrid, Cantoblanco, E-28049 Madrid, Spain}
\begin{document}

\date{Accepted XXX. Received XXX; in original from XXX}

\pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{2012}

\maketitle

\label{firstpage}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
  The underlying physics of giant and mini radio halos in galaxy clusters is
  still an open question, which becomes more pressing with the growing number of
  detections. Assuming that the radio-emitting electrons are generated in
  hadronic cosmic ray (CR) interactions with protons of the intra-cluster medium
  explains the radio emission in mini halos (Perseus, Ophiuchus). {\bf By contrast,
  the hadronic model either fails to explain the extended emission of giant
  radio halos (Coma at low frequencies) or would require a flat CR profile, 
  realized through CR streaming and diffusion (Coma and A2163 at 1.4~GHz). 
  We suggest that a second, leptonic component could be responsible 
  for the missing flux in giant halos within a new hybrid scenario of which 
  we describe possible observational consequences. We then study in
  detail the hadronic component, including an effective parameterization of CR
  transport, using a cosmological complete mock galaxy cluster catalog built 
  from the MultiDark $N$-body $\Lambda$CDM simulation.} 
  Because of CR transport and the different scalings of the
  X-ray luminosity, $L_{\rmn{X}}$, and the Sunyaev-Zel'dovich flux, $Y$, with
  gas density, our model can simultaneously reproduce the observed bimodality of
  radio-loud and radio-quiet clusters at the same $L_{\rmn{X}}$ as well as the
  unimodal distribution of radio-halo luminosity versus $Y$; thereby suggesting
  a physical solution to this apparent contradiction. {\bf Assuming a plausible fraction
  of radio-loud clusters, fixed at all redshifts, we demonstrate the unique 
  prospects for low-frequency radio surveys (such as the
  LOFAR Tier~1 survey) to detect $\sim600\times\rmn{\emph{loud~fraction}[\%]}/10$ 
  hadronically-generated (giant and mini) radio halos and to probe the underlying 
  physics of radio halos. This shows the potentially of future radio surveys in determining 
  the generation mechanism of halos and the importance of the hadronic component in 
  galaxy clusters, particularly at low masses which are currently unexplored.}
  We make our cosmologically complete multi-frequency mock 
  catalogs for the (non-)thermal cluster emission at different redshifts publicly and freely 
  available on-line through the MultiDark database.
%  The underlying physics of giant and mini radio halos in galaxy clusters is
%  still an open question, which becomes more pressing with the growing number of
%  detections. Assuming that the radio-emitting electrons are generated in
%  hadronic cosmic ray (CR) interactions with protons of the intra-cluster medium
%  explains the radio emission in mini halos (Perseus, Ophiuchus). By contrast,
%  the hadronic model either fails to explain the extended emission of giant
%  radio halos (Coma at low frequencies) or would require a flat CR profile 
%  (Coma and A2163 at 1.4~GHz). Flat CR distributions are only expected to be realized 
%  through CR streaming in {\em relaxed} clusters---in conflict with the observation that
%  radio halos are hosted by merging {\em turbulent} clusters. This motivates us
%  to propose a new hybrid model, where (i) mini halos are primarily of hadronic
%  origin, (ii) giant halos experience a transition from central hadronic
%  emission to peripheral leptonic emission due to Fermi I or II reacceleration
%  of fossil or hadronically produced electrons, and (iii) steep spectrum radio
%  sources are mainly of leptonic origin. {\bf We use a mock galaxy cluster catalog
%  built from the MultiDark $N$-body $\Lambda$CDM simulation that matches 
%  Sunyaev-Zel'dovich and X-ray scaling relations and luminosity function.} 
%  Because of CR streaming and the different scalings of the
%  X-ray luminosity, $L_{\rmn{X}}$, and the Sunyaev-Zel'dovich flux, $Y$, with
%  gas density, our model can simultaneously reproduce the observed bimodality of
%  radio-loud and radio-quiet clusters at the same $L_{\rmn{X}}$ as well as the
%  unimodal distribution of radio-halo luminosity versus $Y$; thereby suggesting
%  a physical solution to this apparent contradiction. For a plausible fraction
%  of 10\% radio-loud clusters, our model matches the NVSS radio-halo luminosity
%  function. Constructing an analytical radio-halo luminosity function, we
%  demonstrate the unique prospects for low-frequency radio surveys (such as the
%  LOFAR Tier 1 survey) to detect $\sim3500$ radio halos back to redshift two and
%  to probe the underlying physics of radio halos. We make our cosmologically 
%  complete multi-frequency mock catalogs for the (non-)thermal cluster emission 
%  at different redshifts publicly and freely available on-line
%  through the MultiDark database.
\end{abstract}

\begin{keywords}
  Galaxies: clusters - Radio continuum - Gamma rays - X-rays: galaxies: clusters
\end{keywords}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:1}

\begingroup
\let\thefootnote\relax\footnotetext{* f.zandanel@uva.nl}
\let\thefootnote\relax\footnotetext{$\dagger$ christoph.pfrommer@h-its.org}
\let\thefootnote\relax\footnotetext{$\S$ fprada@iaa.es}
\endgroup

{\bf The presence of large-scale diffuse radio synchrotron emission in clusters of
galaxies proves the existence of relativistic electrons and magnetic fields
permeating the intra-cluster medium (ICM). Diffuse cluster radio emission can be
separated in two classes: radio halos and radio relics (see, e.g., 
\citealp{2012A&ARv..20...54F}).  Radio \mbox{(mini-)}halos (RHs) are centered 
on clusters and characterized by a regular and unpolarized morphology, resembling 
the morphology of the thermal X-ray emission.}

Two principal models have been proposed to explain RHs.  In the ``hadronic
model'' the radio emitting electrons are produced in hadronic cosmic ray (CR)
proton interactions with protons of the ambient thermal ICM, requiring only a
very modest fraction of (at most) a few percent of CR-to-thermal pressure
(\citealp{1980ApJ...239L..93D,1982AJ.....87.1266V, 1999APh....12..169B,
  2000A&A...362..151D, 2001ApJ...562..233M,2001ApJ...559...59M,
  2003MNRAS.342.1009M,2003A&A...407L..73P, 2004A&A...413...17P,
  2004MNRAS.352...76P, 2007IJMPA..22..681B, 2008MNRAS.385.1211P,
  2008MNRAS.385.1242P, 2009JCAP...09..024K, 2010MNRAS.401...47D,
  2010arXiv1003.0336D, 2010arXiv1003.1133K, 2010arXiv1011.0729K,
  2011A&A...527A..99E}).  CR protons and heavier nuclei, like electrons, can be
accelerated and injected into the ICM by structure formation shocks, active
galactic nuclei (AGN) and galactic winds.  Due to their higher masses with
respect to electrons, CR protons are accelerated more efficiently to
relativistic energies and are expected to show a ratio of the spectral energy
flux of CR protons to electrons above 1 GeV of about 100, similarly to what is
observed in our Galaxy \citep{2002cra..book.....S}. Additionally, CR protons
have a radiative cooling time larger than that of the electrons by the square of
the mass ratio and therefore can accumulate in clusters for cosmological times
\citep{1996SSRv...75..279V}. Indeed, CR electrons suffer more severe energy
losses via synchrotron and inverse Compton emission at particle energies $E
\gtrsim 100$~MeV, and Coulomb losses below that energy range.

In the ``re-acceleration model'', RHs are thought to be the result of
re-acceleration of electrons through interactions with plasma waves during
powerful states of ICM turbulence, as a consequence of a cluster merger
(\citealp{1987A&A...182...21S, 1993ApJ...406..399G, 2002A&A...386..456G,
  2004MNRAS.350.1174B, 2005MNRAS.363.1173B, 2007MNRAS.378..245B,
  2010arXiv1008.0184B, 2009A&A...507..661B, 2012arXiv1211.3337D}). This,
however, requires a sufficiently long-lived CR electron population at energies
around 100~MeV which has to be continuously maintained by re-acceleration at a
rate faster than the cooling processes.  We refer the reader to
\citet{2011A&A...527A..99E} for a discussion on the strengths and weaknesses of
these two models.

RHs can be divided in two classes. Giant radio halos are typically associated
with merging clusters and have large extensions, e.g., the Coma RH has
an extension of about 2~Mpc. Radio mini-halos are associated with relaxed
clusters that harbor a cool core and typically extend over a few hundred
kilo-parsecs, e.g., the Perseus radio mini-halo has an extension of about
0.2~Mpc.  The observed morphological similarities with the thermal X-ray
emission suggests that RHs may be of hadronic origin. In fact, cool-core
clusters (CCCs) are characterized by high thermal X-ray emissivities and ICM
densities that are more peaked in comparison to (merging) non cool-core clusters
(NCCCs) (e.g., \citealp{2008A&A...487..431C}). This distinct difference in the
ICM density structure of CCCs and NCCCs would be reflected in the morphology 
of the two observed classes of RHs.

The RH luminosity seems to be correlated to the thermal X-ray luminosity (e.g.,
\citealp{2009A&A...507..661B,2011A&A...527A..99E}). However, a large fraction
of clusters does not exhibit significant diffuse synchrotron emission at current
sensitivity limits. Instead, stacking subsamples of luminous X-ray clusters
reveals a signal of extended diffuse radio emission that is below
the radio upper limits on individual clusters \citep{2011ApJ...740L..28B}
suggesting that at least a subset of apparently ``radio-quiet'' clusters shows a
low-level diffuse emission. Galaxy clusters with the same thermal X-ray
luminosity show an apparent bimodality with respect to their radio
luminosity. 
%5Either they harbor a RH or they do not have any detectable diffuse
%radio emission \citep{2009A&A...507..661B,2011A&A...527A..99E}. 
This suggests the existence of a switch-on/switch-off mechanism that is able to change the
radio luminosity by more than one order of magnitude.  While such a mechanism
could be easily realized in the framework of the re-acceleration model
\citep{2009A&A...507..661B}, the \emph{classical} hadronic model predicts the
presence of RHs in all clusters. The failure to reproduce the observed cluster
radio-to-X-ray bimodality was one of the main criticisms against the hadronic
model.  Additionally, the classical hadronic model cannot reproduce some
spectral features observed in clusters, such as the total spectral (convex)
curvature claimed in the Coma RH or the spectral steepening observed at
the boundary of some RHs. 
%However, the recent report of spectral flattening with
%frequency of the RH in A2256 \citep{2012A&A...543A..43V} could easily be
%accommodated in the hadronic model, which naturally produces such a concave
%spectrum \citep{2010MNRAS.409..449P}. 
%This raises the interesting question
%whether such a variability among different sources that are generally classified
%as `radio halos' signals the presence of richer underlying physics---a question
%that we will address in this paper.

\cite{2011A&A...527A..99E} tried to asses these problems of the classical hadronic 
model by analyzing CR transport processes within a cluster. While CR advection with 
turbulently driven flows results in centrally enhanced CR profiles, the propagation in 
form of CR streaming and diffusion produces a flattening of CR profiles. Hence, 
different CR transport phenomena may also account for the observed bimodality 
of the radio luminosity in the hadronic model and may also explain the spectral 
features observed in some clusters. {\bf This has been recently confirmed 
by \cite{2013arXiv1303.4746W} that developed a more rigorous treatment. 
In particular, they show that when considering turbulent
damping, CRs can stream at super-Alfvenic velocities, which is crucial
for CR transport to be of relevant magnitude.} 
Note that these phenomena were not considered in earlier analytical works 
(e.g., \citealp{2004A&A...413...17P}) as well as in previous hydrodynamic 
simulations (e.g., \citealp{2001ApJ...562..233M, 
2008MNRAS.385.1211P, 2010MNRAS.409..449P}).
{\bf A satisfactory theory of CR transport in clusters does not exist yet, 
however CR streaming and diffusion may represent an intriguing solution
for the issues of the classical hadronic model.}

Recently, \cite{2012MNRAS.421L.112B} presented the first scaling relations
between RH luminosity and Sunyaev-Zel'dovich (SZ) flux measurements, using the
\emph{Planck} cluster catalogue. While the correlation agrees with previous
scaling measurements based on X-ray data, there is no indication for a bimodal
cluster population dividing clusters into radio-loud and radio-quiet objects at
fixed SZ flux. While the SZ flux correlates tightly with cluster mass, the X-ray
luminosity, $L_\rmn{X}$, exhibits a larger scatter. The CCCs predominantly
populate the high-$L_\rmn{X}$ tail (at any cluster temperature) and make up
approximately half of the radio-quiet objects \citep{2011A&A...527A..99E}. This
suggests that the switch-on/switch-off mechanism may not operate at fixed
$L_\rmn{X}$ but also causes an evolution of that quantity. As the cluster
relaxes after a merger, it cools and forms a denser core. Simultaneously,
$L_\rmn{X}$ is expected to {\em increase} which may simultaneously {\em
  decrease} the radio luminosity owing to the decaying turbulence that is
responsible in maintaining the radio emission in either model (that accounts for
microscopic CR transport). {\bf This has been confirmed by \cite{2013arXiv1307.3049S}
and \cite{2013arXiv1306.4379C}.}

An observational test that is able to disentangle between the hadronic and
re-acceleration models is the gamma-ray emission resulting from neutral pion
decays, a secondary product of the hadronic CR interaction with protons of the
ICM, which is not predicted by the re-acceleration model. Such observational
efforts have been undertaken in the last few years (for space-based cluster
observations in the GeV-band, see \citealt{2003ApJ...588..155R,
  2010JCAP...05..025A,2010ApJ...717L..71A,2012AAS...21920701Z,2012arXiv1207.6749H}; for ground-based
observations in the energy band $\gtrsim100$~GeV, see
\citealt{2006ApJ...644..148P, 2008AIPC.1085..569P,
  2009arXiv0907.0727T,2009A&A...495...27A, 2009arXiv0907.3001D,
  2009arXiv0907.5000G, cangaroo_clusters, 2009ApJ...706L.275A,
  2010ApJ...710..634A, 2011arXiv1111.5544M,2012...VERITAS,2012A&A...545A.103H})
without being able to detect cluster gamma-ray emission. Current gamma-ray 
limits enable us to constrain the average CR-to-thermal pressure to be less than a few
percent, and the maximum CR acceleration efficiency at structure formation shocks 
to be $<50\%$. Alternatively, this may indeed suggest the presence of non-negligible 
CR transport processes into the outer cluster regions. 
%significant constraints on the relative CR pressure contribution. 
%The long observational campaign of the Perseus galaxy cluster
%performed by the Major Atmospheric Gamma-ray Cherenkov (MAGIC) telescopes
%constrains the cluster average CR-to-thermal pressure to be less than a few
%percent \citep{2010ApJ...710..634A,2011arXiv1111.5544M}. Comparing the
%corresponding upper limits to predictions of simulations by
%\cite{2010MNRAS.409..449P} constrains the maximum CR acceleration efficiency at
%structure formation shocks to be $<50\%$.  Alternatively, this may indeed
%suggest the presence of non-negligible CR transport processes into the outer
%cluster regions as suggested by \cite{2011A&A...527A..99E}.  Constraints at the
%same level are confirmed by the \emph{Fermi}-Large Area Telescope (LAT) data on
%the Coma cluster \citep{2011arXiv1105.3240P,2012AAS...21920701Z,
%2012...VERITAS,2012arXiv1207.6749H}. To summarize, gamma-ray observations are 
%not yet sensitive enough to severely challenge hadronic models of RHs.

An important step towards understanding the generating mechanism of RHs could
come from detailed RH population analyses. To date, we know of 53 clusters that
harbor RHs (\citealp{2012A&ARv..20...54F}, for an almost up-to-date list). Only
few X-ray flux-limited studies have been conducted that assess the important
question of the RH frequency in clusters \citep{1999NewA....4..141G,
  VenturiGMRT_2,2013arXiv1306.3102K}. Since the number of RHs in such X-ray flux-limited samples is
small with typically a few RHs, the conclusions on the underlying physical
mechanisms of RHs are not very robust. Fortunately, this is expected to change
thanks to the next-generation of low-frequency radio observatories such as the
Low Frequency Array (LOFAR).\footnote{www.lofar.org} In fact, a deep cluster
survey is part of the LOFAR science key projects and expected to provide a large
number of radio-emitting galaxy clusters up to redshift $z\approx1$
\citep{2012JApA..tmp...34R}. This will hopefully permit
to clearly determine the RH phenomenology with respect to cluster properties
such as the fractions of radio-loud/quiet, non cool-core/cool-core, and
non-merging/merging clusters, and to explore the role of different parameters
like the magnetic field, the CR acceleration efficiency, and CR transport
properties.

{\bf The main scope of this work is to improve the classical hadronic model with
the inclusion of possible CR transport phenomena, trying in this way to solve
its main issues when comparing to observations and to make predictions for
future radio surveys. The outline is as follows. In Section~\ref{sec:2.3}, we 
construct a model for the CR proton distribution in clusters that merges results 
of hydrodynamic cluster simulations and an analytical model for microscopic 
CR transport processes. In Section~\ref{sec:3}, we model observed surface 
brightness profiles of individual RHs within the hadronic scenario and explore the 
allowable parameter space for CRs and magnetic fields. Motivated by immanent 
challenges to explain the extent of giant radio halos within the hadronic model, 
we suggest a new hybrid leptonic/hadronic scenario meant to unify the apparently 
distinct classes of giant radio halos, mini halos, and steep spectrum radio sources in 
Section~\ref{sec:discussion_hadronic}. In Section~\ref{sec:4}, we apply our
extended hadronic model to a cosmologically complete mock galaxy cluster catalog 
built from the MultiDark $N$-body $\Lambda$CDM simulation
in Zandanel, Pfrommer \& Prada (2013; hereafter Paper~I). 
We compare the resulting modeled radio-to-X-ray and radio-to-SZ
scaling relations to current observations and show how they vary for different
choices of our CR and magnetic parametrizations. In Section~\ref{sec:5}, we show
the radio luminosity functions, compare them to current observational
constraints and provide predictions for the hadronically-generated
RHs for the LOFAR cluster survey. Finally, in Section~\ref{sec:6}, we present 
our conclusions.} In this work, the cluster mass
$M_{\Delta}$ and radius $R_{\Delta}$ are defined with respect to a density that
is $\Delta=200$ or $\Delta=500$ times the \emph{critical} density of the
Universe. We adopt density parameters of $\Omega_{\rmn{m}}=0.3$,
$\Omega_{\Lambda}=0.7$ and today's Hubble constant of $H_0 = 100 \times
h_{70}$~km~s$^{-1}$~Mpc$^{-1}$ where $h_{70} = 0.7$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Cosmic Ray Modeling}
\label{sec:2.3}
We assume a power-law for the spectral distribution of CR protons, $f(R,p) \dd
p=C(R) p^{-\alpha} \dd p$, which is the effective one-dimensional momentum
distribution (assuming isotropy in momentum space). {\bf We are interested 
in calculating the radio synchrotron and gamma-ray emission resulting from 
secondaries of hadronic CR interactions with protons of the ICM (see
Appendix~\ref{app:A} and Appendix~\ref{app:C} for the details).}

The spatial CR distribution within a galaxy cluster is governed by an interplay
of CR advection, streaming, and diffusion. The advection of CRs by turbulent gas
motions is dominated by the largest eddy turnover time $\tau_{\rmn{tu}}\sim
L_{\rmn{tu}}/ \vel_{\rmn{tu}}$. Here, $L_{\rmn{tu}}$ denotes the turbulent
injection scale (typically of order the core radius) and $\vel_{\rmn{tu}}$ is
the associated turbulent velocity that approaches the sound speed
$\vel_{\rmn{s}}$ for transsonic turbulence after a cluster merger and relaxes to
small velocities afterwards. As a result of advection into the dense cluster
atmosphere, CRs are adiabatically compressed and experience a stratified
distribution in the cluster potential. The gradient of the CR number density
leads to a net CR streaming motion towards the cluster outskirts. Streaming CRs
excite Alfv{\'e}n waves on which they resonantly scatter
\citep{1969ApJ...156..445K}. This isotropizes the CRs' pitch angles, and thereby
reduces the CR bulk speed. Balancing the growth rate of the CR Alfv{\'e}n wave
instability with the wave damping rate due to non-linear Landau damping yields a
CR streaming speed of order the Alfv{\'e}n speed \citep{2001ApJ...553..198F}.
This increases considerably when balancing it with the turbulent damping rate,
which implies an inverse scaling with the CR number density \citep{2013arXiv1303.4746W}.
Once CR streaming depletes the CR number density, this causes a
run-away process with a rapidly increasing streaming speed that even surpasses
the sound speed because the smaller CR number density drives the CR Alfv{\'e}n
wave instability less efficiently. Hence, the crossing time of streaming CRs
over $L_{\rmn{tu}}$ is $\tau_{\rmn{st}}\sim \chi_B\,L_{\rmn{tu}}/
\vel_{\rmn{st}}$ with the streaming velocity given by $\vel_{\rmn{st}}\sim
\vel_{\rmn{s}}$ and $\chi_B\lesssim 1$ parametrizes the magnetic bending scale.
Magnetic bottlenecks for the macroscopic, diffusive CR transport, are critical
in lowering the microscopic streaming velocity of CR by some finite
factor. Therefore, we can define a turbulent propagation parameter
\begin{equation}
  \label{eq:gamma_tu}
  \gamma_{\rmn{tu}}\equiv\frac{\tau_{\rmn{st}}}{\tau_{\rmn{tu}}}=
  \frac{\chi_B\,\vel_{\rmn{tu}}}{\vel_{\rmn{st}}}
\end{equation}
that indicates the relative importance of advection versus CR streaming as the
dominant CR transport mechanism. After a merger, turbulent advective transport
should dominate yielding $\gamma_{\rmn{tu}}\gg 1$, which results in centrally enhanced
CR profiles. In contrast, in a relaxed cluster, CR streaming should be the
dominant transport mechanism implying $\gamma_{\rmn{tu}}\sim1$ and producing
flat CR profiles (for a detailed discussion of these processes, see
\citealp{2011A&A...527A..99E} and \citealp{2013arXiv1303.4746W}).

We propose here to take the spectral shape of the CR distribution function from
cosmological hydrodynamical simulation of clusters \citep{2010MNRAS.409..449P},
which however did not account for CR transport. {\bf To include the latter, we adapt 
the analytical formalism from \citet{2011A&A...527A..99E}. This yields a model that includes 
the necessary CR transport physics and is able to predict radio and gamma-ray 
emission. Note that this approach is not fully self-consistent and points to
the necessity of future hydrodynamical simulations to include the effect of CR
streaming and diffusion on the CR spectrum.}

\begin{figure*} 
\centering
\includegraphics[width=0.62\textwidth]{figures/CR_profiles_FinalModel.eps}
\includegraphics[width=0.37\textwidth]{figures/CR_profiles_FinalModelvsREX_norm0.1.eps}
\caption{\emph{Left panel.} We show our extended model profiles for the
  normalization of the CR distribution for the NCCC and CCC cases and for
  different values of $\gamma_{\rmn{tu}}$. We fix the CR number for the case of
  $\gamma_{\rmn{tu}}=100$ using equation~(36) of \protect\cite{2011A&A...527A..99E},
  while integrating the cluster volume within $R_{200}$, and require CR number
  conservation during CR streaming. \emph{Right panel.} We compare the
  extended model (adopting $\gamma_{\rmn{tu}}=100$) with the semi-analytical
  advection-only case (adopting our GNFW gas profiles and the outer temperature
  decrease to the simulation-derived model proposed by
  \protect\citealp{2010MNRAS.409..449P}) and with the exact analytical solution as in
  \protect\citet{2011A&A...527A..99E}, but for our GNFW profiles (adopting $\alpha=2.3$
  and $\gamma_{\rmn{tu}}=100$). Here, the CR profiles are normalized at
  $C_{0.1}=C(0.1R_{200})$.}
\label{fig:CRFinalModel}
\end{figure*}

{\bf To construct such a model, we have to generalize the approach proposed by
\citet{2011A&A...527A..99E}, which uses a $\beta$-profile gas parameterizatio, 
in order to account for different kind of ICM gas profiles, such as our generalized 
Navarro-Frank-White (GNFW) profiles derived in Paper~I from X-ray observations.} 
We also have to include the cluster mass-scaling of the
CR normalization obtained from simulations \citep{2010MNRAS.409..449P}. While
details are given in Appendix~\ref{app:B}, we show below the main steps. When
turbulent advection completely dominates the CR transport, the CR normalization
can be written as \citep{2011A&A...527A..99E}
\begin{equation}
C_{\rmn{adv}}(R)=C_{0} \left( \frac{P_{\rmn{th}}(R)}{P_{\rmn{th},0}} \right)^{\frac{\beta_{\rmn{CR}}}{\gamma}} = 
C_{0} \eta(R)^{\beta_{\rmn{CR}}},
\label{eq:Csimple_1}
\end{equation} 
where $P_{\rmn{th}}$ is the thermal pressure, $\beta_{\rmn{CR}}=(\alpha+2)/3$, $\gamma=5/3$, 
and we introduced the advective CR profile $\eta(R)=(P_{\rmn{th}}(R)/P_{\rmn{th},0})^{1/\gamma}$. Solving the continuity
equation for CRs, \citet{2011A&A...527A..99E} derive the CR density profile,
\begin{equation}
\rho_{\rmn{CR}}(R) = \rho_{\rmn{CR},0} \eta(R) \rmn{exp} \left( \frac{R}{R_{*}} \right) \, ,
\label{eg:rhoCR_1}
\end{equation} 
where $R_{*}=\gamma_{\rmn{\rmn{tu}}}R_{\rmn{c}}$ and $R_{\rmn{c}}$ is the characteristic 
radius, of order the core radius, at which the turbulence is supposed to be injected.
Now, we introduce the \emph{semi-analytical} mass-dependent normalization of the
CR profile of \cite{2010MNRAS.409..449P} such that
\begin{equation}
\eta(R) = \left( \frac{C_{\rmn{adv}}(R)}{C_0} \right)^{1/\beta_{\rmn{CR}}} \to
\left( \frac{C_{\rmn{extended}}(R)}{C_0} \right)^{1/\beta_{\rmn{CR}}} \, ,
\label{eq:eta}
\end{equation} 
which effectively redefines $C_{\rmn{adv}}(R)$ by that of our extended model, i.e.,
\begin{equation}
C_{\rmn{extended}}(R) =  \tilde{C}(R)\, \frac{\rho_{\rmn{gas}}(R)}{m_\rmn{p}} \frac{T(R)}{T_0}.
\label{eq:Cf}
\end{equation} 
Here, $\rho_{\rmn{gas}}$ is the ICM gas density and $\tilde{C}(R)$ is the normalization 
CR profile of equation~(22) of \cite{2010MNRAS.409..449P}. We additionally account for the 
temperature decline toward the cluster periphery, $T(R)$, given by the fit to the universal
temperature profile obtained from cosmological hydrodynamical simulations
\citep{2007MNRAS.378..385P,2010MNRAS.409..449P} and deep {\em Chandra} X-ray
observations \citep{2005ApJ...628..655V}. Eventually, the CR profile in our
extended model is $C(R)=C_{0}(\rho_{\rmn{CR}}(R) /
\rho_{\rmn{CR},0})^{\beta_{\rmn{CR}}}$ within $R_{\pm}$ of
equation~(\ref{eq:Rpm}), with $\rho_{\rmn{CR}}$ defined by
equation~(\ref{eg:rhoCR_1}) where $C_{\rmn{extended}}$ enters through our
redefinition of $\eta$, and $C(R) = C(R_{\pm})$ for $R > R_{+}$ and $R < R_{-}$,
respectively.

The last step is to generalize the case of one CR population with a single
spectral index $\alpha$ to include the spectral curvature as suggested by
\cite{2010MNRAS.409..449P}. They model the CR spectrum with three different
power-law CR populations with spectral indices of
$\alpha_{i}=(2.15,2.3,2.55)$. {\bf Our formalism can be easily extended to account
for multiple CR populations by extending the terms with a single $\alpha$ to
sums over the three spectral indices (\citealp{2010MNRAS.409..449P}, see
Appendix~\ref{app:A}). 
%This extension has to be applied to $A_{\nu}$, to the factor $(\epsilon_{\rmn{B}}(R)/
%\epsilon_{B_{\rmn{c}}})^{(\alpha-2)/4}$ of equation~(\ref{eq:jnu}), and to
%equation~(\ref{eq:Csimple_1}). 
%While the modifications are straight forward in
%the first two cases (and are adopted for our extended model,
%Appendix~\ref{app:A}), 
However, introducing a sum over $\alpha_{i}$ in
equation~(\ref{eq:Csimple_1}) would make impossible to solve analytically for
$\eta(R)$ in equation~(\ref{eq:eta}).} For simplicity, we decided to only use
$\alpha = 2.3$ in this last case.\footnote{We checked that the choice of
  $\alpha$ in equation~(\ref{eq:Csimple_1}) has only a minor effect on the
  results. Varying $\alpha$ within $2.15-2.55$ leaves the radial shape and the
  normalization unchanged within $0.5\%$.} For the highly turbulent cases, i.e.,
for $\gamma_{\rmn{tu}}=100$ (1000), we recover the radial shape and
normalization of the semi-analytical model of \cite{2010MNRAS.409..449P} within
$1\%$ ($0.1\%$).

Summarizing, our \emph{extended} model for the CR distribution function, has the
following properties: it accounts for (i) {\bf the X-ray-inferred gas
profiles and cluster-mass scaling of the gas fraction (see Paper~I)}, in addition to the
universal temperature drop in the outskirts of clusters, (ii) a cluster-mass
dependent CR normalization and universal CR spectrum as derived from
cosmological hydrodynamical simulations, (iii) an effective parametrization of
active CR transport processes, including CR streaming and diffusion, which
allows us to explore different turbulent states of the clusters in our mock
cluster catalog.

{\bf In the left two panels of Fig.~\ref{fig:CRFinalModel}, we show our extended CR 
normalization for the GNFW gas profile in the NCCC and CCC cases (see Paper I) 
and for different values of $\gamma_{\rmn{tu}}$.}  
As expected, when CR streaming is the dominant CR
transport mechanism, i.e., for negligible advective turbulent transport or
equivalently, $\gamma_{\rmn{tu}}\sim1$, the spatial CR profiles are flattened
irrespective of the cluster state. While turbulence in NCCCs could be
injected by a merging (sub-)cluster, in the case of CCCs, the interaction of the
AGN jet or radio lobe with the ambient ICM could be the source of turbulence.

In the right panel of Fig.~\ref{fig:CRFinalModel}, we compare our extended model
profile with the semi-analytical advection-only case (adopting our GNFW gas
profiles and the outer temperature decrease to the model proposed by
\citealp{2010MNRAS.409..449P}) and with the exact analytical solution as in
\citet{2011A&A...527A..99E}, but for our GNFW profiles (Appendix~\ref{app:B}
for details).  The profiles are normalized at $0.1 R_{200}$. In the case of
dominant advective CR transport, our extended model compares nicely with the
semi-analytical model derived from cosmological cluster simulations
\citep{2010MNRAS.409..449P}.  The main differences between our extended model (and
the semi-analytical model) on the one side and the analytical solution on the
other side is the inclusion of the simulation-based ``reference'' profile
$\tilde{C}$ for the advection-only case and the universally observed temperature
drop towards the outskirts of clusters. Note that the profiles in our extended
model are generally more centrally peaked in comparison to the analytical GNFW
case, which is due to the enhanced radiative cooling in the
\citet{2010MNRAS.409..449P} simulations that did not account for AGN
feedback. Thanks to the flexible parametrization in our model, this can be
easily counteracted by changing $\gamma_{\rmn{tu}}$ and $ \alpha_{\rmn{B}}$ 
(representing the magnetic field radial decline, see next section), however, at
the expense that these parameters are now degenerate with our assumptions  on the
CR profile in the advection-dominated regime and other possible effects that we
are not considering, such as cluster asphericity.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Radio Surface Brightness Modeling}
\label{sec:3}

In this section, we apply our model to reproduce the emission characteristics of
four well-observed RHs.
%
{\bf We provide the synchrotron emissivity $j_{\nu}$, at frequency $\nu$ and 
per steradian, in Appendix~\ref{app:A}.
% 
The radio surface brightness $S_{\nu}(R_{\perp})$ (in the small-angle approximation) and
luminosity $L_{\nu}$, at a given frequency $\nu$, are given by
\begin{eqnarray}
S_\nu(R_{\perp}) &=& 2 \int_{R_{\perp}}^{\infty} j_{\nu}(R) \frac{R}{\sqrt{R^{2}-R_{\perp}^{2}}} \rmn{d}R, \label{eq:surf} \\
L_{\nu}  &=&  4 \pi \int \dd V j_\nu(R).
\label{eq:lum}
\end{eqnarray}
The flux is given by $F_{\nu}=L_{\nu}/(4\pi D^{2})$ where $D$ is the luminosity
distance to the object. Note that we do not convolve $S_\nu$ with the instrumental
point spread function unless specified.}

For the purpose of this section, we adopt the
measured gas and temperature profiles derived from X-ray observations of each cluster.  
Our extended model includes an overall normalization $g_{\rmn{CR}}$ of the CR
distribution function and the hadronically-induced non-thermal emission 
(Appendix~\ref{app:A}). Note that
this parameter can be interpreted as a functional that depends on the
\emph{maximum CR acceleration efficiency}, $g(\zeta_{\rmn{p,max}})$,
\citep{2010MNRAS.409..449P} but \emph{only} for
$\gamma_{\rmn{tu}}\gtrsim100$.

{\bf We assume a scaling of the magnetic field with gas density that is given by
\begin{equation}
B(R) = B_0\,\left(\frac{\rho_{\rmn{gas}}(R)}{\rho_{\rmn{gas},0}}\right)^{ \alpha_{\rmn{B}}},
\label{eq:B}
\end{equation}
where $B_0$ is the central magnetic field and $\alpha_{\rmn{B}}$ describes the
declining rate of the magnetic field strength toward the cluster outskirts. Such
a parametrization is suggested by cosmological simulations \citep{2008A&A...482L..13D} 
as well as Faraday rotation measurements 
\citep[][and references therein]{2010A&A...513A..30B, 2011A&A...529A..13K}.}

We will additionally study the CR-to-thermal
pressure $X_{\rmn{CR}}=P_{\rmn{CR}}/P_{\rmn{th}}$, where the CR pressure is
given by
\begin{equation}
  \label{eq:PCR}
  P_{\rmn{CR}}=\frac{g_{\rmn{CR}} C m_{\rmn{p}} c^{2}}{6}
  \sum_{i=1}^{3} \Delta_{i} \mathcal{B}_{1/(1+q^2)} \left(
    \frac{\alpha_{i}-1}{2},\frac{3-\alpha_{i}}{2} \right).
\end{equation}
Here, $c$ is the speed of light, $q=0.8$ is the low-momentum cutoff of the CR
distribution, and the normalization factors of the individual CR populations are
given by $\Delta_{i} = (0.767, 0.143, 0.0975)$ \citep[][see also
Appendix~\ref{app:A}]{2010MNRAS.409..449P}.

For our study, we choose the giant radio halos of Coma
\citep{1997A&A...321...55D} and Abell~2163 \citep{2001A&A...373..106F,
  2009A&A...499..679M}, both in merging NCCCs, and the radio mini-halos of
Perseus \citep{1990MNRAS.246..477P} and Ophiuchus \citep{2009A&A...499..371G,
  2009A&A...499..679M}, both in relaxed CCCs. The radio emission of these
clusters is representative of a wide class of RHs.  Additionally, Perseus,
Ophiuchus and Coma are among the most promising clusters for gamma-ray
observations \citep{2010MNRAS.409..449P,2011arXiv1105.3240P}. 
We use X-ray-inferred gas densities $\rho_{\rmn{gas}}$ and temperatures 
for Coma \citep{1992A&A...259L..31B}, for A2163 and Ophiuchus 
\citep{2002ApJ...567..716R}, and for Perseus \citep{2003ApJ...590..225C}. 
In Table~\ref{tab:RadioHalos}, we summarize the main characteristics of these RHs.

To assess the ability of our extended hadronic model to fit the observed surface
brightness profiles, we scan our physically motivated parameter space. {\bf The free 
parameters are the magnetic field ($B_0$, $ \alpha_{\rmn{B}}$), 
$\gamma_{\rmn{tu}}$, and the CR acceleration efficiency.} Generally, the normalization 
of the magnetic profile, $B_0$, and the CR acceleration efficiency function, $g_{\rmn{CR}}$, 
determine the overall normalization of the emission. The radial decline of the magnetic field,
$ \alpha_{\rmn{B}}$, and the turbulent CR propagation parameter, $\gamma_{\rmn{tu}}$, both
determine the shape of the radio profile and, hence, are also degenerate. 
%By scanning the allowed parameter space and asserting Bayesian priors that rely on
%observational constraints and theoretical considerations about likely parameter
%combinations for certain classes (mini halos versus giant halos), we will draw
%conclusions on the applicability of the hadronic model for RHs.  
In Fig.~\ref{fig:SBmodeling}, we show the surface brightness and CR-to-thermal
pressure profiles of each cluster together with the allowed $\gamma_{\rmn{tu}}-\alpha_{B}$ parameter space. 
All these clusters are modeled at 1.4~GHz and within $R_{200}$, unless differently specified.

\begin{table} 
\begin{center}
\caption{Radio-halo and mini-halo characteristics.}
\medskip
%\begin{tabular}{cccccccc}
%\hline
%\phantom{\Big|}
%name & $z$ & $D$ & $\Delta d$ & $L_{1.4~\rmn{GHz},~\rmn{obs}}$ & model parameters & $L_{1.4~\rmn{GHz},~\rmn{model}}$ & references \\
%\phantom{\Big|}
%           &   & [$h_{70}^{-1}$~Mpc] & [$h_{70}^{-1}$~Mpc] & $10^{31}$ [$h_{70}^{-2}$~erg~s$^{-1}$~Hz$^{-1}$] & $\gamma_{\rmn{tu}}$, $\alpha_{\rmn{B}}$ & $10^{31}$ [$h_{70}^{-2}$~erg~s$^{-1}$~Hz$^{-1}$] & \\
%\hline \\[-0.5em]
%Coma           & $0.023$ & $101$ & $2.15$ & $0.72$  & 1, 0.6  & 0.86 &  [1, 2, 3]   \\
%               &         &       &        &                        & 4, 0.3  & 0.90  &  \\
%A2163         & $0.203$ & $962$ & $2.07$ & $15.36$     & 1, 0.3  & 13.43  &  [3, 4]  \\
%\hline \\[-0.5em]
%Perseus        & $0.018$ & $78$   & $0.15$ & $4.40$ & 3, 0.4   & 4.80 &  [3, 5, 6]  \\
%               &         &        &        &                       & 100, 0.3 & 3.97 &  \\
%Ophiuchucs     & $0.028$ & $121$  & $0.41$ & $0.19$       & 5, 0.7   & 0.19  &  [3, 4] \\
%               &         &        &        &                       & 100, 0.3 & 0.23 &   \\[0.5em]
\begin{tabular}{lcrrc}
\hline
\phantom{\Big|}
 cluster & $z$ & $D$~~ & $L_{1.4~\rmn{GHz}}$ & references \\
\hline \\[-0.5em]
Coma           & $0.023$ & $101$ & $0.72$  &  [1]   \\
A2163         & $0.203$ & $962$ & $15.36$  &  [2]  \\
\hline \\[-0.5em]
Perseus        & $0.018$ & $78$   & $4.40$ &  [3]  \\
Ophiuchucs     & $0.028$ & $121$  & $0.19$  &  [2] \\[0.5em]
\hline
\end{tabular}
\label{tab:RadioHalos}
\end{center}
\footnotesize{Note. Top two rows correspond to giant radio halos, while the
  bottom two rows are radio mini-halos.  $D$ is the luminosity distance in units
  of $h_{70}^{-1}$~Mpc and $L_{1.4~\rmn{GHz}}$ is the observed radio luminosity
  at 1.4~GHz in units of $10^{31}$~$h_{70}^{-2}$~erg~s$^{-1}$~Hz$^{-1}$.
  References: [1] \cite{1997A&A...321...55D} [2] \cite{2009A&A...499..679M} [3]
  \cite{1990MNRAS.246..477P}.}
\end{table}

\del{$M_{200}$ and $R_{200}$ are taken from \cite{2002ApJ...567..716R}. }

\begin{figure*}
\centering
%\includegraphics[width=0.75\textwidth]{figures/SB_profiles_ALL.eps}
%
\includegraphics[width=5.5cm,height=5.5cm,keepaspectratio]{figures/SB_Coma.eps}
\includegraphics[width=5.6cm,height=5.6cm,keepaspectratio]{figures/XCR_Coma.eps}
\includegraphics[width=5cm,height=4.6cm]{figures/ProbComa.eps}
%%
\includegraphics[width=5.5cm,height=5.5cm,keepaspectratio]{figures/SB_A2163.eps}
\includegraphics[width=5.6cm,height=5.6cm,keepaspectratio]{figures/XCR_A2163.eps}
\includegraphics[width=5cm,height=4.6cm]{figures/ProbA2163.eps}
%%
\includegraphics[width=5.6cm,height=5.6cm,keepaspectratio]{figures/SB_Perseus.eps}
\includegraphics[width=5.6cm,height=5.6cm,keepaspectratio]{figures/XCR_Perseus.eps}
\includegraphics[width=5cm,height=4.6cm]{figures/ProbPerseus.eps}
%%
\includegraphics[width=5.6cm,height=5.6cm,keepaspectratio]{figures/SB_Ophiuchus.eps}
\includegraphics[width=5.6cm,height=5.6cm,keepaspectratio]{figures/XCR_Ophiuchus.eps}
\includegraphics[width=5cm,height=4.6cm]{figures/ProbOphiuchus.eps}
%
\caption{Surface brightness modeling of the RHs in Coma, Abell~2163, Perseus and
  Ophiuchus. The left and middle panels show the RHs' azimuthally averaged
  surface brightness profiles and the corresponding CR-to-thermal pressure
  profiles $X_{\rmn{CR}}(r)$, respectively. Representative hadronic model
  parameters that fit the data well (solid) are compared to parameter choices
  that will be used in the second part of the paper (dashed, Sects.~\ref{sec:4}
  and \ref{sec:5}), which addresses RH statistics. While radio mini-halos can be
  fit by either set of parameters, for the latter choice of parameters, the
  hadronic model is not able to explain the emission in the outer parts of giant
  radio halos and would need a secondary, leptonic component (see text for
  details). This is exemplified in the lower left panels for Coma and Abell~2163
  that show the fraction of missing surface brightness for these parameter
  choices. In the middle panels, we additionally mark the RHs' radial extension
  by a vertical line. The panels on the right show the reduced-$\chi^2$ values
  of our model fits to the data in the $\gamma_{\rmn{tu}}-\alpha_{B}$ parameter
  space. (For Coma, it refers to the 1.4~GHz case only.)  Regions of parameter
  space with reduced-$\chi^2$ values substantially larger than unity are
  excluded by the data while values much smaller than unity may point to an
  overestimate of the uncertainty intervals. Note that different parameter
  values that yield almost the same surface brightness profile may result in
  very different $X_{\rmn{CR}}$ profiles. In the case of Abell~2163 and
  Ophiuchus, we adopt a $10\%$ uncertainty range instead of the errors reported
  by \citet{2009A&A...499..679M} to account for additional systematic
  uncertainties, e.g., residual point source contamination. For Perseus, we show
  the mini-halo data only for the range that is unaffected by residual point
  sources \citep{1990MNRAS.246..477P} and adopt $10\%$ uncertainty budget.}
\label{fig:SBmodeling}
\end{figure*}

\del{ We adopt a $10\%$ uncertainty range for the inner points of the Coma
  $352$~MHz data.}

\subsection{The Coma radio halo}

The giant radio halo in Coma has a morphology remarkably similar to the extended
X-ray thermal bremsstrahlung emission, although the radio emission declines more
slowly towards the cluster outskirts \citep{1992A&A...259L..31B,
  1997A&A...321...55D}. The morphology is non-spherical, showing an elongation
in the East-West direction.  The full-width half maximum (FWHM) of the radio
beam is $0.156$~deg \citep{1997A&A...321...55D}, almost two orders of magnitude
larger than the X-ray observation of \cite{1992A&A...259L..31B}.\footnote{The
  apparent displacement of the radio and X-ray peak of about $0.05$~deg is well
  within the angular resolution of the radio observation and hence negligible
  for the modeling.}  Thus, we apply a Gaussian smoothing to our theoretical
surface brightness of equation~(\ref{eq:surf}) with $\sigma_{\rmn{smoothing}} =
FWHM_{\rmn{radio}}/2.355$.

We investigate different values for $\alpha_{\rmn{B}}\in [0.3,0.7]$ and
$\gamma_{\rmn{tu}}\in [1,100]$. First, we determine the CR number for
$\gamma_{\rmn{tu}}=100$ using equation~(36) of \cite{2011A&A...527A..99E} while
integrating the cluster volume within $R_{200}$. Then, we require CR number
conservation during CR streaming (for CR energies $E>$~GeV where Coulomb cooling
is negligible for CR protons), which is realized in our model by lowering the
values of $\gamma_{\rmn{tu}}$. Fixing the central magnetic field
$B_{0}=5$~$\mu$G \citep{2010A&A...513A..30B}, we use $g_{\rmn{CR}}$ as
normalization factor to match the radio observations.  The study of the
$\gamma_{\rmn{tu}}-\alpha_{B}$ parameter space shown in
Fig.~\ref{fig:SBmodeling} (top right panel) demonstrates the necessity of low
values of $\gamma_{\rmn{tu}}$ to match the data, i.e., very flat CR profiles. An
example of such a good match to the data is obtained for $\gamma_{\rmn{tu}}=2$
and $\alpha_{\rmn{B}}=0.5$ (top left panel). Values as high as
$\gamma_{\rmn{tu}} \approx 4$ still provide a good fit, however, at the expense
of a shallower decline of the magnetic field profile (smaller $ \alpha_{\rmn{B}}$) as a
function of cluster-centric radius. With such values, we can recover the shape
of the radio surface brightness as well as the total radio luminosity with a
maximal relative deviation of about $25\%$.

The gamma-ray flux (Appendix~\ref{app:C}) within $R_{200}$ for the parameter
combination $\gamma_{\rmn{tu}} = 2$ and $\alpha_{\rmn{B}}=0.5$ and for energies
above 100~MeV (100~GeV) is $F_{\gamma} = 2.4 \times 10^{-9}$ ($8.7 \times
10^{-13}$) cm$^{-2}$~s$^{-1}$. This is below the the gamma-ray limit recently
set with the \emph{Fermi} data of $F_{\gamma, UL} (>100~\rmn{MeV}) \approx 3.2
\times 10^{-9}$~cm$^{-2}$~s$^{-1}$ \citep{2012...VERITAS}.  Note that for
slightly higher values of $\gamma_{\rmn{tu}}$, i.e., a more centrally
concentrated CR distribution, the radio and gamma-ray yield would be increased
(assuming CR number conservation). However, in order to match the observed radio
synchrotron profiles, we have to decrease the CR normalization (parametrized by
$g_{\rmn{CR}}$). This causes the associated gamma-ray flux also to be reduced to
a level that is low enough to easily circumvent the gamma-ray constraints. E.g.,
for the parameter combination $\gamma_{\rmn{tu}} = 3$ and
$\alpha_{\rmn{B}}=0.4$, we obtain $F_{\gamma} (>100~\rmn{MeV}) = 1.3 \times
10^{-9}$~cm$^{-2}$~s$^{-1}$ (and $F_{\gamma} (>100~\rmn{GeV}) = 4.9 \times
10^{-13}$~cm$^{-2}$~s$^{-1}$).  We caution that in principle, CR streaming
should cause the CR spectrum to steepen \citep{2013arXiv1303.4746W}.  
This may then considerably weaken these constraints as a result of the convex spectral 
curvature since the gamma-ray emission probes the high-energy tail of the CR distribution 
that is suppressed in this picture in comparison to the lower-energy protons that the
radio emission is sensitive to \citep[see][for an extended discussion of this
point]{2011arXiv1111.5544M}.

However, such low values of $\gamma_{\rmn{tu}}$ challenge the picture
that only clusters that are characterized by a highly turbulent state can host
giant radio halos. For illustration, in Fig.~\ref{fig:SBmodeling}, we
additionally show the radio surface brightness for $\gamma_{\rmn{tu}} = 60$ and
$\alpha_{\rmn{B}}=0.5$; {\bf the corresponding gamma-ray flux above 100~MeV 
(100~GeV) is $F_{\gamma} = 5.4 \times 10^{-10}$ ($1.9 \times
10^{-13}$) cm$^{-2}$~s$^{-1}$.} 
Clearly, the hadronic model is not able to explain the
emission in the outer halo parts and would need a secondary component to fill in
the `missing' hadronic radio emission. This is exemplified in the lower plot of
the top left panel of Fig.~\ref{fig:SBmodeling}, which shows the fraction of
missing surface brightness as a function of radius and accumulates to a total
missing power of about 35\%.

Recently, \citet{2012arXiv1207.3025B} pointed out problems of the hadronic model
for the limited parameter space $\alpha\gtrsim2.6$, while adopting a much
more extended azimuthally averaged RH profile at 352~MHz
\citep{2011MNRAS.412....2B} than the one used in the present study so far
\citep{1997A&A...321...55D}. The problem of reproducing the spectral steepening
claimed in the Coma RH is somewhat mitigated when considering the negative flux
bowl due to the SZ effect that causes the measured RH spectrum to experience a
sharp cutoff towards high frequencies \citep[][which both use X-ray inferred
pseudo-pressure profiles and assume an accretion shock radius to estimate the
Compton-$y$ parameter of Coma]{2002A&A...396L..17E, 2004A&A...413...17P}. To
overcome this uncertainty, we use the observed SZ decrement of the Coma cluster
by the \citet{2012arXiv1208.3611P}. We obtain the total SZ flux by integrating
the Compton-$y$ profile up to the RH's radial extent at 352~MHz of about
$1.3$~$h_{0.7}^{-1}$~Mpc \citep[][which provide the most sensitive observation
of the Coma RH to date]{2011MNRAS.412....2B}. We show the resulting SZ decrement
in Fig.~\ref{fig:SZ_Coma} together with the Coma RH flux at different
frequencies \citep{2003A&A...397...53T}. An intrinsic power-law radio spectrum,
$(\nu/\nu_{0})^{-\alpha/2}$, exhibits a sharp cutoff at frequencies around 3-5
GHz due to the negative flux contribution of the SZ effect. Hence, we fit the
resulting RH spectrum with different spectral indices, $2.1\lesssim
\alpha\lesssim2.9$. We allow the normalization and $\nu_{0}$ to vary freely and
impose a lower floor to the reported uncertainties of 10\% to account for
possible systematics. The resulting reduced-$\chi^{2}$ values (shown in the
legend of Fig.{\ }\ref{fig:SZ_Coma}) underline the discrepancy between RH flux
measurements at different frequencies---in particular for interferometric
measurements that have to reconstruct a large fraction of the flux due to the
``missing zero spacing'' problem. At $\sim5$~GHz, the SZ decrement is comparable
to the measured RH flux. {\bf Additionally, we want to stress once more that
CR streaming can also cause spectral steepening \citep{2013arXiv1303.4746W}.}  
%This demonstrates that the magnitude of the SZ effect
%is higher than assumed by \cite{2004JKAS...37..493B}, \cite{2004A&A...424..773R}, 
%and \cite{2010MNRAS.401...47D}, while it is lower than the models of 
%\cite{2002A&A...396L..17E} and \cite{2004A&A...413...17P}.

{\bf The much more extended RH profile at 352~MHz represents a serious
challenge for our extended hadronic model. We complement our RH modeling at high
frequencies (1.4 GHz) with modeling of the new data at 352~MHz
\citep{2011MNRAS.412....2B}. To this end, we use a {\em novel} $352$~MHz surface
brightness profile that was corrected for residual point-source contamination by
applying the multi-resolution filtering technique described in
\citet{2002PASP..114..427R} as well as adopting the X-ray center for the RH
profile (Rudnick, priv.{\ }comm.). The resulting profile (shown in blue in
Fig.~\ref{fig:SBmodeling}) declines at a slightly faster rate towards the outskirts
than the profile used by \citet{2012arXiv1207.3025B}. More
importantly, there is considerable azimuthal variation in the halo profile 
(see Fig.{\ }4 of \citealp{2011MNRAS.412....2B} and also our discussion about 
RH asphericity in the next section), which would eventually have to
be modeled through hydrodynamical cluster simulations but which is beyond the
scope of this work.}  
%Interestingly, as shown in Fig.~\ref{fig:SB_Coma}, the 1.4
%GHz profile can be brought into agreement with the low-frequency profile by
%choosing a lower zero level (Rudnick, priv. comm.; see also
%\citealp{2012arXiv1208.3611P}), however at the expense of emerging super-cluster
%emission from the Coma region on scales much more extended than the RH
%\citep{2007ApJ...659..267K}. Conversely, by increasing the zero level of the 352
%MHz data \citep{2011MNRAS.412....2B} reconciles that profile with the narrower
%profile of \citet{1997A&A...321...55D} (Fig.~\ref{fig:SB_Coma}), possibly at the
%expense of an implausibly high zero level, judging from the more sensitive 352
%MHz data (Rudnick, priv.{\ }comm.).  Assuming for a moment that the choices of
%zero level at both frequencies were indeed correct, this would imply a larger
%extent of the RH at lower frequencies. A combination of better data at 1.4 GHz,
%careful cleaning of the emission of tailed radio galaxies, and a full accounting
%of the resulting systematic uncertainties into the total error budget are
%certainly needed to fully clarify the observational situation.
%
\begin{figure} 
\centering
\includegraphics[width=\columnwidth]{figures/SZ_Coma.eps}
\caption{Observed RH fluxes of the Coma cluster as compiled by
  \citet{2003A&A...397...53T}. Intrinsic power-law radio spectra are modified at
  high frequencies by means of the SZ decrement (dotted), which we estimate from
  observations by the \citet{2012arXiv1208.3611P} and integrate within the
  radial extend of the RH at 352 MHz. We fit the data points with SZ-modified
  power-law spectra with different spectral indices $\alpha$ and impose a lower
  floor to the reported uncertainties of 10\% to account for possible
  systematics. The corresponding reduced-$\chi^{2}$ values demonstrate the
  discrepancy between RH flux measurements at different frequencies.}
\label{fig:SZ_Coma}
\end{figure}

%\begin{figure} 
%\centering
%\includegraphics[width=\columnwidth]{figures/SB_Coma_norm_band.eps}
%\caption{Surface brightness profiles of the Coma RH, normalized at 300 kpc.  We
% show a 352 MHz profile that was corrected for residual point-source
%  contamination by applying the multi-resolution filtering technique as well as
%  adopting the X-ray center for the RH profile (blue, Rudnick,
%  priv. comm.). This profile declines at a slightly faster rate towards the
%  outskirts than the profile used by \citet[][black
%  squares]{2012arXiv1207.3025B}. Increasing the zero level of the (more
%  sensitive) 352 MHz data (blue open squares) to the level of 1.4 GHz halo data
%  \citep[red filled circles,][]{1997A&A...321...55D} brings those data into
%  agreement. Alternatively, lowering the zero level of the 1.4 GHz data (red
%  open circles, Rudnick, priv. comm.) allows to match the much larger radial
%  extend of the low-frequency data. Those systematic uncertainties need to be
%  carefully addressed in future observations and accounted for in the error
%  budget that currently only account for statistical uncertainties (grey shaded
%  band, \citealp{2012arXiv1207.3025B}).}
%\label{fig:SB_Coma}
%\end{figure}

As shown by the two model realizations in Fig.~\ref{fig:SBmodeling}, the
(extended) hadronic model cannot account for the total emission at $352$~MHz for
any value in the ($\gamma_{\rmn{tu}}$, $\alpha_{\rmn{B}}$) parameter space; in
agreement with the findings of \citet{2012arXiv1207.3025B}. At the same time,
our analysis at 1.4~GHz confirms the result by \citet{2012...VERITAS} who also
conclude that the hadronic model for the Coma RH is a viable explanation for
magnetic field estimates inferred by Faraday rotation measure studies
\citep{2010A&A...513A..30B} and is not challenged by {\em Fermi} upper limits on
the gamma-ray emission. However, this model agreement is bought at the expense
of flat CR profiles (i.e., {\em low} $\gamma_{\rmn{tu}}$ values) that are
contrary to the expectation of turbulent clusters to host giant radio halos
(i.e., {\em high} $\gamma_{\rmn{tu}}$ values) as proposed by
\citet{2011A&A...527A..99E}. {\bf Note that \cite{2013arXiv1303.4746W} 
arrive at a different conclusion finding that the increase of turbulence promotes 
outward streaming more than inward advection, therefore allowing flat CR 
distributions in turbulent clusters. However, this does not help in, e.g.,
the case of the 352~MHz data, where, as discussed above, not even a
flat CR profile is enough to explain the observed emission within the
hadronic scenario.} These finding hint at the necessity of a second,
leptonic component (within the general framework of the hadronic model) that
fills in the patchier emission in the peripheral, low-surface brightness regions
of the halo, in particular at low frequencies \cite[see Fig.~3
of][]{2011MNRAS.412....2B}. We will return to this point in
Section~\ref{sec:discussion_hadronic}.

\subsection{The radio halo in Abell~2163}

The morphology of the giant radio halo in Abell~2163 is also closely correlated
to the cluster's thermal X-ray structure. As in Coma, the radio emission declines
towards the cluster outskirts at a slower rate in comparison to the thermal
X-ray emission \citep{2001A&A...373..106F}. The morphological appearance is
non-spherical, with an elongation in the East-West direction. We use the surface
brightness map provided by \citet{2009A&A...499..679M} for which the synthesized
radio beam can be approximated by a circular Gaussian with
$FWHM_{\rmn{radio}}=62\arcsec$.  Again, $FWHM_{\rmn{radio}}$ is larger than the
resolution of the \emph{ROSAT} observation and the corresponding gas density
profile. Converted to physical scale, $\sigma_{\rmn{smoothing}}$ is of the order
of that in Coma because of the larger distance of Abell~2163. Hence, we also apply
Gaussian smoothing.

We follow the same procedure as in Coma, and adopt a central magnetic field
strength of $B_{0}=5~\mu$G. Similar to the case of Coma (in fact even more
extremely) only very low values of $\gamma_{\rmn{tu}}$ provide a good match to
the data.  In Fig.~\ref{fig:SBmodeling}, we show the case of
$\gamma_{\rmn{tu}}=1$ and $ \alpha_{\rmn{B}}=0.3$, i.e., the flattest possible surface
brightness. With this choice of parameters, we recover the emission shape and
the total luminosity within about $15\%$.  The corresponding gamma-ray flux
within $R_{200}$ is $F_{\gamma} (>100~\rmn{MeV}) = 4.2
\times10^{-10}$~cm$^{-2}$~s$^{-1}$, about two orders of magnitude lower than the
upper limit obtained by \emph{Fermi}-LAT \citep{2010ApJ...717L..71A}, and
$F_{\gamma} (>100~\rmn{GeV}) =1.5 \times10^{-13}$~cm$^{-2}$~s$^{-1}$.

%As for Coma, such low values of $\gamma_{\rmn{tu}}$ appear to be in conflict
%with our understanding of giant radio halos that are expected to be
%turbulent. 
As for Coma, in Fig.~\ref{fig:SBmodeling}, we show the model surface brightness
for the parameter combination $\gamma_{\rmn{tu}} = 60$ and
$\alpha_{\rmn{B}}=0.5$. {\bf The corresponding gamma-ray flux above 100~MeV 
(100~GeV) is $F_{\gamma} = 5.9 \times 10^{-11}$ ($2.2 \times
10^{-14}$) cm$^{-2}$~s$^{-1}$.} The lower panel shows the fraction
of missing surface brightness of our model to explain the data as a function of
radius. That fraction accumulates to a total missing power of about 80\% for the
giant radio halo.

\subsection{The Perseus radio mini-halo}

The diffuse radio emission in Perseus is the best known example of a radio
mini-halo \citep{1990MNRAS.246..477P}\footnote{We make use of the
  \citet{1990MNRAS.246..477P} data instead of \citet{Sijbring1993} as the latter
  may be affected by residual point-source contamination.}  and Perseus itself
is among the best studied clusters in X-rays
(e.g.,~\citealp{2003ApJ...590..225C,2006MNRAS.366..417F,2011arXiv1105.5025F}). Also
the Perseus radio morphology resembles that in the X-rays. We proceed as before,
but now adopt a higher central magnetic field strength of
$B_{0}=10$~$\mu$G. Such a larger $B_0$ is expected in a CCC with its higher
central gas density, implying a larger adiabatic compression factor of the
magnetic field during the condensation of the cool core
(\citealp{2010ApJ...710..634A,2011arXiv1111.5544M} for a discussion on the
Perseus magnetic field).

Our parameter space study of $\gamma_{\rmn{tu}}$ and $\alpha_{\rmn{B}}$ favors
low $\gamma_{\rmn{tu}}$ values---in accordance with our expectation for
mini-halos. However, a large region of that parameter space, up to
$\gamma_{\rmn{tu}} = 100$, can equally well fit the data. The coloring of the
goodness of fit (reduced $\chi^2$) in the $\gamma_{\rmn{tu}}-\alpha_{\rmn{B}}$
plane shows the anti-correlation of $\gamma_{\rmn{tu}}$ and $\alpha_{\rmn{B}}$:
large $\gamma_{\rmn{tu}}$ values (peaked CR profiles) and low $\alpha_{\rmn{B}}$
values (flat magnetic profiles) combine to match the observed surface brightness
profile and vice versa.

In Fig.~\ref{fig:SBmodeling}, we show the two parameter combinations
($\gamma_{\rmn{tu}}=3$, $\alpha_{\rmn{B}}=0.4$) and ($\gamma_{\rmn{tu}}=100$,
$\alpha_{\rmn{B}}=0.3$). Both model realizations nicely recover the surface
brightness profile and the total luminosity within $10\%$.  The gamma-ray flux
within $R_{200}$ for the $\gamma_{\rmn{tu}}=3$ case and for energies above
100~MeV (100~GeV) is $F_{\gamma} = 1.4 \times 10^{-8}$ ($5.1 \times 10^{-12}$)
cm$^{-2}$~s$^{-1}$. Adopting $\gamma_{\rmn{tu}}=100$ and $ \alpha_{\rmn{B}}=0.3$, the
corresponding gamma-ray flux above 100~MeV (100~GeV) is $F_{\gamma} = 4.9 \times
10^{-9}$ ($1.8 \times 10^{-12}$) cm$^{-2}$~s$^{-1}$. Note that the gamma-ray
flux above 100~MeV of the central galaxy NGC~1275 as measured by \emph{Fermi} is
$2 \times 10^{-7}$~cm$^{-2}$~s$^{-1}$ \citep{2009arXiv0904.1904T}, well above
our model predictions due to hadronically produced diffuse gamma-ray emission
that is expected to mostly glow from the core region of the cluster.

We can compare these predictions with the upper limit above 1~TeV, and for a
region within $0.15$~deg around the cluster center, recently obtained by
\cite{2011arXiv1111.5544M}. For $\gamma_{\rmn{tu}}=3$ ($\gamma_{\rmn{tu}}=100$),
we obtain a flux of $F_{\gamma}(>1~\rmn{TeV},<0.15~\rmn{deg}) = 7.3 \times
10^{-14}$ ($5.5 \times 10^{-14}$) cm$^{-2}$~s$^{-1}$, which is well below the
upper limit of the MAGIC collaboration,
$F_{\gamma,\rmn{UL}}(>1~\rmn{TeV},<0.15~\rmn{deg}) \approx 1.4 \times
10^{-13}$~cm$^{-2}$~s$^{-1}$. Note also that, in the case of $\gamma_{\rmn{tu}}
= 100$, we obtain a maximum CR acceleration efficiency multiplier of
$g(\zeta_{\rmn{p,max}})=0.52$, about half of the value adopted by
\cite{2010MNRAS.409..449P}. Note that adopting $g(\zeta_{\rmn{p,max}})=1$
results in slightly smaller gamma-ray luminosities in comparison to those
predicted by \cite{2010MNRAS.409..449P} and \cite{2011arXiv1105.3240P} because
we additionally account for the central temperature dip and as well as the
decrease towards larger radii.

\subsection{The Ophiuchus radio mini-halo}

The Ophiuchus cluster has been widely studied both in radio and X-rays in the
last few years because of the claimed presence of a non-thermal hard X-ray tail
\citep{2008A&A...479...27E,2008PASJ...60.1133F,2009A&A...499..371G,
  2009A&A...499..679M,2009MNRAS.396.2237P,2009A&A...508.1161N,2010A&A...514A..76M,
  2010MNRAS.405.1624M}.  It was classified as a merging cluster by
\cite{2001PASJ...53..605W}, but more recently \cite{2008PASJ...60.1133F} did not
find any evidence of merging and, on the contrary, classified it as one of the
hottest clusters with a cool-core (see also \citealp{2010MNRAS.405.1624M}).  To
simplify modeling, we neglect the small central temperature dip for radii
$r<30\,h_{70}^{-1}$~kpc and adopt a constant central temperature (due to its
small size, the cool core region has no influence on the resulting radio surface
brightness).  The radio mini-halo morphology displays similarities with the
thermal X-ray emission. For our modeling we use the surface brightness profile
provided by \cite{2009A&A...499..679M}.

We proceed as before, adopting a central magnetic field value of
$B_{0}=10$~$\mu$G. Similarly to Perseus, low $\gamma_{\rmn{tu}}$ values are
favored, as expected for mini-halos. However, large regions of the parameter
space provide nice fits to the data.  In Fig.~\ref{fig:SBmodeling}, we show the
two parameter combinations ($\gamma_{\rmn{tu}}=3$, $ \alpha_{\rmn{B}}=0.4$) and
($\gamma_{\rmn{tu}}=100$, $ \alpha_{\rmn{B}}=0.3$).  For those, we recover the surface
brightness profile and the total luminosity within $20\%$. The gamma-ray flux
within $R_{200}$ for the $\gamma_{\rmn{tu}}=3$ case and for energies above
100~MeV (100~GeV) is $F_{\gamma} = 1.3 \times 10^{-10}$ ($4.9 \times 10^{-14}$)
cm$^{-2}$~s$^{-1}$. Adopting $\gamma_{\rmn{tu}}=100$ and $ \alpha_{\rmn{B}}=0.3$, the
corresponding gamma-ray flux above 100~MeV (100~GeV) is $F_{\gamma} = 8.3 \times
10^{-11}$ ($3.1 \times 10^{-14}$) cm$^{-2}$~s$^{-1}$. The gamma-ray flux is, in
both cases, about two orders of magnitude lower than the upper limit obtained by
\emph{Fermi}-LAT \citep{2010ApJ...717L..71A}. Note also that in the case of
$\gamma_{\rmn{tu}} = 100$ we obtain a maximum CR acceleration efficiency
multiplier of $g(\zeta_{\rmn{p,max}})=0.014$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{Possible biases in the modeling of individual radio halos}
%\subsection{Discussion}
\section{Discussion: an hybrid scenario for Giant and Mini Radio Halos?}
\label{sec:discussion_hadronic}

In order to cleanly assess the possibility of the hadronic model to alone
explain the RH data, we only considered the hadronically-induced radio 
emission component in the preceding section. Hence, by construction, we 
neglected other (leptonic) emission components, such as re-accelerated electrons. 
{\bf Possible biases that may affect our previous conclusions are the following.}

%\begin{enumerate} 
%\item 
(i) Merging clusters are not spherically symmetric as can be seen in Coma and
  Abell~2163, requiring inherently non-spherical modelling. In order to
  reproduce the more extended radio emission relative to the thermal X-ray
  emission, the non-thermal clumping factor, $C_{\rmn{non-th}}$, needs to be
  larger than its thermal analogue, $C_{\rmn{th}}$, in concentric spherical
  shells, where we defined those statistics by
  \begin{eqnarray}
    \label{eq:clumping}
    C_{\rmn{non-th}} &=&
    \expval{\rho_\rmn{gas} C}/\expval{\sqrt{\rho_\rmn{gas} C}}^2,\\
    C_{\rmn{th}} &=& 
    \expval{\rho_\rmn{gas}^2}/\expval{\rho_\rmn{gas}}^2.
  \end{eqnarray}
  This manifests itself, e.g., in the large-scale morphology of the radio
  surface brightness emission, which is more elongated than its counterpart in
  thermal X-rays, but also on scales smaller than the radio beam. In our
  phenomenological modeling, we allow for those deviations by means of the
  parameters $\gamma_{\rmn{tu}}$ and $ \alpha_{\rmn{B}}$ for the CRs and magnetic fields,
  respectively. 
  %While this approach is well suited to describe large-scale
  %anisotropies, it may be inadequate to model small-scale inhomogeneities such
  %as CR trapping in magnetic mirrors through the second adiabatic invariant and
  %needs to be carefully quantified in future work.

%\item 
(ii) Adopting the simulation-derived $\tilde{C}$ profile
  \citep{2010MNRAS.409..449P} for our extended model may have biased the inner
  slope of the CR density profile to become too steep due to the overcooling
  problem of purely radiative simulations. This produces cluster cores that are
  too dense (in comparison to observations), which also should overestimate the
  rate of adiabatic compression that is experienced by the CR population during
  the formation of the cooling core. Hence, the resulting values of
  $\gamma_{\rmn{tu}}$ are then biased low in comparison to a potentially
  shallower slope of the inner CR profile. To quantify the last point, we try to
  reproduce the Coma surface brightness at 1.4 GHz using a model without
  $\tilde{C}$. We find that values as high as $\gamma_{\rmn{tu}} \approx 8$ can
  be accommodated. However, $\gamma_{\rmn{tu}}=1$ still represents the best
  match to the data, demonstrating that the problem can be weakened but not
  circumvented even in this case of a cored CR profile.

%\item 
(iii) Considering the case of advection-dominated CR transport
  ($\gamma_{\rmn{tu}}\gtrsim100$), which only allows for a good match to the
  mini-halo data of Perseus and Ophiuchus, the $g_{\rmn{CR}}$ parameter can be
  interpreted as the maximum CR acceleration efficiency used in
  \cite{2010MNRAS.409..449P}. If the cluster CR population is mainly accelerated
  in cosmological structure formation shocks, then this value should depend on
  the mass accretion history and should be approximately universal, i.e.,
  similar for all clusters. We find $g_{\rmn{CR, Perseus}} = 0.52$ and
  $g_{\rmn{CR, Ophiuchus}} = 0.014$, because we fixed $B_{0}=10$~$\mu$G in both
  cases and used $g_{\rmn{CR}}$ as normalization. This discrepancy can be
  resolved by increasing/lowering the central magnetic field in
  Perseus/Ophiuchus to $B_{0,\rmn{Perseus}}\approx20$~$\mu$G and
  $B_{0,\rmn{Ophiuchus}}\approx1$~$\mu$G. We note, however, that without the
  guidance of cosmological cluster simulations that include CR transport, the
  data does not yet constrain $\gamma_{\rmn{tu}}$.
%\end{enumerate}

The small cluster sample analysed here is only meant to serve as a proof
of concept and to show the viability of matching observed representative 
RH data with our extended hadronic model. {\bf Despite the available
observational input on the magnetic field in clusters ($B_0$, $ \alpha_{\rmn{B}}$), 
the parameter space that the physics modeled here demands is quite large
encompassing also $\gamma_{\rmn{tu}}$ and the CR acceleration efficiency
function. Particularly, a large region of the ($\gamma_{\rmn{tu}}$,
$\alpha_{\rmn{B}}$) parameter space is available for the analyzed radio
mini-halos (note also that the parameters $\gamma_{\rmn{tu}}$ and
$\alpha_{\rmn{B}}$ are degenerate). Future work on all known RHs may 
provide better insight.}
% 
%This is in especially
%true because of the comparably large parameter space that the physics modeled
%here demands and which encompasses our parametrization of the magnetic field
%($B_0$, $ \alpha_{\rmn{B}}$), $\gamma_{\rmn{tu}}$, and the CR acceleration efficiency
%function. Particularly, a large region of the ($\gamma_{\rmn{tu}}$,
%$\alpha_{\rmn{B}}$) parameter space is available for the analyzed radio
%mini-halos (note also that the parameters $\gamma_{\rmn{tu}}$ and
%$\alpha_{\rmn{B}}$ are degenerate). Future work on all known RHs may provide
%better insight, but is beyond the scope of this work.
%
However, it seems unlikely that the biases discussed above severely affect our findings
that the extended hadronic model successfully reproduces the main morphological
characteristics of radio mini-halos with a wide range of possible values for
$\gamma_{\rmn{tu}}$ and without violating gamma-ray constraints. In contrast, it
appears to fail in the outskirts of the Coma RH at low frequencies and
require a flat CR distribution both in Coma and in A2163 at 1.4~GHz. {\bf This motivates 
us to consider a modification of this purely hadronic model in explaining RHs.} 
%which 
%we will then scrutinize statistically in the following Sections, namely by investigating the
%radio-to-X-ray and radio-to-SZ scaling relations as well as RH
%luminosity functions.}

%\section{A Model for Giant and Mini Radio Halos}
%\label{sec:discussion_hadronic}

\subsection{Hybrid hadronic-leptonic model}

{\bf Within the hadronic scenario, there emerges a plausible physical solution to
this observational challenge. We suggest that the rich phenomenology of RHs may be a
consequence of two different radio emission components---one of which is induced
by hadronic interactions and the other is of leptonic origin. 
%While we leave the origin of the leptonic component unspecified, 
There are a number of plausible processes for the latter. 
These includes turbulent reacceleration of primary or secondary (hadronic)
electrons \citep{2010arXiv1008.0184B} or reacceleration of fossil electrons by
means of diffusive shock acceleration \citep{kang11,kang12,pinzke13}.
%The fossil electron population may stem from the time-integrated and successively
%cooled population of directly injected electrons at strong structure formation
%shocks trough the Lagrangian history. Alternatively, a seed population of
%relativistic electrons could be provided by the time-integrated action of AGN
%feedback or by supernova-driven galactic winds. 
Depending on relative strength of the different components, this scenario would imply 
various halo phenomena:}
\begin{enumerate}
\item A dominating hadronic component  manifests in form of radio mini-halos in
  CCCs \citep{2004A&A...413...17P}.
\item When the leptonic component dominates, we should have steep spectrum halo
  sources \citep[such as A520,][]{2008Natur.455..944B}, some of which could be
  produced by giant radio relic sources projected onto the main cluster
  \citep{2012arXiv1211.3122S}.
\item The case of both components significantly contributing to the diffuse
  radio emission results in giant radio halos, with the hadronic component
  dominating in the center and the leptonic emission taking over in the outer
  parts. The peripheral regions of merging clusters experience an especially
  high level of kinetic pressure contribution \citep{2009ApJ...705.1129L,
    2012ApJ...758...74B} that manifests in form of subsonic turbulence (as
  suggested observationally by \citealp{2004A&A...426..387S} or theoretically by
  \citealp{2006MNRAS.366.1437S,2005MNRAS.364..753D, 2008Sci...320..909R}) and a
  complex network of shocks \citep{2003ApJ...593..599R, 2006MNRAS.367..113P,
    2008MNRAS.385.1211P, 2008ApJ...689.1063S, 2009MNRAS.395.1333V}. Depending on
  the merger geometry and dynamical stage, as well as the electron acceleration
  efficiencies at these non-equilibrium processes and realized CR streaming
  speeds, we would expect the development of a (fuzzy) transition region between
  hadronic and leptonic component. This generalizes the simulation-inspired
  model by \cite{2008MNRAS.385.1211P} who propose that primary electron
  substantially contribute to the peripheral RH emission.
\end{enumerate}

{\bf A detailed implementation of this hybrid scenario would depend very much
on the precise characterization of a given cluster. This goes beyond the scope of the 
present work which is mainly to explore the possible observational consequences of the 
hadronic component, through our extended model, for future radio surveys. Nevertheless, 
we sketch possible observational implications of an hybrid hadronic-leptonic scenario in the 
following subsection.}

%\subsection{What are the observational implications of this picture?}
\subsection{Possible observational implications}

\subsubsection{Spectral and morphological variability}
  In mini-halos and in the
  centers of giant halos, where the hadronic component dominates in our picture,
  we would naively expect at most modest spectral variations. This is because
  these regions average over sufficiently many fluid elements that each
  experienced its characteristic shock history during the cluster assembly, but
  which produces a CR population that has on average a nearly universal spectrum
  \citep{2010MNRAS.409..449P}. However, CR streaming and diffusive transport may 
  cause a possible spectral steepening in the cluster core region because more 
  energetic CRs diffuse/stream faster. This would
  then imply spatial variations of the CR spectral index and, hence, spatially
  varying radio emission throughout the cluster (core region) when taking the CR
  advection effects into account, which would mix regions of different CR
  spectral properties. In regions where the leptonic component dominates (such
  as the outer regions of giant halos or steep spectrum halo sources), we expect
  substantial spectral and morphological variations in the radio maps. This is
  because of the intermittency of the acceleration process (acceleration at
  discrete weak shocks or turbulent acceleration), the expected distribution of
  Mach numbers or CR momentum diffusion coefficient, respectively, and the
  comparably short electron cooling time ($\sim100$~Myr). Interestingly, this
  compares well with the large azimuthal scatter of different sector profiles of
  the Coma halo, Fig.~4 of \cite{2011MNRAS.412....2B}, and fronts (primarily
  towards the West) in their high-resolution surface brightness map, which may
  indicate the transition from the hadronic to the leptonic emission
  component. In particular, the relative inefficiency of shock acceleration at
  weak shocks or turbulent acceleration generates steeper radio spectra in the
  leptonically dominated regions. Hence, this would naturally imply a radial
  spectral steepening and cause substantial morphological and spectral variation
  in the outer regions of giant halos. The increasing fraction of the leptonic
  component towards lower frequencies may then imply a larger halo size
  with decreasing observational frequency.

\subsubsection{Halo switch-on/-off mechanism and the radio-X-ray bimodality.}
  Clearly, a cluster merger injects turbulence and shocks that could both
  accelerate fossil electrons and switch the leptonic component on. On the other
  hand, CR advection produces centrally enhanced CR profiles because of adiabatic
  compression of CRs for radial eddies. The energetization and transport of
  CRs to the central halo regions implies a lightening up of the hadronic
  emission component. For the leptonic component,
  the halo switch off is faster or comparable to the dynamical time scale,
  $t_{\rm dyn} \sim t_{\rm H}/\sqrt{\Delta} \sim 1 \,\rmn{Gyr}
  \Delta_{100}^{-1/2}$, where $t_{\rm H}=10$~Gyr,
  $\Delta_{100}=\rho/(100\bar{\rho})$. In case of diffusive shock acceleration
  of fossil electrons, the radio emission will be shut off within a CR electron
  cooling time ($t_\rmn{cool}\sim100$~Myr) if the acceleration source ceases,
  i.e., when shocks have dissipated all the energy. In the case of the turbulent
  re-acceleration model, the turbulence decays on a few eddy turnover time
  scales on the injection scale which should take only somewhat longer. The
  hadronic emission component is also expected to decrease substantially once
  turbulent pumping of CRs ceases and CRs are set free to stream, which results
  in a net CR flux towards the external cluster regions. The accompanying
  flattening of the CR profile implies a lowering of the hadronic radio emission
  because the CRs see a smaller target density in the outer parts. 
  {\bf Additionally, \cite{2013arXiv1303.4746W} opened the possibility
  to substantially decrease the radio flux even in merging clusters as
  they found that turbulence seems to promote outward streaming 
  more than inward advection.} This should
  lead naturally to a bimodality of radio synchrotron emissivities due to
  hadronic and leptonic halo components.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*} 
\centering
\includegraphics[width=0.49\textwidth]{figures/PL_relation_testing_gimp.eps}
\includegraphics[width=0.49\textwidth]{figures/PSZ_relation_testing_gimp.eps}
\caption{Radio-to-X-ray and radio-to-SZ scaling relations as predicted by our
  extended CR model. In the left panel, we show how the
  $L_{1.4~\rmn{GHz}}-L_{\rmn{X,bol}}$ relation varies upon changing different
  parameters. In the right panel, we show the same, but for the
  $L_{1.4~\rmn{GHz}}-Y_{\rmn{SZ},500}$ relation. Note that in each plot there
  are two separated populations for each model realization, shown with the same
  color. The upper sets of points correspond to the CCC population while the
  lower sets correspond to NCCCs. The plot labels indicate those parameters
  which are kept fixed. We fix the $g_{\rmn{CR}}$-normalization parameter to 0.5
  for all cases. See main text for details.}
\label{fig:SR}
\end{figure*}

\section{Scaling Relations}
\label{sec:4}
As introduced in Section~\ref{sec:1}, there exist an apparent bimodality between
the radio and X-ray cluster emission. Clusters with a given X-ray luminosity can
either host RHs or show an absence of diffuse radio emission (e.g.,
\citealp{2009A&A...507..661B,2011A&A...527A..99E}). More recently, a study of
the radio-to-SZ scaling relation revealed the absence of a strong bimodality
dividing the cluster population into radio-loud and radio-quiet clusters
\citep{2012MNRAS.421L.112B,2013arXiv1306.4379C,2013arXiv1307.3049S}. 
Since $Y_{\rmn{SZ}}$ correlates more tightly with
cluster mass than $L_{\rmn{X}}$, this may indicate that the larger scatter of
$L_{\rmn{X}}$ correlates with the scatter of the radio luminosity in such a way
that it produces a bimodality; but as a result of a second (hidden parameter)
rather than the fundamental cluster parameter---its mass. In this section, we 
investigate these two scaling relations in the framework of our extended 
hadronic scenario.

{\bf In the following we apply our model to the complete
cosmological mock cluster catalog build from the MultiDark $N$-body 
simulation in our Paper~I. For each object in the sample, we mainly use
the information on its mass, radius and phenomenologically assigned 
ICM gas density to calculate the radio (and gamma-ray) emission.}

\subsection{Exploring the parameter space of scaling relations}

In Fig.~\ref{fig:SR}, we show the general scaling relations of our extended CR
model of Section~\ref{sec:2.3} applied to the MultiDark sample. We show how both
the radio-to-X-ray and the radio-to-SZ scaling relations differ upon varying the
parameters $\gamma_{\rmn{tu}}$, $B_{0}$, $\alpha_{\rmn{B}}$ and redshift. We fix
the CR-normalization parameter $g_{\rmn{CR}}$ to 0.5 in all cases, ensuring an
average CR-to-thermal pressure of $2\%$ ($0.05\%$) within $R_{500}$
($R_{500}/2$) {\bf as suggested by current gamma-ray limits}. 
Here, the radio luminosity is calculated at $1.4$~GHz within
$R_{500}.$\footnote{The mean (median) difference between calculating $L_{\nu}$
  within $R_{200}$ or $R_{500}$ is 5.3\% (5.6\%).}  In our CR model, we fix the
CR number for $\gamma_{\rmn{tu}}=100$ using equation~(36) of
\cite{2011A&A...527A..99E}, integrating up to $R_{500}$. To compute the radio
luminosity for different values of $\gamma_{\rmn{tu}}$, we employ CR number
conservation (for CR energies $E>$~GeV where Coulomb cooling is negligible for CR
protons).

In each panel in Fig.~\ref{fig:SR} there are two separated populations for
each model realization (i.e., for a given set of parameters). Each upper set of
points corresponds to the CCC population while the lower set corresponds to
NCCCs, respectively. In our model, the radio and X-ray emissivities scale with
the square of the gas density so that $L_{1.4~\rmn{GHz}}$ and $L_{\rmn{X,bol}}$
are significantly higher for CCCs in comparison to NCCCs. In contrast,
$Y_{\rmn{SZ}}$ only depends weakly on the central gas density as discussed in
Paper~I. This explains the relative location of the NCCC and
CCC populations in the $L_{1.4~\rmn{GHz}}-L_{\rmn{X,bol}}$ and
$L_{1.4~\rmn{GHz}}-Y_{\rmn{SZ}}$ planes. In particular, CCCs are shifted to the
upper right in the $L_{1.4~\rmn{GHz}}-L_{\rmn{X,bol}}$ plane while they are
shifted vertically upward in the plane spanned by
$L_{1.4~\rmn{GHz}}-Y_{\rmn{SZ}}$. In reality, we expect an (ab initio unknown)
distribution of these parameters which would substantially increase the scatter
in the scaling relations and possibly lead to a bimodality, depending on
correlations among the different parameters.

Most interestingly, the slope of the radio scaling relations does not differ
when varying parameter values because we do not include any cluster
mass-dependence in our parametrizations which is not
constrained by current data. Closely inspecting Fig.~\ref{fig:SR}, we see that
we obtain the largest changes in $L_{1.4~\rmn{GHz}}$ for variations in
$1<\gamma_{\rmn{tu}}<5$ and $B_0$ over the parameter range probed, albeit with a
stronger dependence for weaker field strengths (as expected from
equation~(\ref{eq:jnu})).

\subsection{Comparison to observations}
\label{sec:scaling-obs}

After collecting the X-ray luminosity and the SZ flux of known RHs, we compare
the resulting scaling relations to a phenomenological model realization that was
chosen to additionally obey other observational constraints (e.g., from Faraday
rotation measure studies) as well as theoretical considerations on CR transport.

\begin{figure*} 
\centering
\includegraphics[width=0.49\textwidth]{figures/PL_relation.eps}
\includegraphics[width=0.49\textwidth]{figures/PSZ_relation.eps}
\caption{Radio-to-X-ray and radio-to-SZ scaling relations in our extended CR model
  (see main text for the details of the chosen parameters) compared with
  observations.  \emph{Left.} $L_{1.4~\rmn{GHz}}-L_{\rmn{X,bol}}$ relation in
  comparison to the observational sample taken from the literature and detailed
  in Appendix~\ref{app:D}. We additionally show the detected signal of Mpc-scale 
  diffuse emission in a stacked sample of radio-quiet galaxy clusters 
  (green, \protect\citealp{2011ApJ...740L..28B}). 
  \emph{Right.} $L_{1.4~\rmn{GHz}}-Y_{\rmn{SZ}}$
  {\bf relation from the PSZ(V) sample (direct integration method) 
  of \protect\cite{2013arXiv1307.3049S}
  together with the data points shown in their Fig.~13.}}
\label{fig:PLSZ}
\end{figure*}

\subsubsection{Observational samples}

In Appendix~\ref{app:D} we construct a sample of giant radio halos (black) and
radio mini-halos (red), as well as upper limits on the radio emission
\citep{2009A&A...499..371G,2009A&A...507..661B, 2011A&A...527A..99E}, and show
this in the left panel of Fig.~\ref{fig:PLSZ}. The median redshift of this
sample is $z\approx0.18$. The corresponding observational scaling relation is
well fit by $\log_{10} L_{1.4~\rmn{GHz}} = A + B~\log_{10} L_{\rmn{X,bol}}$ with
$A=-37.204\pm1.838$ and $B=1.512\pm0.041$, and a scatter of $\sigma_{yx} \approx
0.52$ (we do not include upper limits in the fit; units are as in
Fig.~\ref{fig:PLSZ}). We refer the reader to \cite{2009A&A...507..661B}, 
\cite{2011A&A...527A..99E} and \cite{2013arXiv1306.4379C} for an extensive discussion on this topic. 
We emphasize that in contrast to giant radio halos, mini-halos span a wider range
in radio luminosity (as also pointed out by \citealp{2009A&A...499..679M}). The
Perseus mini-halo (highest radio mini-halo luminosity in the left panel of
Fig.~\ref{fig:PLSZ}), e.g., has a radio luminosity that is almost an order of
magnitude higher than in giant radio halos at the same X-ray luminosity. In
contrast, the Ophiuchus mini-halo (lowest radio mini-halo luminosity in the left
panel of Fig.~\ref{fig:PLSZ}), which is representative of a few other similar
examples recently detected in CCCs (such as A2029 and A1835), has a radio
luminosity which is much lower than giant radio halos in merging clusters and is
even below the upper limits.

We caution that the determination of the slope of the observational
$L_{1.4}-L_{\rmn{X,bol}}$ relation is not very robust because of the small
sample size of RHs, selection biases of extended low-surface brightness objects,
and systematic uncertainties in the measurements of $L_{1.4}$ and
$L_{\rmn{X,bol}}$. The recently detected low-luminosity mini-halos exemplify
those uncertainties and the large intrinsic scatter of this relation. On the
other hand, X-ray luminosities for the same object as derived by,
e.g.,~\emph{ROSAT} and \emph{Chandra} can easily differ by a factor of a
few.\footnote{For example, the bolometric X-ray luminosity of A2163 as measured
  by \emph{ROSAT} is $8.65\times10^{45}$~$h_{70}^{-1}$~erg~s$^{-1}$
  \citep{2009A&A...507..661B} while the \emph{Chandra} measurement is
  $4.93\times10^{45}$~$h_{70}^{-1}$~erg~s$^{-1}$ (\citealp{2009ApJS..182...12C};
  ACCEPT: Archive of Chandra Cluster Entropy Profile Tables;
  http://www.pa.msu.edu/astro/MC2/accept/).}  In the left panel of
Fig.~\ref{fig:PLSZ}, we additionally show the model of
\citet{2009JCAP...09..024K} with a slope of $\approx1.2$, arbitrarily normalized
for visual purposes, from their simple analytical hadronic model.

{\bf In order to compare our model to the observed 1.4~GHz radio-to-SZ scaling
relation, we use the result by \cite{2013arXiv1307.3049S} that is based 
on a sub-sample of the \emph{Planck} COSMO sample \citep{2013arXiv1303.5080P} with 
a median redshift of $z \approx XXX$, which compares favourably with our MultiDark 
$z = 0.2$ snapshot. The same comments regarding the small sample size of RHs, selection 
biases, and systematic uncertainties in the luminosity measurements also apply here.}

\subsubsection{Model realization}

In order to compare with observations, we select a
particular realization of our extended CR model. To this end, we use the MultiDark cluster
sample at $z=0.2$, which compares well with the redshift of the observational
samples; see above and Appendix~\ref{app:D}. We divide our cluster sample
randomly into radio-quiet and radio-loud clusters, assuming a ratio of $10\%$ of
the latter (see next section). We use the turbulent propagation parameter $\gamma_{\rmn{tu}}$ to
separate both populations. In radio-quiet clusters, we assign
$\gamma_{\rmn{tu}}=1$, and in radio-loud clusters, we adopt randomly and
uniformly $\gamma_{\rmn{tu}}$ values in the intervals $[40,80]$ and $[1,5]$ for
NCCCs and CCCs, respectively.

Our modeling of magnetic fields is inspired by Faraday rotation studies that
point to higher field values in the core region of CCCs compared to NCCCs
\citep{2010A&A...513A..30B,2011A&A...529A..13K}, presumably due to the higher
adiabatic compression factor during the formation of the cooling core. Hence,
for radio-quiet clusters, we adopt randomly and uniformly distributed values of
the central magnetic field $B_0$ in the intervals $[2.5,5.5]$~$\mu$G and
$[5,10]$~$\mu$G for NCCCs and CCCs, respectively. To account for the potential
turbulent dynamo in radio-loud objects (characterized by a higher turbulent
transport parameter in our model), we slightly increase $B_0$ in those objects
and chose $B_0$ intervals of $[4.5,7.5]$~$\mu$G and $[7.5,12.5]$~$\mu$G for
NCCCs and CCCs, respectively.

We fix $\alpha_{\rmn{B}}=0.5$ and $g_{\rmn{CR}}=0.5$ for all clusters. We note
that our parameter choices are mostly phenomenologically driven with the aim to
reproduce observations. The parameter study in Fig.~\ref{fig:SR} exemplifies
considerable degeneracies so that different combinations of parameters can
potentially result in very similar distributions. We emphasize the need of more
detailed observations of RHs and in particular of multi-frequency
correlation studies to constrain the interplay of some of these parameters.

In Fig.~\ref{fig:PLSZ}, we show our model in comparison to the observed
radio-to-X-ray and radio-to-SZ scaling relations. The normalization of our model
can be arbitrarily varied by changing $g_{\rmn{CR}}$ as long as the resulting
$X_{\rmn{CR}}$ respects the current observational constraints
(e.g., \citealp{2011arXiv1111.5544M}) and remains below a few percents. As
explained above, our choice of $g_{CR}=0.5$ ensures an average CR-to-thermal
pressure of $2\%$ within $R_{500}$, allowing for plenty of available parameter
space to match the observational constraints.

Our model is sufficiently flexible to either mimic a cluster radio bimodality or not, depending 
on the parameters adopted for the populations of radio-loud and radio-quiet
objects. However, with the given model realization as in Fig.~\ref{fig:PLSZ}, the
separation of the radio-loud and radio-quiet populations is substantially larger in
the $L_{1.4~\rmn{GHz}}-L_{\rmn{X,bol}}$ plane than in the
$L_{1.4~\rmn{GHz}}-Y_{\rmn{SZ}}$ plane, which exhibits almost a continuum
distribution from radio-loud CCCs to the radio-quiet NCCCs. This is mainly
because the bolometric X-ray emissivity scales with $\rho_{\rmn{gas}}^2$ while
$Y_{\rmn{SZ}}\propto\rho_{\rmn{gas}}$ (which is only strictly valid for an
isothermal gas distribution). 
%As a consequence, the highly peaked gas profiles
%of CCCs have less impact on $Y_{\rmn{SZ}}$ than on $L_{\rmn{X,bol}}$. 
This is one plausible explanation for the observed discrepancy of the presence of a
bimodality in $L_{1.4~\rmn{GHz}}-L_{\rmn{X,bol}}$ and the apparent absence of it
in $L_{1.4~\rmn{GHz}}-Y_{\rmn{SZ}}$.

The slope of our model depends on the different parameter choices and,
particularly, on the relative differences introduced for the NCCC/CCC and 
the radio-loud/quiet populations. However, we note that our
$L_{1.4~\rmn{GHz}}-L_{\rmn{X,bol}}$ is slightly shallower than the 
observed relation, more similar to the \cite{2009JCAP...09..024K} prediction.
{\bf The same apply to the $L_{1.4~\rmn{GHz}}-Y_{\rmn{SZ}}$ scaling relation. 
Potentially this may hint at the contribution of a second, leptonic component
that would steepen the slope of our model scaling relation at high masses.
In particular, the finding of \cite{2013arXiv1306.4379C} that clusters do 
seem to show a bimodaily at very high $Y_{\rmn{SZ}}$ may also be an hint 
of an increasingly important leptonic component at high masses.}

{\bf Therefore, we attempt to model such a leptonic emission component in an 
hybrid scenario. We do not expect this component to alter significantly our conclusions
regarding the luminosity functions of next sections for two main reasons. (i) It would be present only in 
the radio-loud merging NCCC sample. And (ii) it would be dominant only at very high masses 
because the dissipated energy that is available for energizing fossil electrons should be a fraction 
of the thermal energy which scales with cluster mass as $E_\rmn{th}\propto M_{200}^{5/3}$ \citep[][for 
magneto-turbulent reacceleration models]{2005MNRAS.357.1313C}. In fact, in the $z = 0.2$ snapshot 
of our mock sample, only $31$ radio-loud \mbox{NCCCs} are found for $M_{200}\geq5\times10^{14}~h_{70}^{-1}$~M$_{\odot}$, 
where, e.g., turbulent reaccelerated RHs lie according to \cite{2010A&A...509A..68C}. 
As an example of a possible leptonic component, we boost the total flux of these 31 radio-loud NCCCs, according to 
$L_{1.4~\rmn{GHz, boosted}}= L_{1.4~\rmn{GHz}}\times(1+(M_{200}/10^{15}~h_{70}^{-1}$~M$_{\odot})^{5/3})$,
from about 30\% to about 200\% for the most massive one, with a
median (mean) boost of about 46\% (58\%).\footnote{The modeling of
   Coma and Abell~2163 suggests that a boost of about 35\% to 80\%
   may be necessary. Note however that if we would allow flat CR profiles 
   in turbulent, merging clusters as in \cite{2013arXiv1303.4746W},
   the required fraction of leptionic component could be smaller.} 
The resulting boosted population is shown in both panels of Fig.~\ref{fig:PLSZ}. The 
corresponding scaling relations have slopes close to the ones of 
the $L_{1.4~\rmn{GHz}}-L_{\rmn{X,bol}}$ and $L_{1.4~\rmn{GHz}}-Y_{\rmn{SZ}}$ 
observational samples, respectively.}

Owing to the many uncertainties and lack of robustness both in the observations 
and modeling at this stage, we do not attempt to fine-tune our model to the
observations. {\bf Additionally, we do not include the possible leptonic emission 
component in the analysis of next sections, deferring the study of its physical 
details and correlation to the hadronic one to future work. Due to the nature
of our approach, the mock galaxy cluster sample is affected by incomlpetness 
in the highest-mass range because of the limited volume of the MultiDark simulation 
(Paper~1). Only a small number of objects, which lie in this mass range, would be affected 
by such a correction, as shown above and in Fig.~\ref{fig:PLSZ}. These are not statistically 
significant compared to the numbers we are going to discuss. Therefore, we prefer to point the reader to the turbulent 
reacceleration model predictions by \cite{2010A&A...509A..68C, 2012arXiv1210.1020C} for comparison, 
and to get a flavour of how an additional leptonic component would change our predictions.} 
%Note that for a given set of parameter choices, our RH fluxes are conservative lower 
%limits; in particular for the subsample of radio loud high-mass NCCCs.

Interestingly, the detected signal of Mpc-scale diffuse emission in a
stacked sample of radio-quiet galaxy clusters (shown in green in the
left plot of Fig.~\ref{fig:PLSZ}, \citealp{2011ApJ...740L..28B})
agrees with the expected signal of our radio-quiet population.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Luminosity Functions}
\label{sec:5}

\begin{figure*} 
\centering
\includegraphics[width=0.85\textwidth]{figures/RLFs_1.4.eps}
\caption{RH luminosity function (RLF) at 1.4~GHz. The top left panel shows
  the RLF of our extended CR model (see main text for the details of the chosen
  parameters) for different fractions of radio-loud clusters. Additionally shown
  is the contribution of radio-quiet and radio-loud populations to the total RLF
  (assuming a fraction of $25\%$ and $1\%$ of radio-loud objects). The top right
  panel shows the RLF obtained by applying the observed
  $L_{1.4~\rmn{GHz}}-L_{\rmn{X,bol}}$ relation to the MultiDark clusters at $z =
  0.2$, using our phenomenological gas model for $L_{\rmn{X,bol}}$ of each
  cluster; again for different percentages of radio-loud clusters.  The bottom
  left panel shows the RLF obtained by applying the observed
  $L_{1.4~\rmn{GHz}}-Y_{\rmn{SZ}, 500}$ relation to the MultiDark clusters at $z
  = 0.2$, using $Y_{\rmn{SZ}, 500}$ of our our phenomenological gas model
  for each cluster. The bottom right panel shows the comparison between the
  three approaches for 10\% of radio-loud clusters. In all panels, we show the
  NVSS survey RLF \citep{1999NewA....4..141G} with a median redshift of 
  $z\approx 0.18$, corrected for the sample incompleteness and survey sky coverage. 
  Horizontal error bars represent the mass bins while the vertical error bars are Poissonian 
  uncertainties. The light gray line marked by the arrow estimates the incompleteness limit owing
  to the adopted low-mass cut (in the construction of the mock cluster catalog, see Paper~I)
  and the scatter in the halo luminosities.}
\label{fig:RLF_1.4}
\end{figure*}

\subsection{Comparison with observations at 1.4~GHz}

In Fig.~\ref{fig:RLF_1.4}, we show the RH luminosity function (RLF) at 1.4~GHz
for a representative realization of our extended CR model (as in
Section~\ref{sec:4}), and compare it with observational results. 
The RLF is completely determined by the cluster mass function and the radio
luminosity-to-mass relation, through $L_{1.4~\rmn{GHz}}-L_{ \rmn{X,bol}}$ or
$L_{1.4~\rmn{GHz}}-Y_{\rmn{SZ}}$ in combination with our phenomenological gas
model (see Paper~I). However, in the radio band there is the additional uncertainty of the
fraction of radio-loud clusters. Thus, in Fig.~\ref{fig:RLF_1.4}, we also show
the RLFs obtained by applying the $L_{1.4~\rmn{GHz}}-L_{\rmn{X,bol}}$ and
$L_{1.4~\rmn{GHz}}-Y_{\rmn{SZ}}$ relations to simulated clusters of the
MultiDark snapshot at $z = 0.2$, using our phenomenological gas model for
$L_{\rmn{X,bol}}$ and $Y_{\rmn{SZ}, 500}$ of each cluster, respectively. Note
that this procedure is {\em only} applied to halos defined as radio-loud
clusters (which are by definition accounted for in the $L_{1.4~\rmn{GHz}}$
scaling relations) and we assume a fraction of 100\%, 25\%, 10\%, 5\% and 1\% of
radio-loud clusters. As evident from Fig.~\ref{fig:RLF_1.4}, this is different
from our model for the radio luminosity: there we define a fraction of
radio-loud clusters too, but the radio-quiet population also contributes to the
RLF with an increasing fraction at low luminosities. This is exemplified in the
top left plot of Fig.~\ref{fig:RLF_1.4}, which shows the contribution of
radio-quiet and loud populations to the total RLF, assuming a fraction of $25\%$
and $1\%$ of radio-loud objects.

In Appendix~\ref{app:D}, we make an attempt to construct an RLF from existing
X-ray flux-limited radio surveys. Few such studies exist, in particular, the cluster
radio survey done with the National Radio Astronomy Observatory (NRAO) Very
Large Array (VLA) sky survey (NVSS) at $1.4$~GHz of \cite{1999NewA....4..141G}
and the survey with the Giant Metrewave Radio Telescope (GMRT) at $610$~MHz by
\cite{VenturiGMRT_1,VenturiGMRT_2}. For the latter, one can also construct an RLF
at 1.4~GHz using the corresponding RH follow-up measurements. The fractions of
radio-loud clusters are about 6\%, 18\% and 24\% for the NVSS 1.4~GHz, GMRT
610~MHz and GMRT 1.4~GHz samples, respectively. As explained in
Appendix~\ref{app:D}, we use the 1.4~GHz NVSS RLF (with a median redshift of $z
\approx 0.18$) as observational reference for our comparisons. We conclude that
the observational determinations of the RLF is not very robust at this stage;
the very different fractions of radio-loud clusters found in the different
studies is one indicator of this. {\bf Recently, \cite{2013arXiv1306.3102K} published
the results for an \emph{extended} GMRT survey where only one additional radio 
mini-halo is found. This does not increase significantly the statistic for RLF 
studies with respect to \cite{VenturiGMRT_1,VenturiGMRT_2}. We therefore decide to 
stick with the 1.4~GHz NVSS RLF as reference in this work.}

Generally, there is fair agreement between the NVSS RLF and both our modeled RLF
and the RLFs based on observational scaling relations, particularly for
radio-loud fractions between 10\% and 1\%. In particular, we verified that the
cumulative number of RHs above a certain flux limit of the NVSS survey is well
matched by our 10\%-loud fraction case, which will be used in the following
section.  The RLF obtained from the $L_{1.4~\rmn{GHz}}-L_{\rmn{X,bol}}$ relation
differs from the NVSS RLF at high luminosities, presumably caused by the large
observed scatter.  On the other side, the RLF obtained from the
$L_{1.4~\rmn{GHz}}-Y_{\rmn{SZ}}$ relation matches the NVSS result better. These
results need to be consolidated by RLFs corrected for flux-incompleteness and
simulations of larger cosmological volumes that are more complete at the
high-mass end. Figure~\ref{fig:RLF_1.4} shows that it will be difficult to
discriminate between different scenarios at high radio luminosities (or
equivalently masses). Indeed, in the bottom right panel of
Fig.~\ref{fig:RLF_1.4} we compare our RLF and the RLFs based on observational
scaling relations for a 10\% fraction of radio-loud clusters to the NVSS
RLF. This suggests that the low-luminosity (low-mass) clusters will be the most
useful in disentangling between different models. This emphasizes the importance
of conducting homogeneous, well controlled surveys of RHs with the
Jansky VLA, ASKAP \citep{2011PASA...28..215N} and APERTIF
\citep{2012JApA..tmp...34R} at 1.4 GHz and LOFAR at lower frequencies. Since the
latter has already started to take data, it is extremely timely to present RLF
predictions in this wavelength regime for our extended hadronic model, which 
we will do next.

\subsection{Low-frequency predictions at 120~MHz}

In Fig.~\ref{fig:RLF_120}, we show our model predictions at 120~MHz obtained
with the same representative realization of our model as in Section~\ref{sec:4},
with 10\% radio-loud clusters {\bf at all redshifts}. We show both the differential RLF (top left
panel) and the cumulative number density (bottom left panel) at different
redshifts (corresponding to different the MultiDark snapshots in Table~1 of Paper~I).  
We note that the redshift evolution is almost entirely due to the
$1/(\epsilon_{\rmn{B}}+\epsilon_{\rmn{CMB}})$ factor of equation~(\ref{eq:jnu})
since $\epsilon_\rmn{CMB}\propto (1+z)^4$.  Our imposed mass cutoff of
$M_{200}=10^{14}\,h^{-1}\,M_\odot$, which has been adopted to reliably model the
cluster gas distribution (Paper~I), translates into a luminosity cutoff. This causes the
differential luminosity function to turn over at the low-luminosity end and may
artificially flatten the slope already at sightly higher luminosities than the
luminosity maximum that indicates our formal incompleteness limit.  
{\bf Note that the low-frequency predictions of our model suffer from 
the uncertainty of possible intrinsic spectral features that may differ
from our assumed power-law.}
%Note that calibrating our model to 1.4~GHz observations may cause an over- or
%underestimate of the number of low-frequency halos as a result of intrinsic
%spectral steepening (e.g., due to CR transport) or steeper leptonic spectra in
%comparison to the hadronic component in the high-mass radio-loud NCCC 
%population, respectively.

\begin{figure*} 
\centering
\includegraphics[width=0.5\textwidth,height=0.305\textheight]{figures/RLF_LOFAR.eps}
\includegraphics[width=0.47\textwidth,height=0.3\textheight]{figures/RLF_LOFAR_analytical_1.eps}
\includegraphics[width=0.5\textwidth,height=0.305\textheight]{figures/CumDensityL_LOFAR.eps}
\includegraphics[width=0.47\textwidth,height=0.3\textheight]{figures/CumDensityL_LOFAR_1.eps}
\caption{RH luminosity function $n(L,z)$ at 120~MHz (top left panel) and cumulative
  number density of RHs  $n(>L,z)$ (bottom left panel) at different redshifts $z$ (color
  coded) for the model realization described in Section~\ref{sec:4} with a 10\%
  fraction of radio-loud clusters. To obtain an analytical model for $n(L,z)$,
  we fit the logarithm of the RLF at each $z$ with a second-order polynomial and
  constrain the evolution of the three free parameters to follow a linear
  function in $1+z$ (see main text for details). The right panels show the
  comparison of the RLF fits (top) and the cumulative number density of the
  MultiDark samples (bottom) to the constrained analytical model. The bottom panels of these
  two panels show the relative differences $\Delta n / n =
  (n_{\rmn{analytical}} - n_{\rmn{fit}})/n_{\rmn{fit}}$. Additionally shown is
  the LOFAR Tier~1 \emph{point-source} flux limit of
  $F_{5\sigma}^{\rmn{PS}}=0.5$~mJy \citep{2012JApA..tmp...34R} converted to a
  luminosity limit at a given redshift. Horizontal error bars represent the mass
  bins while the vertical error bars are Poissonian uncertainties.  The light
  gray line marked by the arrow estimates the incompleteness limit owing to the
  adopted low-mass cut (in the construction of the mock cluster catalog, see Paper~I)
  and the scatter in the halo luminosities.}
\label{fig:RLF_120}
\end{figure*}

Additionally shown in Fig.~\ref{fig:RLF_120} is the expected LOFAR Tier~1
\emph{point-source} flux limit of $F_{5\sigma}^{\rmn{PS}}=0.5$~mJy
\citep{2012JApA..tmp...34R} converted to a luminosity limit at a few representative
redshifts. This flux limit is clearly an underestimate for nearby RHs, which
extend over angular scales $\sim1$~deg, as e.g., in the case of the Coma radio
halo. {\bf In order to make more reliable predictions, in the following, we will
calculate the RH flux limit with equation~(10) of \cite{2010A&A...509A..68C}
based on the assumption that RHs emit about half of their total radio flux within 
their half radius. In our sample, the typical radius within which half of the
radio flux is emitted is $R_{500}/4$, and we require that the flux within it is
higher than $F_{5\sigma}^{\rmn{PS}}$. The median $R_{500}$ of our sample 
is about $0.8$~$h_{70}^{-1}$~Mpc at all redshifts. This translates to a flux limit 
of about $48, 14, 3.5$ and $2.5$~mJy at $z = 0.1, 0.2, 0.6$ and $1$, respectively.}

\begin{figure*} 
\centering
\includegraphics[width=0.48\textwidth]{figures/RLF_LOFAR_flux.eps}
\includegraphics[width=0.48\textwidth]{figures/RLF_LOFAR_flux_detectable.eps}
\caption{Cumulative number of RHs above a certain flux limit in an all-sky
  survey at 120~MHz. We show the result of the model realization described in
  Section~\ref{sec:4} using all clusters and adopting a fraction of 10\% of
  radio-loud clusters (black solid line). Additionally, we show the result
  obtained by using the 10\% radio-loud clusters \emph{only} (black dashed
  line). We also show the differential contribution to the RLF in redshift
  slices. Note that the number of (detectable) RHs would be dramatically reduced
  by the presence of a break in the model at some low luminosity-scale, or a
  mass-dependence of the model parameters causing the RH luminosities to
  decrease at low masses.  \emph{Left.} Total number of RHs in the sky.
  \emph{Right.} Number of detectable RHs by the LOFAR Tier~1 survey considering
  its sky coverage (half sky) and adopting a realistic flux limit corresponding
  to different angular source extensions at different redshifts (see main text for details).
}
\label{fig:RLF_120_flux}
\end{figure*}

To derive low-frequency flux functions, we construct an analytical model for the
evolving RLF. We fit the 120~MHz RLF at different redshifts with a second-order
polynomial of the form $\log_{10} \rmn{d}n/\rmn{d}L_{120~\rmn{MHz}} = A_{0} +
A_{1}~\log_{10} L_{120~\rmn{MHz}} + A_{2}~(\log_{10} L_{120~\rmn{MHz}})^{2}$.
All luminosities are measured in units of $h_{70}^{-2}
\rmn{erg~s}^{-1}\,\rmn{Hz}^{-1}$ and (comoving) number densities in units of
$h_{70}^{3}\,\rmn{Mpc}^{-3}$. We consider only luminosities with $\log_{10}
L_{120~\rmn{MHz}} \geq 29.25$ to exclude the turn-over at low luminosities
caused by incompleteness. To obtain an analytical model for $n(L,z)$, we
constrain the evolution of the three free parameters $A_i$ to follow a linear
function in $1+z$, i.e., $A_{i} = A_{i,0} + A_{i,1}~(1+z)$.\footnote{The values
  of these parameters are $A_{0,0} = -436.79$, $A_{0,1} = 109.75$, $A_{1,0} =
  29.68$, $A_{1,1} = -7.17$, $A_{2,0} = -0.51$ and $A_{2,1}$ = 0.12.} In the
right panels of Fig.~\ref{fig:RLF_120}, we compare the RLF fits (top) and the
cumulative number density in the simulation (bottom) to the analytical model. In
particular the analytics matches the simulation well except for high
luminosities and high redshifts where small number statistics explains the
deviations.

This analytical model describes the number of RHs expected in our model per unit
luminosity and per unit comoving volume $V_{\rmn{c}}$, i.e., $\rmn{d}^2N(L,z)
/\rmn{d}V_{\rmn{c}}\rmn{d}L$. Hence the cumulative number of RHs above a given flux
limit $F$ is given by the integral
\begin{equation}
N(>F)  =  \int_{z_1}^{z_2} \int_{L(F)}^{\infty} 
\frac{\rmn{d}^2N(L,z)}{\rmn{d}V_{\rmn{c}}\rmn{d}L}\,
\frac{\rmn{d}V_{\rmn{c}}}{\rmn{d}z}\, \rmn{d}z\, \rmn{d}L ,
\label{eq:NtotRH}
\end{equation}
where $L(F) = 4 \pi D(z)^2 F$ and $D(z)$ is the luminosity distance to an RH at
redshift $z$.  The result is shown in the left panel of
Fig.~\ref{fig:RLF_120_flux} for the model realization described in
Section~\ref{sec:4} with a 10\% fraction of radio-loud clusters (black solid
line). We limit the integral to luminosities $\log_{10} L_{120~\rmn{MHz}}
\geq 29.25$. Our redshift integration extends from $z_{1} = 0.018$, the redshift
of the closest known RH in Perseus, to $z_{2} = 2$. As shown in
Fig.~\ref{fig:RLF_120_flux}, already redshifts $z\gtrsim1$ do not
significantly contribute to the flux function. Additionally, there are large
theoretical uncertainties since our gas model is not calibrated for these
redshifts (and implied low-mass range) and very little is observationally known
about diffuse radio emission on group scales in particularly at these redshifts,
which motivates our upper redshift limit. {\bf Note also that at these high redshifts, 
the analytical model for the evolving RLF suffers due to the non-perfect matching 
with simulations in this regime, as explained above.}

Figure~\ref{fig:RLF_120_flux} shows the contribution of different redshift
slices to the total flux function. We contrast this to the flux function using
\emph{only} the subsample of 10\% radio-loud clusters (black dashed line). This
was obtained by constructing the corresponding RLF and repeating the steps above
in building an analytical model, however, discarding luminosities $\log_{10}
L_{120~\rmn{MHz}} \leq 30.75$ in the integration.

In the right panel of Fig.~\ref{fig:RLF_120_flux}, we show the total number of
RHs that would be \emph{detectable} by the LOFAR Tier~1 survey, where its sky
coverage (of about half the entire sky) and the signal degradation due to source
extensions of close-by RHs is taken into account. The latter is calculated with
equation~(\ref{eq:NtotRH}) and adopting $F = F_{\rmn{min}}$ where
$F_{\rmn{min}}$ is given by equation~(10) of \cite{2010A&A...509A..68C} as
explained above. {\bf Comparing the left and right panel of Fig.~\ref{fig:RLF_120_flux}
elucidate the critical impact of the detection threshold on the number observable RHs.
Indeed, a detailed characterisation of the instrumental response is needed in order
to obtain more precise estimations.}

{\bf The LOFAR Tier~1 survey at 120~MHz should be able to detect about
$600$ clusters hosting RHs, considering the hadronic
component only (see \citealp{2010A&A...509A..68C,2012arXiv1210.1020C}
for predictions for giant halos in the turbulent reacceleration scenario)}. The precise number 
of detections depends strongly on the underlying assumptions. There are two main uncertainties
in our model: the fraction of radio-loud to radio-quiet clusters and the
corresponding luminosities as well as our assumed RH modeling in low-mass
clusters (which are not yet known to host RHs). The fraction of radio-loud to
radio-quiet clusters is determined from a given (degenerate) set of model
parameters that include $\gamma_{\rmn{th}}$, $B_{0}$, $\alpha_{B}$,
$g_{\rmn{CR}}$, or equivalently $X_{CR}$. The fraction of radio-loud clusters
mostly affects the number of medium-to-high luminosity RHs (as can be seen from
the 1.4~GHz RLFs in the top left panel of Fig.~\ref{fig:RLF_1.4}). The total
number of RHs is dominated by low-luminosity RHs. While this may suggest that
the radio-loud fraction is of minor importance for the detectable numbers,
instead the opposite is the case. Because of the fixed flux limit, only the most
luminous clusters at each redshift are observable so that the total number of
detectable RHs scales almost linearly with the radio-loud fraction.

%We asses the second uncertainty by comparing
%the total result of our model (black solid line) with the RLF obtained only from
%the radio-loud population (black dashed line). Their difference somehow shows
%the uncertainty in the modeling for a fixed fraction of radio-loud clusters as
%all the configuration between the solid and dashed lines can be virtually
%realized changing the relative normalization of the loud and quiet populations.

We caution that our predicted total number of (detectable) RHs depends on the
ability to extrapolate the observed and modeled scalings down to our adopted
mass limit of $M_{200}\approx1.4\times10^{14}$~$h_{70}^{-1}$~M$_{\odot}$. If the
underlying physics imprinted a characteristic scale into the CR transport or
magnetic field distribution, this would manifest itself as a break in the radio
luminosity scaling relations and dramatically reduce (or even increase) the
number of expected RHs.  While this does not interfere with previous
(high-frequency) measurements at high luminosities, this may of critical
importance for future, more sensitive (low-frequency) measurements of
low-redshift clusters that probe the uncertain regime of diffuse radio emission
in low-mass clusters.

The reason for this lies in the steep halo mass function which ensures that that
clusters above a given cutoff (that is either physically motivated or
observationally realized through a survey flux limit) dominate the total number
of (detectable) RHs. Only if the radio luminosity scaling remains unaltered
below the survey flux limit, the steepness of the mass function ensures that
there will be more RHs scattered above the flux limit then below it. This is the
so-called Eddington bias that causes the inferred luminosities based on only the
detected sources to end up as an overestimate. Hence the presence of any
hypothetical break in the radio luminosity scaling, which is unconstrained by
current data, explains the largely varying model predictions in the recent
literature, which vary from a few to hundreds observable RHs
\citep{2010A&A...509A..68C,2012arXiv1210.1020C,2011arXiv1110.2786S} to thousands 
of detectable RHs in future surveys \citep{2002A&A...396...83E}.

Another relevant issue in such surveys is the identification of RHs and their
hosting clusters (see also \citealp{2010A&A...509A..68C}). RHs constitute a
small part of the entire (diffuse as well as apparent point-like) radio source
population and therefore need to be distinguished from the emission produced by
other sources. A good approach will be to cross-correlate the radio maps with
high-sensitivity X-ray surveys such as that by the future \emph{e}ROSITA mission, which
is expected to detect around $10^{5}$ clusters up to redshift $z \approx 1.3$
(e.g., \citealp{2011MSAIS..17..159C}).

Our results show the prospects of the LOFAR survey and other future radio
instruments in determining the RH properties over a broad range of luminosities.
This should permit a robust determination of the number of clusters hosting RHs 
at a given luminosity (mass) and to carefully asses completeness issues. This will 
be extremely helpful in elucidating the RH generation mechanism, in determining the 
viable parameter space for the hadronic model and in establishing the precise role of 
the hadronic contribution to the total radio emission of merging clusters. 
{\bf In particular, the comparison with the predictions of, e.g., the turbulent reaccelerating 
scenario by \cite{2010A&A...509A..68C,2012arXiv1210.1020C}, where a significantly
smaller number of RHs is expected, will eventually help in disentangling different 
models and in identifying the importance of the hadronic component in galaxy clusters.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
\label{sec:6}

This paper aims at scrutinizing the hadronic model for giant and mini radio
halos. Our phenomenological modeling of the CR distribution is guided by
cosmological cluster simulations and theoretical considerations of microscopic
CR transport. It is designed to efficiently and simultaneously model the RH
surface brightness emission, RH scaling relations and luminosity
functions. Within the hadronic scenario, the interplay of CR advection and
streaming appears to be crucial to match observed RH distributions as a function
of SZ flux as well as to explain the bimodality of radio-loud and radio-quiet
clusters at a fixed X-ray luminosity. However, the spatial extend of giant radio
halos is difficult to accomplish within the hadronic framework, especially for
the Coma halo at low frequencies \citep{2012arXiv1207.3025B}. This calls for a
revision of purely hadronic models for giant radio halos that we propose in this
work.

To construct an \emph{extended} model for the CR distribution in clusters, we
adopt the universal spatial and spectral CR distribution found in hydrodynamic
cosmological simulations of cluster formation \citep{2010MNRAS.409..449P}. Since
these simulations only follow the macroscopic, advective CR transport, we
additionally account for microscopic CR transport processes
\citep{2011A&A...527A..99E,2013arXiv1303.4746W}. While turbulently-driven CR 
advection can lead to centrally enhanced CR profiles, CR propagation in the form 
of CR streaming and diffusion produces flatter CR profiles, which should be realized 
for decaying cluster turbulence. In our model, we introduce a CR propagation parameter
$\gamma_{\rmn{tu}}$ that is the ratio of the CR streaming-to-advection time
scale. This parameter allows us to effectively switch the regimes where either
process dominates the CR transport and to explore different turbulent states of
clusters.

This enables us to model the radio surface brightness profiles of giant radio
halos (as exemplified in Coma and Abell~2163) as well as of radio mini-halos (in
Perseus and Ophiuchus) at 1.4~GHz. We find an excellent match to mini halos over
a wide range of parameter choices, rendering the hadronic model as an attractive
explanation for mini halos. However, in order to match the extended surface
brightness profiles of giant halos at {\em high} frequencies (1.4 GHz), the
hadronic model would require flat CR profiles for magnetic field configurations
favored by Faraday rotation measurements. These flat CR profiles should only be
realized through CR streaming transport in {\em relaxed} clusters, which appears
to be in conflict with the observation that giant radio halos are hosted by merging
{\em turbulent} clusters\footnote{{\bf Note however that \cite{2013arXiv1303.4746W} 
   arrive at a different conclusion finding that the increase of turbulence promotes 
   outward streaming more than inward advection, therefore allowing flat CR 
   distributions in turbulent clusters.}}. 
{\bf Moreover, the hadronic model fails to explain the emission in the outer parts of the 
Coma halo at 352~MHz where not even the extreme case of
a flat CR profile is enough to explain the emission as of purely hadronic origin.} 
This motivates us to suggest the following new \emph{hybrid} hadronic-leptonic scenario.
\begin{enumerate}
\item Radio mini halos are primarily of hadronic origin.  
\item Giant radio halos experience a transition from the central hadronic
  emission component to a dominantly leptonic emission component in the outer
  halo that is due to Fermi I or II reacceleration of fossil or hadronically
  produced electrons.
\item Steep spectrum radio sources are mainly of leptonic origin.
\end{enumerate}
This scenario would imply an increased spectral and morphological variability in
leptonically dominated emission regions because of the intermittency and
relative inefficiency of the corresponding reacceleration processes (Fermi I
acceleration at weak intra-cluster shocks or Fermi II acceleration at plasma
waves). In particular, it implies a spectral steepening from the hadronic to the
leptonic component, since the long-lived CR protons are dominantly accelerated
by stronger formation shocks during the gas assembling history onto a cluster,
which causes a harder spectrum in comparison to the softer leptonic component.
We checked that for parameter ranges that provide acceptable matches to the
radio profiles, the resulting gamma-ray emission from the decay of neutral
pions---an inevitable by-product in hadronic CR interactions---is below
observational gamma-ray upper limits provided by {\em Fermi} and imaging
atmospheric Cherenkov telescopes.

{\bf To address the hadronic RH statistics, we apply our extended CR model 
to a cosmologically complete mock cluster catalog built from the MultiDark
$N$-body simulation in a companion paper (Paper~1).} We select a representative 
realization of our extended CR model and compare it with existing radio scaling relations. 
Because of CR transport and the different gas-density scalings of the X-ray luminosity,
$L_{\rmn{X}}\propto\int \rho_\rmn{gas}^2 \dd V$, and the Sunyaev-Zel'dovich
flux, $Y\propto\int \rho_{\rmn{gas}} k_{\rmn{B}} T \dd V$, our model is able to
simultaneously reproduce the observed bimodality of radio-loud and radio-quiet
clusters at the same $L_{\rmn{X}}$ as well as the unimodal distribution of
radio-halo luminosity versus $Y$; thereby suggesting a physical solution to this
apparent contradiction. We caution however, that some parameters in our model
are degenerate with respect to the resulting radio luminosity and radio emission
profiles, in particular $\gamma_{\rmn{tu}}$ and $ \alpha_{\rmn{B}}$ (our rate of decline
of the magnetic field toward the cluster outskirts). Multi-frequency data will
be needed to better constrain these parameters and to break these degeneracies.

{\bf We show how a possible leptonic component in an hybrid scenario could affect 
the population of high-mass radio-loud NCCCs, bringing its scaling relations in agreement 
with the the available observational samples. However, due to the nature of our approach, 
i.e., the use of an $N$-body simulation which is volume-limited, only few tens of objects 
would be affected by such a correction. These are not statistically significant against our 
whole sample and, therefore, we refrain from adding this component in the analysis
of the luminosity functions and in making predictions for future surveys.}

Assuming a {\bf constant} fraction of 10\% radio-loud clusters, we demonstrate that our 
model matches the NVSS RH luminosity function (RLF). However, the
high-luminosity tail of our model RLF is subject to cosmic variance because of
the comparably small simulation volume of $1
h^{-3}\,\rmn{Gpc}^3$. Interestingly, the RLF derived from the
$L_{1.4~\rmn{GHz}}-L_{\rmn{X,bol}}$ relation differs at high radio luminosities
from the NVSS RLF; possibly because of selection and incompleteness effects that
are not fully taken into account. The comparison between different RLFs suggests
that the low-luminosity (low-mass) regime is the most promising place to
differentiate between various models.

It is expected that the next-generation of low-frequency radio surveys will
probe this regime. Hence, we we make prediction for the LOFAR cluster survey, in
particular, we compute the 120~MHz RLF and the cumulative RH number
density. {\bf Given our assumptions, we would expect the LOFAR Tier~1 survey at
120~MHz to detect about $600\times\rmn{\emph{loud~fraction}[\%]/10}$ 
hadronically-generated RHs.} 
We caution that the precise number depends strongly on the underling assumptions. 
In particular, we assume that the model parameters can be extrapolated down to cluster 
masses of about $M_{200}\approx1.4\times10^{14}$~$h_{70}^{-1}$~M$_{\odot}$ without 
any break in the radio scaling relation that would indicate additional scales in the physics.
Most of the RHs in our sample lie at low masses and thus at low luminosities
that are unconstrained by current observations. If, e.g., the magnetic field
and/or the CR distribution in clusters are not statistically self-similar and
would exhibit much reduced strength/number density on group scales, our
predictions for the detectable number of RHs would be dramatically reduced.

This demonstrates the potential of LOFAR, and other next-generation
low-sensitivity radio instruments such as APERTIF, ASKAP, EVLA and SKA, in
determining the RLF properties. In combination with future X-ray missions like
\emph{e}ROSITA, this should yield a robust determination of the number of
clusters hosting RHs at a given luminosity (mass) and thus elucidate the
relation of the radio emission with the dynamical state of a cluster.
{\bf This is crucial in order to understand the RH generation mechanism and to
establish the precise role of the hadronic contribution in clusters.}

To summarize, we have constructed a model for the ICM (in Paper~I) and CR distributions 
in galaxy clusters that enables us to provide a cosmologically complete multi-frequency mock 
catalog for the \mbox{(non-)thermal} cluster emission at different redshifts. We make these 
catalogs publicly and freely available on-line through the MultiDark database (www.multidark.org). 
Those contain the quantities $\rho_{\rmn{gas}}$, $L_{\rmn{X, bol}}$, $Y_{\rmn{X}}$, $Y_{\rmn{SZ}}$,
$L_{120~\rmn{MHz}}$, $L_{1.4~\rmn{GHz}}$ and $L_{\gamma}$ (among many others). We hope 
that the community can make valuable use of these catalogues in
synergy with the future radio, X-ray and gamma-ray data.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{acknowledgements}
\section*{Acknowledgments}
We thank Anders Pinzke for many useful discussions. We thank Lawrence Rudnick
and Shea Brown for a reanalysis of their 352~MHz radio map of Coma, and for useful discussions. 
We thank Matteo Murgia for kindly providing the radio surface brightness profiles of Ophiuchucs
and Abell~2163 that have been recomputed with respect to the Reiprich \& B\"{o}ringher (2002) cluster 
positions, and Wolfgang Reich for providing the 1.4~GHz radio map of Coma.  
We also thank Harald Ebeling, Stefan Gottl{\"o}berg, Anatoly Klypin, Andrey Kravtsov, Adam Mantz, 
Frazer Pearce, Miguel-Angel Perez Torres, Huub R{\"o}ttgering, Jos\'e Alberto Rubi\~no, and Gustavo 
Yepes, for the useful discussions and advices.  Finally, we thank the MultiDark database
people, in particular Adrian Partl and Kristin Riebe. 
F.Z.{\ }acknowledges the CSIC financial support as a JAE-Predoc grant of the 
program ``Junta para la Ampliaci\'on de Estudios'' co-financed by the FSE. 
F.Z.{\ }acknowledges the hospitality of the Leiden Observatory during his stay.
F.Z.{\ }and F.P.{\ } thank the support of the Spanish MICINN's Consolider-Ingenio 2010 Programme 
under grant MultiDark CSD2009-00064. C.P.{\ }gratefully acknowledges financial support
of the Klaus Tschira Foundation. The MultiDark Database used in this paper and
the web application providing online access to it were constructed as part of
the activities of the German Astrophysical Virtual Observatory as result of a
collaboration between the Leibniz-Institute for Astrophysics Potsdam (AIP) and
the Spanish MultiDark Consolider Project CSD2009-00064. The Bolshoi and
MultiDark simulations were run on the NASA's Pleiades supercomputer at the NASA
Ames Research Center.
%\end{acknowledgements}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{mn2e}
%\bibliographystyle{aa}
\bibliography{bib_file}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{appendix}

\section{Cosmic Ray Modeling Details}
\label{app:B}

Here, we describe in detail how our \emph{extended} model for the CR distribution
in galaxy clusters of Section~\ref{sec:2.3} is constructed by generalizing the
analytical results by \cite{2011A&A...527A..99E}.

As anticipated in Section~\ref{sec:2.3}, when advection dominates the CR
transport, the CR normalization can be expressed as in
equation~(\ref{eq:Csimple_1}). However, when CR streaming and diffusion
dominates, the CR distribution is modified and flattens considerably. This can
be shown analytically by solving the continuity equation for CRs and obtaining
the CR density profile, $\rho_{\rmn{CR}}$, of
equation~(\ref{eg:rhoCR_1}). Assuming $P_{\rmn{th}}(R)/P_{\rmn{th},0}=n_{\rmn{e}}(R)/n_{0}$, i.e.,
neglecting the temperature dependence, and adopting a standard $\beta$-profile
for the electron density,
%
\begin{equation}
n_{\rmn{e}} = n_{0} \left( 1+\frac{R^{2}}{R_{\rmn{c}}^{2}} \right)^{-\frac{3\beta_{\rmn{cl}}}{2}} \, ,
\label{eq:beta_profile}
\end{equation}
% 
\cite{2011A&A...527A..99E} find that the solution of equation~(\ref{eg:rhoCR_1}) is physical only 
for $\rho_{\rmn{CR}}$ within the radial range $R_{-} < R < R_{+}$ with
%
\begin{equation}
R_{\pm} = \frac{3\beta_{\rmn{cl}}}{2\gamma}R_{*}\left(1\pm\sqrt{1-\left(\frac{2R_{\rmn{c}}\gamma}{3\beta_{\rmn{cl}}R_{*}}\right)^{2}}\right) \, ;
\label{eq:Rpm}
\end{equation} 
%
while it is non-stationary outside these radii. In these regions, the authors
suggest to set $\rho_{\rmn{CR}}(R) = \rho_{\rm{CR}}(R_{\pm})$ for $R > R_{+}$
and $R < R_{-}$, respectively. \cite{2011A&A...527A..99E} obtain the profile for
the CR normalization,
$C(R)=C_{0}(\rho_{\rmn{CR}}(R)/\rho_{\rmn{CR},0})^{\beta_{\rmn{CR}}}$, as
%
\begin{equation}
C(R) = C_{0}\left( 1+ \frac{R^{2}}{R_{C}^{2}} \right)^{-\beta_{\rmn{c}}} \rmn{exp}\left( {\frac{R}{R_{*}}\beta_{\rmn{CR}}} \right)
\label{eq:Ctransport}
\end{equation} 
%
for $R_{-}<R<R_{+}$, where
$\beta_{\rmn{c}}=3\beta_{\rmn{cl}}~\beta_{\rmn{CR}}/2\gamma$, and $C(R) =
C(R_{\pm})$ for $R<R_{-}$ and $R>R_{+}$, respectively. In this way, different CR
transport cases are parametrized through $\gamma_{\rmn{tu}}$.  A high value of
$\gamma_{\rmn{tu}}$ characterizes the advection-dominated case, while the CR
profile is flat for $\gamma_{\rmn{tu}} \sim1$. We refer the reader to
\cite{2011A&A...527A..99E} for an extensive discussion.

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{figures/CR_profiles_REXexactVSfake.eps}
\caption{Comparison of the exact and approximate solutions for $C(R)$ in the
  case of our GNFW profile. In the latter case, we use the formulae by
  \protect\cite{2011A&A...527A..99E} but adopt $P(R)/P_{0}=n_{\rmn{e,GNFW}}(R)/n_{0}$
  for this comparison only, i.e., we assume here an isothermal ICM. We show the GNFW
  profiles for NCCCs and CCCs, as derived in Paper~I. For each of
  these profile classes, we show three different cases of
  $\gamma_{\rmn{tu}}=100$, 10, and 1 (top to bottom). We normalize $C(R)$ for
  the advection dominated case ($\gamma_{\rmn{tu}}=100$) at $R=10^{-3}R_{200}$
  and and require CR number conservation during CR streaming. Note that the
  value for $C(10^{-3}R_{200},\gamma_{\rmn{tu}}=100)$ in the CCC case is
  identical for the exact solution and its approximation, while there is a small
  difference of about 9\% in the NCCC case. We adopt $\alpha=2.3$.}
\label{fig:REXexactVSfake}
\end{figure}

We want to extend this result to account for (i) our GNFW gas profiles of
Paper~I, (ii) the universal temperature drop in the cluster
outskirts, and (iii) merge it with the universal cluster mass-scaling of the CR
normalization, $\tilde{C}$, obtained from hydrodynamical simulations
\citep{2010MNRAS.409..449P}.  Therefore, we adopt the extended profile,
$C_{\rm{extended}} = \tilde{C}(R) (\rho_{\rmn{gas}}(R)/m_\rmn{p}) (T(R)/T_0)$, of
equation~(\ref{eq:Cf}). We note that for such a choice, there does not any more
exist an analytical solution to equation~(\ref{eg:rhoCR_1}) as in
\cite{2011A&A...527A..99E}. This results in a 5-order equation and a numerical
solution would not be of practical use for every cluster in our large MultiDark
sample. For simplicity, we adopt the formulae above also for our extended
model. I.e., we adopt
$C(R)=C_{0}(\rho_{\rmn{CR}}(R)/\rho_{\rmn{CR},0})^{\beta_{\rmn{CR}}}$ within
$R_{\pm}$ of equation~(\ref{eq:Rpm}), with $\rho_{\rmn{CR}}$ defined by
equation~(\ref{eg:rhoCR_1}) where $C_{\rmn{extended}}$ enters through the
advective CR profile, $\eta(R)$, of equation~(\ref{eq:eta}), and $C(R) =
C(R_{\pm})$ for $R > R_{+}$ and $R < R_{-}$, respectively.  Note that, in our
formalism, $R_{\rmn{c}}$ of equation~(\ref{eq:Rpm}) becomes the characteristic
radius of our GNFW gas profile (see Paper~I), i.e., $R_{\rmn{c}} =
0.2 R_{500}$, and $\beta_{\rmn{cl}}=0.8$ (we checked that varying the value of
$\beta_{\rmn{cl}}$ between 0.4 and 1.2 has no impact).  The relevant factors are
$\gamma_{\rmn{tu}}$ and the exponential factor of
equation~(\ref{eg:rhoCR_1}). As we will see in the following, the two radii
$R_{\pm}$ are not critically affected by the form of $\eta(R)$. Therefore,
despite the approximation, this approach captures the main CR transport effects.

Assuming our GNFW gas profile instead of a standard $\beta$-profile for the
electron density, so adopting $P(R)/P_{0}=n_{\rmn{e,GNFW}}(R)/n_{0}$, there
exist an exact analytical solution to equation~(\ref{eg:rhoCR_1}) as in
\cite{2011A&A...527A..99E}. In order to evaluate the systematic error that we
are introducing with the approach described above, in
Fig.~\ref{fig:REXexactVSfake}, we compare the \emph{exact} solution for $C(R)$
in the case of our GNFW profile with the \emph{approximate} solution where we
use the formulae by \cite{2011A&A...527A..99E}, and only substitute the electron
$\beta$-profile for our GNFW profiles (with $R_{\rmn{c}} = 0.2 R_{500}$,
$\beta_{\rmn{cl}}=0.8$). In this last case, we fix $R_{-}=10^{-3}R/R_{200}$ to
mimic the typical $R_{-}$ value of the exact solution, otherwise an unphysical
step feature would appear at $\leq10^{-2}R/R_{200}$. This latter approximation
is kept in our extended model, which however has no impact on the model surface
brightness and total luminosity. There is almost no difference between the two
cases, as clear from Fig.~\ref{fig:REXexactVSfake}. This shows that the approach
presented here to construct our extended model can be safely followed in order to
derive a fully working parametrization which captures the main CR transport
effects.

%\begin{figure*}[t!]
%\centering
%\includegraphics[width=0.99\textwidth]{figures/CR_profiles_simple_comparison.eps}
%\caption{Comparison of different CR profiles. The left plot shows the \emph{simple} advective $C_{\rmn{adv}}$ of equation~(\ref{eq:Csimple_1}) for the Coma and Perseus cases both neglecting the temperature dependence ($\rho$) and considering it ($P$). The temperature profile of Coma has been modified so that it follows the characteristic decline toward the cluster periphery. Perseus is a CCC and it is characterized by a central dip in the temperature profile which may importantly affect the final CR profile, so we adopt the temperature profile as given in \cite{2003ApJ...590..225C} ($P_{1}$). We also show the case where we only apply the characteristic decline toward the cluster periphery ($P_{2}$). The other two right plots show the \emph{transport} case of equation~(\ref{eq:Ctransport}) for Coma and Perseus for different values of $\gamma_{\rmn{tu}}$ in comparison with the \emph{simple} case. Additionally shown is the result in case of $C(R)=C_{\rmn{semi-analytical}}(R)=\tilde{C}(R)\rho_{\rmn{gas}}(R)/m_{\rmn{p}}$ where $\tilde{C}(R)$ is the mass-dependent universal normalization CR profile found in cosmological simulations \citep{2010MNRAS.409..449P}. The \emph{simple} and \emph{semi-analytical} profiles are normalized at $C_{0}=C(0)$. In the transport case, we fix the CR number for $\gamma_{\rmn{tu}}=100$ using equation~(36) of \cite{2011A&A...527A..99E}, while integrating the cluster volume within $R_{200}$, and require CR number conservation during CR streaming. We adopt $\alpha=2.3$.}
%\label{fig:simpleVStransport}
%\end{figure*}
%
%
%In Fig.~\ref{fig:simpleVStransport}, we show a comparison between $C_{\rmn{adv}}$ of 
%equation~(\ref{eq:Csimple_1}) and $C$ of equation~(\ref{eq:Ctransport}) considering the 
%NCCC Coma and CCC Perseus cases. While for Coma we adopt the $\beta$-profile of 
%\citet{1992A&A...259L..31B}, Perseus needs a double-$\beta$ profile. We adopt both the 
%approximation $P(R)/P_{0}=n_{\rmn{e}}(R)/n_{0}$ and the proper Perseus pressure profile 
%(X-ray data from \citealp{2003ApJ...590..225C}). Note that the \cite{2011A&A...527A..99E} 
%formalism is exact only for the approximation $P(R)/P_{0}=n_{\rmn{e}}(R)/n_{0}$ where $n_{\rmn{e}}$ 
%is a $\beta$-profile. Nevertheless, we adopt the above formulae also for Perseus as a good approximation, 
%i.e., we adopt $C(R)=C_{0}(\rho_{\rmn{CR}}(R)/\rho_{\rmn{CR},0})^{\beta_{\rmn{CR}}}$
%within $R_{\pm}$ of equation~(\ref{eq:Rpm}), and $C(R) = C(R_{\pm})$ for $R > R_{+}$ 
%and $R < R_{-}$, respectively; we take $R_{\rmn{c}}$ in equation~(\ref{eq:Rpm}) to be equal to the Perseus 
%double-$\beta$ profile outer core radius and fix $\beta_{\rmn{cl}}=0.8$. The relevant 
%parameters are $\gamma_{\rmn{tu}}$ and the exponential factor of equation~(\ref{eg:rhoCR_1}). 
%In fact, as we will see in the following, the two radii $R_{\pm}$ are not critically affected 
%by the detail of $\eta(R)$. Therefore, despite the approximation, this approach captures the 
%main CR transport effects also for the Perseus case. 
%
%In Fig.~\ref{fig:simpleVStransport}, we additionally show the result in case 
%$C(R)=C_{\rmn{semi-analytical}}(R)=\tilde{C}(R)\rho_{\rmn{\rmn{gas}}}(R)/m_{\rmn{p}}$ 
%where $\tilde{C}(R)$ is the universal normalization CR profile found in cosmological 
%simulations \citep{2010MNRAS.409..449P}. As expected, the CR profile driven by 
%simulations is characterized by a more centrally peaked profile with respect to the 
%analytical case. Note also the flatter profile of Coma with respect to Perseus, which 
%reflects their NCCC and CCC classification, respectively. Finally, the effect of varying 
%the turbulent cluster state by means of $\gamma_{\rmn{tu}}$ can be clearly appreciated.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Radio Emission}
\label{app:A}

The synchrotron emissivity $j_{\nu}$, at frequency $\nu$ and per
steradian, of a steady-state electron population where radiative cooling
balances injection from hadronic interactions (adapted from
\citealp{2008MNRAS.385.1211P} and \citealp{2011A&A...527A..99E})
is given by
%
\begin{equation}
j_{\nu}  =  A_\nu C(R) \rho_{\rmn{gas}}(R) 
\frac{\epsilon_{\rmn{B}}(R)}{\epsilon_{\rmn{B}}(R)+\epsilon_{\rmn{CMB}}} 
\left( \frac{\epsilon_{\rmn{B}}(R)}{\epsilon_{B_{\rmn{c}}}} \right)^{(\alpha-2)/4} \, ,
\label{eq:jnu}
\end{equation}
%
where $\epsilon_{\rmn{CMB}}$ is the energy density of the cosmic microwave 
background (CMB), $\epsilon_B=B^{2}/(8\pi)$ denotes the magnetic
energy density, and $B_{\rmn{c}} = \sqrt{ 8 \pi
  \epsilon_{B_{\rmn{c}}}} \simeq 31 \left( \nu/\rmn{GHz} \right)~\mu$G. 
%
The factor $A_{\nu}$ is given by: 
%
\begin{equation}
A_{\nu} = A_{\rmn{E_{synch}}} \frac{16^{2-\alpha_{\rmn{e}}}\sigma_{\rmn{pp}}m_{\rmn{e}}c^{2}}{(\alpha_{\rmn{e}}-2)\sigma_{\rmn{T}}\epsilon_{B_{\rmn{C}}}m_{\rmn{p}}}\left(\frac{m_{\rmn{p}}
}{m_{\rmn{e}}}\right)^{\alpha_{\rmn{e}}-2} \left(\frac{m_{\rmn{e}}c^{2}}{\rmn{GeV}}\right)^{\alpha_{\rmn{e}}-1} \, ,
\end{equation}
%
with
%
\begin{equation}
A_{\rmn{E_{synch}}} = \frac{\sqrt{3\pi}}{32\pi}\frac{B_{\rmn{c}}e^{3}}{m_{\rmn{e}}c^{2}}\frac{\alpha_{\rmn{e}}+\frac{7}{3}}{\alpha_{\rmn{e}}+1}\frac{\Gamma\left(\frac{3\alpha_{\rmn{e}}-1}{12}\right)\Gamma\left(\frac{3\alpha_{\rmn{e}}+7}{12}\right)\Gamma\left(\frac{\alpha_{\rmn{e}}+5}{4}\right)}{\Gamma\left(\frac{\alpha_{\rmn{e}}+7}{4}\right)} \, ,
\end{equation}
%
where $\alpha_{\rmn{e}}=\alpha+1$, the effective inelastic cross-section for
proton-proton interactions is $\sigma_{\rmn{pp}} =
32~(0.96+\rmn{e}^{4.42-2.4\alpha})$, and
$\Gamma$ is the Gamma-function
\citep{1965hmfw.book.....A}. $A_{\rmn{E_{synch}}}$ is given in units of erg, and
$A_{\nu}$ is given in units of erg~cm$^{3}$~g$^{-1}$~sr$^{-1}$.

The generalization of the radio emissivity, $j_{\nu}$, to account for three CR populations,
each characterized by different power-law spectra and the inclusion of the
normalization parameter $g_{\rmn{CR}}$, following \cite{2010MNRAS.409..449P}, is
straight forward. We obtain
%
\begin{eqnarray}
j_{\nu,\rmn{extended}} & = &g_{\rmn{CR}} C(R) \rho_{\rmn{gas}}(R) \frac{\epsilon_{\rmn{B}}(R)}{\epsilon_{\rmn{B}}(R)+\epsilon_{\rmn{CMB}}} \nonumber \\
& \times & \Sigma_{i=1}^{3} \Delta_{i} A_{\nu,i} \left( \frac{\epsilon_{\rmn{B}}(R)}{\epsilon_{B_{\rmn{c}}}} \right)^{\frac{\alpha_{i}-2}{4}}  \, ,
\end{eqnarray}
%
where the sum is over the three CR spectral indexes $\alpha_{i}=(2.55,2.3,2.15)$
with the corresponding factors $\Delta_{i} = (0.767, 0.143, 0.0975)$ found by
\cite{2010MNRAS.409..449P}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Gamma-ray Emission}
\label{app:C}

The gamma-ray flux above an energy $E_{\gamma}$ is given by (e.g.,
\citealp{2010MNRAS.409..449P})
%
\begin{equation}
F_{\gamma} (>E_{\gamma}) = \frac{1}{4\pi D^{2}} \int dV  \lambda_{\gamma}(R)\, ,
\end{equation}
%
where the omnidirectional (i.e., integrated over the $4\pi$ solid angle)
gamma-ray emissivity above $E_{\gamma}$ is $ \lambda_{\gamma}(R)=A_{\gamma} C(R)
\rho_{\rmn{gas}}(R)$. The parameter $A_{\gamma}$ is \citep{2010MNRAS.409..449P}
%
\begin{eqnarray}
A_{\gamma} = g_{\rmn{CR}} D_{\gamma,\rmn{break}} \frac{4 m_{\pi^{0}} c}{3 m_{\rmn{p}}^{2}} \Sigma_{i=1}^{3} \Delta_{i} \frac{\sigma_{\rmn{pp},i}}{\alpha_{i} \delta_{i}} \left( \frac{m_{\rmn{p}}}{2 m_{\pi^{0}}} \right)^{\alpha_{i}} \times \nonumber \\
\times \left[ \beta_{x} \left( \frac{\alpha_{i}+1}{2\delta_{i}}, \frac{\alpha_{i}-1}{2\delta_{i}} \right) \right]_{x_{1}}^{x_{2}} \, ,
\end{eqnarray}
%
where $x_{j}=\{ 1 + [ m_{\pi^{0}}c^2/(2E_{\gamma,j})]^{2\sigma_{i}} \}$, $\left[ \beta_{x}(a,b) \right]_{x_1}^{x_2} =
\beta_{x_2}(a,b)-\beta_{x_1}(a,b)$ where $\beta$ denotes the incomplete
Beta-function \citep{1965hmfw.book.....A}, and
$\delta_{i}=0.14\alpha_{i}^{-1.6}+0.44$. The term $D_{\gamma,
  \rmn{break}}=D_{\gamma}(E_{\gamma},E_{\gamma,\rmn{break}})$ represents
diffusive CR losses due to escaping protons from the cluster at the equivalent
photon energy for the break $E_{\gamma, \rmn{break}}$ (see
\citealp{2010MNRAS.409..449P} for details). $A_{\gamma}$ is given in units of
cm$^3$~s$^{-1}$~g$^{-1}$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Observational Radio-to-X-ray Scaling relation and Luminosity Function}
\label{app:D}

For comparison with the observed 1.4~GHz radio-to-X-ray scaling relation, we
include almost all RHs of the sample by \cite{2011A&A...527A..99E}. 
We exclude RXCJ1314.4-2515 and Z7160 because they lack bolometric X-ray measurements. 
%and A2626 because its X-ray luminosity is very low placing it as an extreme outlier. 
We add to our sample the clusters Ophiuchus, A2029 and A1835
\citep{2009A&A...499..371G}. The bolometric X-ray luminosities,
$L_{\rmn{X,bol}}$, of clusters hosting giant radio halos are taken from
\cite{2009A&A...507..661B}, while $L_{\rmn{X,bol}}$ values of cluster hosting
for mini-halos are taken from \cite{2002ApJ...567..716R},
\cite{Boehringer:1998vv} and ACCEPT. In the cases where measurement
uncertainties for X-ray and radio luminosities are not reported, we adopt a
$10\%$ uncertainty. Our final RH sample has a median redshift of
$z\approx0.18$. In the left panel of Fig.~\ref{fig:PLSZ}, we show the
corresponding radio-to-X-ray scaling relation which is well fit by $\log_{10}
(L_{1.4~\rmn{GHz}}/h_{70}^{-2}~\rmn{erg}~\rmn{s}^{-1}~\rmn{Hz}^{-1}) = A +
B~\log_{10} (L_{\rmn{X,bol}}/h_{70}^{-2}~\rmn{erg}~\rmn{s}^{-1})$, with
$A=-37.204\pm1.838$, $B=1.512\pm0.041$, and scatter $\sigma_{yx} \approx
0.52$. Regarding the clusters with upper limits on the diffuse radio emission in
the sample of \cite{2011A&A...527A..99E}, we select only those 8 clusters with
ACCEPT measurements to obtain a homogeneous data set in $L_{\rmn{X,bol}}$ (note
that there are a number of clusters with upper limits on $L_{1.4~\rmn{GHz}}$ for
which there are only soft-band X-ray luminosities available).

In Fig.~\ref{fig:RLFobs}, we make an attempt to construct an RLF from existing
X-ray flux-limited radio surveys. We consider the
\cite{1999NewA....4..141G} survey with NVSS at $1.4$~GHz and the
\cite{VenturiGMRT_1,VenturiGMRT_2} survey with GMRT at $610$~MHz by. We only
select RHs, i.e., we do not consider radio relics or other diffuse radio
emissions of unclear classification. The 1.4~GHz NVSS survey contains 13~RHs out
of 205 analyzed clusters while the 610~MHz GMRT survey contains 6 RHs out of the
34 observed. The sample finally analyzed by \cite{VenturiGMRT_1,VenturiGMRT_2}
is composed by 50 clusters and we can also build a corresponding RLF at 1.4~GHz
using the 12 present RHs. The fraction of radio-loud clusters is about 6\%, 18\%
and 24\% for the NVSS 1.4~GHz, GMRT 610~MHz and GMRT 1.4~GHz sample,
respectively. The corresponding median redshift is 0.18, 0.26 and 0.25. We
calculate the RLF using the classical $V_{\rmn{max}}$ estimator (e.g.,
\citealp{1976ApJ...207..700F}) correcting for the sample incompleteness and
survey sky coverage. The most problematic aspect in obtaining these RLFs, apart
from the few available objects, is the calculation of a meaningful flux
limit. We obtain such a limit by fitting the upper envelope of the
luminosity-distance distribution of a given sample, as shown in the insets of
Fig.~\ref{fig:RLFobs}, following the procedure adopted by
\cite{2011arXiv1106.5494B}. Note that it is particularly ambiguous to calculate
a meaningful flux limit for the GMRT survey due to its poor luminosity-distance
distribution. We decide therefore to take the 1.4~GHz NVSS RLF as reference in
our comparisons with observation. However, we want to stress that several issues
can affect this result, such as the small sample size that impacts the resulting
flux limit, and the Malmquist and Eddington biases. Indeed, the very different
fraction of radio loud clusters obtained from different samples is one clear
indicator of the large uncertainty in the RLF. {\bf Note that, as explained in 
Section~\ref{sec:5}, we refrain from use the newly published results of \cite{2013arXiv1306.3102K} 
on an \emph{extended} GMRT survey because they find only one additional radio 
mini-halo with respect to \cite{VenturiGMRT_1,VenturiGMRT_2}.}

\begin{figure} 
\centering
\includegraphics[width=0.48\textwidth]{figures/RLF_observations.eps}
\caption{RH luminosity function obtained from existent observations. The insets
  show the sample luminosity-distance distributions (see main text for details)
  where the solid line is the fit to the upper envelope population (indicated in
  green) employed to calculate the flux limit for the classical $V_{\rmn{max}}$
  estimator. The choice of the upper envelope population is somehow arbitrary,
  particularly in the GMRT cases due to the poor luminosity--distance
  distributions. The horizontal error bars represent the mass bins while the
  vertical error bars are Poissonian uncertainties.}
\label{fig:RLFobs}
\end{figure}

%Finally, in Fig.~\ref{fig:RLF1.4_fluxNVSS}, we compare the cumulative number of RHs above a certain flux limit at 1.4~GHz obtained by our model realization described in Section~\ref{sec:4}, adopting a fraction of 10\% of radio-loud clusters, with the NVSS survey result (data is taken from \citealp{2010A&A...509A..68C}). We repeat the steps done in Section~5.2 in order to obtain an analytical model describing the number of RHs expected in our model per unit luminosity and per unit comoving volume. We then use equationx~(\ref{eq:NtotRH}) to calculate the cumulative number of RHs above a given flux. The luminosity integration is limited to $\log_{10} L_{1.4~\rmn{120MHz}} \geq 28$ to exclude the turn-over at low luminosities caused by incompleteness, while the redshift integration is limited to the range covered by the NVSS survey of $0.044 \leq z \leq 0.2$ \citep{1999NewA....4..141G}. We find a agreement comparison between our model and the observational result of the NVSS survey.

%\begin{figure} 
%\centering
%\includegraphics[width=0.48\textwidth]{figures/RLF_1.4_flux_NVSS.eps}
%\caption{Cumulative number of RHs above a certain flux limit in an all-sky
%  survey at 1.4~GHz for $0.044 \leq z \leq 0.2$. The black line shows the result 
%  obtained with the model realization described in Section~\ref{sec:4}, adopting 
%  a fraction of 10\% of radio-loud clusters, integrating within the redshift range covered 
%  by the NVSS survey (black data points).}
%\label{fig:RLF1.4_fluxNVSS}
%\end{figure}

\end{appendix}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\label{lastpage}

\end{document}

%\del{In comparing with observations, we take as reference
%  \cite{2010MNRAS.406.1773M}. There are however many other works on this scaling
%  relation, in particularly we recall the HIghest X-ray FLUx Galaxy Cluster
%  Sample (HIFLUGCS; \citealp{2002ApJ...567..716R}), the REXCESS
%  \citep{2009A&A...498..361P} sample, and the 115 \emph{Chandra} cluster sample
%  of \cite{2007ApJ...668..772M}. The results on the slopes of the $L-M$ relation
%  can vary significantly between different samples. While the slope of
%  \cite{2010MNRAS.406.1773M} is $1.63\pm0.06$,
%  \cite{2002ApJ...567..716R}\footnote[8]{Note that we are quoting the
%    $L_{\rmn{bol}}-M_{200}$ results of \cite{2002ApJ...567..716R}.} found values
%  between $1.72\pm0.09$ and $1.89\pm0.08$ (depending on the fit procedure, which
%  also can affect the final result), \cite{2009A&A...498..361P} found
%  $2.08\pm0.13$ and \cite{2007ApJ...668..772M} found
%  $1.96\pm0.10$. Discrepancies can come from many different sources but likely
%  are to be charged to the selection criteria of the different samples as
%  recently pointed out also by \cite{2011arXiv1109.3708R}. Samples which differ
%  in, e.g., redshift distribution, mass range, fitting procedure and biases
%  treatment, and, of course, the used instrument, can give and actually gave
%  different results. Therefore we decided to take as reference the
%  \cite{2010MNRAS.406.1773M} work because it is very recent, their sample is
%  composed by a high number (238) of objects, and, more importantly, their
%  analysis takes self-consistently into account all selection effects,
%  covariances, systematic uncertainties and the cluster mass function (see also
%  \citealp{2010MNRAS.406.1759M}).}

### 2013-09-16 paper2.tex
New Fabio Version

@@
   transport, using a cosmological complete mock galaxy cluster catalog built 
-  from the MultiDark $N$-body $\Lambda$CDM simulation.} 
+  from the MultiDark $N$-body $\Lambda$CDM simulation in a companion paper.} 
   Because of CR transport and the different scalings of the
@@
   unimodal distribution of radio-halo luminosity versus $Y$; thereby suggesting
-  a physical solution to this apparent contradiction. {\bf Assuming a plausible fraction
-  of radio-loud clusters, fixed at all redshifts, we demonstrate the unique 
+  a physical solution to this apparent contradiction. {\bf Assuming a redshift-independent
+  fraction of radio-loud clusters, we demonstrate the unique 
   prospects for low-frequency radio surveys (such as the
-  LOFAR Tier~1 survey) to detect $\sim600\times\rmn{\emph{loud~fraction}[\%]}/10$ 
-  hadronically-generated (giant and mini) radio halos and to probe the underlying 
-  physics of radio halos. This shows the potentially of future radio surveys in determining 
+  LOFAR Tier~1 survey) to detect about $600\times\rmn{\emph{loud~fraction}[\%]}/10$ 
+  hadronically-generated giant and mini radio halos. 
+  This shows the potentially of future radio surveys in determining 
   the generation mechanism of halos and the importance of the hadronic component in 
@@
 features observed in some clusters. {\bf This has been recently confirmed 
-by \cite{2013arXiv1303.4746W} that developed a more rigorous treatment. 
-In particular, they show that when considering turbulent
+by \cite{2013arXiv1303.4746W}. In particular, they show that when considering turbulent
 damping, CRs can stream at super-Alfvenic velocities, which is crucial
-for CR transport to be of relevant magnitude.} 
+in order to have appreciable CR transport.} 
 Note that these phenomena were not considered in earlier analytical works 
@@
 observations in the GeV-band, see \citealt{2003ApJ...588..155R,
-  2010JCAP...05..025A,2010ApJ...717L..71A,2012AAS...21920701Z,2012arXiv1207.6749H}; for ground-based
+  2010JCAP...05..025A,2010ApJ...717L..71A,2012arXiv1207.6749H,
+  2013arXiv1308.5654T,2013arXiv1308.6278H,2013arXiv1309.0197P}; for ground-based
 observations in the energy band $\gtrsim100$~GeV, see
@@
 {\bf The main scope of this work is to improve the classical hadronic model with
-the inclusion of possible CR transport phenomena, trying in this way to solve
-its main issues when comparing to observations and to make predictions for
+the inclusion of possible CR transport phenomena, and to make predictions for
 future radio surveys. The outline is as follows. In Section~\ref{sec:2.3}, we 
@@
 Section~\ref{sec:discussion_hadronic}. In Section~\ref{sec:4}, we apply our
-extended hadronic model to a cosmologically complete mock galaxy cluster catalog 
-built from the MultiDark $N$-body $\Lambda$CDM simulation
-in Zandanel, Pfrommer \& Prada (2013; hereafter Paper~I). 
+extended hadronic model to a cosmologically complete mock galaxy cluster 
+catalog built from the MultiDark $N$-body $\Lambda$CDM simulation
+in \cite{paper1}, hereafter Paper~I. 
 We compare the resulting modeled radio-to-X-ray and radio-to-SZ
 scaling relations to current observations and show how they vary for different
-choices of our CR and magnetic parametrizations. In Section~\ref{sec:5}, we show
+choices of our CR and magnetic parametrization. In Section~\ref{sec:5}, we show
 the radio luminosity functions, compare them to current observational
-constraints and provide predictions for the hadronically-generated
+constraints and provide predictions of the hadronically-generated
 RHs for the LOFAR cluster survey. Finally, in Section~\ref{sec:6}, we present 
@@
 {\bf To construct such a model, we have to generalize the approach proposed by
-\citet{2011A&A...527A..99E}, which uses a $\beta$-profile gas parameterizatio, 
+\citet{2011A&A...527A..99E}, which uses a $\beta$-profile gas parameterization, 
 in order to account for different kind of ICM gas profiles, such as our generalized 
-Navarro-Frank-White (GNFW) profiles derived in Paper~I from X-ray observations.} 
+Navarro-Frank-White (GNFW) ICM profiles derived in Paper~I from X-ray observations.} 
 We also have to include the cluster mass-scaling of the
@@
 \citealp{2010MNRAS.409..449P}) and with the exact analytical solution as in
-\citet{2011A&A...527A..99E}, but for our GNFW profiles (Appendix~\ref{app:B}
+\citet{2011A&A...527A..99E}, but for our GNFW profiles (see Appendix~\ref{app:B}
 for details).  The profiles are normalized at $0.1 R_{200}$. In the case of
@@
 \emph{maximum CR acceleration efficiency}, $g(\zeta_{\rmn{p,max}})$,
-\citep{2010MNRAS.409..449P} but \emph{only} for
-$\gamma_{\rmn{tu}}\gtrsim100$.
+but \emph{only} for $\gamma_{\rmn{tu}}\gtrsim100$ \citep{2010MNRAS.409..449P}.
 
@@
 above 100~MeV (100~GeV) is $F_{\gamma} = 2.4 \times 10^{-9}$ ($8.7 \times
-10^{-13}$) cm$^{-2}$~s$^{-1}$. This is below the the gamma-ray limit recently
-set with the \emph{Fermi} data of $F_{\gamma, UL} (>100~\rmn{MeV}) \approx 3.2
-\times 10^{-9}$~cm$^{-2}$~s$^{-1}$ \citep{2012...VERITAS}.  Note that for
-slightly higher values of $\gamma_{\rmn{tu}}$, i.e., a more centrally
+10^{-13}$) cm$^{-2}$~s$^{-1}$. 
+{\bf We can compare our $F_{\gamma} (>500~\rmn{MeV}) = 6.9 \times10^{-10}$~cm$^{-2}$~s$^{-1}$
+to the upper limit recently set with the \emph{Fermi} data of $F_{\gamma, UL} (>500~\rmn{MeV}) 
+= 4 \times 10^{-10}$~cm$^{-2}$~s$^{-1}$ \citep{2013arXiv1308.5654T}.  
+However, we note that the latter has been obtained using the \cite{2010MNRAS.409..449P}
+model which is significantly more peaked than the $\gamma_{\rmn{tu}} = 2$ case
+and, therefore, is too stringent for a proper comparison.}
+Note also that for slightly higher values of $\gamma_{\rmn{tu}}$, i.e., a more centrally
 concentrated CR distribution, the radio and gamma-ray yield would be increased
@@
 $g_{\rmn{CR}}$). This causes the associated gamma-ray flux also to be reduced to
-a level that is low enough to easily circumvent the gamma-ray constraints. E.g.,
-for the parameter combination $\gamma_{\rmn{tu}} = 3$ and
-$\alpha_{\rmn{B}}=0.4$, we obtain $F_{\gamma} (>100~\rmn{MeV}) = 1.3 \times
-10^{-9}$~cm$^{-2}$~s$^{-1}$ (and $F_{\gamma} (>100~\rmn{GeV}) = 4.9 \times
-10^{-13}$~cm$^{-2}$~s$^{-1}$).  We caution that in principle, CR streaming
+a level that is low enough to easily circumvent the gamma-ray constraints. 
+{\bf E.g., for the parameter combination $\gamma_{\rmn{tu}} = 3$ and
+$\alpha_{\rmn{B}}=0.4$, we obtain $F_{\gamma} = 1.3 \times 10^{-9}, 3.9 \times 10^{-10}$,
+and $4.9 \times 10^{-13}$~cm$^{-2}$~s$^{-1}$ for energies above 100~MeV, 500~MeV,
+and 100~GeV, respectively.}  We caution that in principle, CR streaming
 should cause the CR spectrum to steepen \citep{2013arXiv1303.4746W}.  
@@
 ``missing zero spacing'' problem. At $\sim5$~GHz, the SZ decrement is comparable
-to the measured RH flux. {\bf Additionally, we want to stress once more that
-CR streaming can also cause spectral steepening \citep{2013arXiv1303.4746W}.}  
+to the measured RH flux. {\bf Recently, \cite{2013arXiv1309.1820B}, using the
+correlation between $Y_{\rmn{SZ}}$ and the low-frequency radio-halo 
+brightness \citep{2011MNRAS.412....2B,2012arXiv1208.3611P}, 
+found that the SZ decrement at $\sim5$~GHz is below 10\%.
+This is clearly in contrast with the results from our simplified approach,
+at least for $\alpha \ge 2.7$. However, as pointed out by \cite{2013arXiv1309.1820B}, 
+the low-frequency observations by \cite{2011MNRAS.412....2B} imply that the Coma
+radio halo is significantly larger than what thought before. This could dramatically
+impact the estimations regarding the SZ decrement and more sensitive
+observations are needed to better clarify this issue. On this, we want to stress once more 
+that CR streaming can also cause spectral steepening \citep{2013arXiv1303.4746W}.
+}
+
 %This demonstrates that the magnitude of the SZ effect
@@
 (i) Merging clusters are not spherically symmetric as can be seen in Coma and
-  Abell~2163, requiring inherently non-spherical modelling. In order to
+  Abell~2163, requiring inherently non-spherical modeling. In order to
   reproduce the more extended radio emission relative to the thermal X-ray
@@
 
-The small cluster sample analysed here is only meant to serve as a proof
+The small cluster sample analyzed here is only meant to serve as a proof
 of concept and to show the viability of matching observed representative 
@@
 observational input on the magnetic field in clusters ($B_0$, $ \alpha_{\rmn{B}}$), 
-the parameter space that the physics modeled here demands is quite large
-encompassing also $\gamma_{\rmn{tu}}$ and the CR acceleration efficiency
-function. Particularly, a large region of the ($\gamma_{\rmn{tu}}$,
+which is, however, very limited, the parameter space that the physics modeled here 
+demands is quite large encompassing also $\gamma_{\rmn{tu}}$ and the CR acceleration 
+efficiency function. Particularly, a large region of the ($\gamma_{\rmn{tu}}$,
 $\alpha_{\rmn{B}}$) parameter space is available for the analyzed radio
@@
 There are a number of plausible processes for the latter.     
-These includes turbulent reacceleration of primary or secondary (hadronic)
-electrons \citep{2010arXiv1008.0184B} or reacceleration of fossil electrons by
+These includes turbulent re-acceleration of primary or secondary (hadronic)
+electrons \citep{2010arXiv1008.0184B} or re-acceleration of fossil electrons by
 means of diffusive shock acceleration \citep{kang11,kang12,pinzke13}.
@@
   because the CRs see a smaller target density in the outer parts. 
-  {\bf Additionally, \cite{2013arXiv1303.4746W} opened the possibility
-  to substantially decrease the radio flux even in merging clusters as
-  they found that turbulence seems to promote outward streaming 
-  more than inward advection.} This should
-  lead naturally to a bimodality of radio synchrotron emissivities due to
+  {\bf Additionally, \cite{2013arXiv1303.4746W} found that turbulence seems 
+  to promote outward streaming more than inward advection, suggesting the 
+  possibility to substantially decrease the radio flux even in merging clusters.} 
+  This should lead naturally to a bimodality of radio synchrotron emissivities due to
   hadronic and leptonic halo components.
@@
   are two separated populations for each model realization, shown with the same
-  color. The upper sets of points correspond to the CCC population while the
-  lower sets correspond to NCCCs. The plot labels indicate those parameters
-  which are kept fixed. We fix the $g_{\rmn{CR}}$-normalization parameter to 0.5
+  color but different symbols. The upper sets of points (circles) correspond to the CCC 
+  population while the lower sets (triangles) correspond to NCCCs. The plot labels indicate 
+  those parameters which are kept fixed. We fix the $g_{\rmn{CR}}$-normalization parameter to 0.5
   for all cases. See main text for details.}
@@
 
-{\bf In the following we apply our model to the complete
+{\bf In the following, we apply our model to the complete
 cosmological mock cluster catalog build from the MultiDark $N$-body 
@@
 average CR-to-thermal pressure of $2\%$ ($0.05\%$) within $R_{500}$
-($R_{500}/2$) {\bf as suggested by current gamma-ray limits}. 
-Here, the radio luminosity is calculated at $1.4$~GHz within
+($R_{500}/2$). Here, the radio luminosity is calculated at $1.4$~GHz within
 $R_{500}.$\footnote{The mean (median) difference between calculating $L_{\nu}$
@@
 each model realization (i.e., for a given set of parameters). Each upper set of
-points corresponds to the CCC population while the lower set corresponds to
-NCCCs, respectively. In our model, the radio and X-ray emissivities scale with
-the square of the gas density so that $L_{1.4~\rmn{GHz}}$ and $L_{\rmn{X,bol}}$
+points (circles) corresponds to the CCC population while the lower set (triangles) 
+corresponds to NCCCs, respectively. In our model, the radio and X-ray emissivities scale 
+with the square of the gas density so that $L_{1.4~\rmn{GHz}}$ and $L_{\rmn{X,bol}}$
 are significantly higher for CCCs in comparison to NCCCs. In contrast,
@@
   (green, \protect\citealp{2011ApJ...740L..28B}). 
-  \emph{Right.} $L_{1.4~\rmn{GHz}}-Y_{\rmn{SZ}}$
-  {\bf relation from the PSZ(V) sample (direct integration method) 
+  \emph{Right.} $L_{1.4~\rmn{GHz}}-Y_{\rmn{SZ}}$ relation 
+  in comparison with
+  {\bf the PSZ(V) sample (direct integration method) 
   of \protect\cite{2013arXiv1307.3049S}
@@
 on a sub-sample of the \emph{Planck} COSMO sample \citep{2013arXiv1303.5080P} with 
-a median redshift of $z \approx XXX$, which compares favourably with our MultiDark 
-$z = 0.2$ snapshot. The same comments regarding the small sample size of RHs, selection 
-biases, and systematic uncertainties in the luminosity measurements also apply here.}
+a median redshift of $z \approx 0.22$ (we use their PSZ(V) sample), which compares favorably 
+with our MultiDark $z = 0.2$ snapshot. The same comments regarding the small sample size of RHs, 
+selection biases, and systematic uncertainties in the luminosity measurements also apply here.}
 
@@
 sample at $z=0.2$, which compares well with the redshift of the observational
-samples; see above and Appendix~\ref{app:D}. We divide our cluster sample
+samples (see above and Appendix~\ref{app:D}). We divide our cluster sample
 randomly into radio-quiet and radio-loud clusters, assuming a ratio of $10\%$ of
@@
 $X_{\rmn{CR}}$ respects the current observational constraints
-(e.g., \citealp{2011arXiv1111.5544M}) and remains below a few percents. As
+and remains below a few percents. As
 explained above, our choice of $g_{CR}=0.5$ ensures an average CR-to-thermal
-pressure of $2\%$ within $R_{500}$, allowing for plenty of available parameter
-space to match the observational constraints.
+pressure of $2\%$ within $R_{500}$.
 
@@
 {\bf The same apply to the $L_{1.4~\rmn{GHz}}-Y_{\rmn{SZ}}$ scaling relation. 
-Potentially this may hint at the contribution of a second, leptonic component
-that would steepen the slope of our model scaling relation at high masses.
+Potentially, this may hint at the contribution of a second, leptonic component
+that would steepen the slope of our model scaling relation at high mass.
 In particular, the finding of \cite{2013arXiv1306.4379C} that clusters do 
 seem to show a bimodaily at very high $Y_{\rmn{SZ}}$ may also be an hint 
-of an increasingly important leptonic component at high masses.}
-
-{\bf Therefore, we attempt to model such a leptonic emission component in an 
-hybrid scenario. We do not expect this component to alter significantly our conclusions
-regarding the luminosity functions of next sections for two main reasons. (i) It would be present only in 
-the radio-loud merging NCCC sample. And (ii) it would be dominant only at very high masses 
-because the dissipated energy that is available for energizing fossil electrons should be a fraction 
-of the thermal energy which scales with cluster mass as $E_\rmn{th}\propto M_{200}^{5/3}$ \citep[][for 
-magneto-turbulent reacceleration models]{2005MNRAS.357.1313C}. In fact, in the $z = 0.2$ snapshot 
+of an increasingly important leptonic component.} 
+{\bf However, we do not expect this component to alter significantly our conclusions
+regarding the luminosity functions of next sections for two main reasons. (i) It would be present 
+only in the radio-loud merging NCCC sample, the radio (giant) halos. And (ii) it would be dominant only 
+at very high masses because the dissipated energy that is available for energizing fossil electrons should 
+be a fraction of the thermal energy which scales with cluster mass as $E_\rmn{th}\propto M_{200}^{5/3}$ \citep[][for 
+magneto-turbulent re-acceleration models]{2005MNRAS.357.1313C}. In fact, in the $z = 0.2$ snapshot 
 of our mock sample, only $31$ radio-loud \mbox{NCCCs} are found for $M_{200}\geq5\times10^{14}~h_{70}^{-1}$~M$_{\odot}$, 
 where, e.g., turbulent reaccelerated RHs lie according to \cite{2010A&A...509A..68C}.
-As an example of a possible leptonic component, we boost the total flux of these 31 radio-loud NCCCs, according to 
-$L_{1.4~\rmn{GHz, boosted}}= L_{1.4~\rmn{GHz}}\times(1+(M_{200}/10^{15}~h_{70}^{-1}$~M$_{\odot})^{5/3})$,
-from about 30\% to about 200\% for the most massive one, with a
-median (mean) boost of about 46\% (58\%).\footnote{The modeling of
+
+As an example of a possible leptonic component, we boost the total flux of these 31 radio-loud NCCCs 
+according to $L_{1.4~\rmn{GHz, boosted}} = L_{1.4~\rmn{GHz, had}} + L_{1.4~\rmn{GHz, boost}}$,
+where $L_{1.4~\rmn{GHz, had}}$ is the value coming from our extended hadronic model
+and
+
+\begin{equation}
+L_{1.4~\rmn{GHz, boost}} = L_{1.4~\rmn{GHz, had}} \times \left( \frac{M_{500}}{7.5\times10^{14}~h_{70}^{-1}~\rmn{M}_{\odot}} \right)^{2.3} \sim M_{500}^4 \, .
+\label{eg:leptonic_boost}
+\end{equation}
+
+This represent just a phenomenological fudge aiming to reproduce what 
+expected by turbulent re-acceleration $L_{1.4~\rmn{GHz}} \sim M_{500}^4$ 
+\citep{2007MNRAS.378.1565C,2013arXiv1306.4379C}.
+It is tied to the underling hadronic component such that we can use as
+guidance the results obtained with the surface brightness modeling
+on the missing signal fraction. Additionally, in this way, it is tied to the
+CR and B properties of a given cluster.  
+As $L_{1.4~\rmn{GHz, had}} \sim M_{500}^{1.7}$,
+we add an additional mass scaling to reach the
+desired $L_{1.4~\rmn{GHz}} \sim M_{500}^4$.
+The resulting median (mean) boost is about
+32\% (47\%) of the hadronic component.\footnote{The modeling of
    Coma and Abell~2163 suggests that a boost of about 35\% to 80\%
@@
    in turbulent, merging clusters as in \cite{2013arXiv1303.4746W},
-   the required fraction of leptionic component could be smaller.} 
-The resulting boosted population is shown in both panels of Fig.~\ref{fig:PLSZ}. The 
+   the required fraction of leptonic component could be smaller.} 
+The boosted population is shown in both panels of Fig.~\ref{fig:PLSZ}. The 
 corresponding scaling relations have slopes close to the ones of 
@@
 and modeling at this stage, we do not attempt to fine-tune our model to the
-observations. {\bf Additionally, we do not include the possible leptonic emission 
+observations. {\bf In particular, we refrain to introduce any 
+mass-dependance in our free parameters at this stage.
+Additionally, we do not include the possible leptonic emission 
 component in the analysis of next sections, deferring the study of its physical 
-details and correlation to the hadronic one to future work. Due to the nature
-of our approach, the mock galaxy cluster sample is affected by incomlpetness 
+details and correlation to the hadronic one to future work. 
+The mock galaxy cluster sample used here is affected by incompleteness 
 in the highest-mass range because of the limited volume of the MultiDark simulation 
-(Paper~1). Only a small number of objects, which lie in this mass range, would be affected 
+(Paper~I). Only a small number of objects, lying in this mass range, would be affected 
 by such a correction, as shown above and in Fig.~\ref{fig:PLSZ}. These are not statistically 
-significant compared to the numbers we are going to discuss. Therefore, we prefer to point the reader to the turbulent 
-reacceleration model predictions by \cite{2010A&A...509A..68C, 2012arXiv1210.1020C} for comparison, 
-and to get a flavour of how an additional leptonic component would change our predictions.} 
-%Note that for a given set of parameter choices, our RH fluxes are conservative lower 
-%limits; in particular for the subsample of radio loud high-mass NCCCs.
-
-Interestingly, the detected signal of Mpc-scale diffuse emission in a
-stacked sample of radio-quiet galaxy clusters (shown in green in the
+significant compared to the numbers we are going to discuss. Therefore, we prefer to point the 
+reader to the turbulent re-acceleration model predictions by \cite{2010A&A...509A..68C, 
+2012arXiv1210.1020C} for comparison, and to get a flavor of how an additional leptonic 
+component would change our predictions at that complementary mass scale.}
+
+As a final remark, we note that, interestingly, the detected signal of Mpc-scale diffuse 
+emission in a stacked sample of radio-quiet galaxy clusters (shown in green in the
 left plot of Fig.~\ref{fig:PLSZ}, \citealp{2011ApJ...740L..28B})
@@
 {\bf Note that the low-frequency predictions of our model suffer from 
-the uncertainty of possible intrinsic spectral features that may differ
-from our assumed power-law.}
+the uncertainty of possible intrinsic spectral features not considered
+here (e.g. spectral steepening by CR transport, SZ decrement).}
 %Note that calibrating our model to 1.4~GHz observations may cause an over- or
@@
 which motivates our upper redshift limit. {\bf Note also that at these high redshifts, 
-the analytical model for the evolving RLF suffers due to the non-perfect matching 
-with simulations in this regime, as explained above.}
+the analytical model for the evolving RLF results in spurious counts due to the 
+non-perfect matching with simulations in this regime.}
 
@@
 elucidate the critical impact of the detection threshold on the number observable RHs.
-Indeed, a detailed characterisation of the instrumental response is needed in order
+Indeed, a detailed characterization of the instrumental response is needed in order
 to obtain more precise estimations.}
@@
 {\bf The LOFAR Tier~1 survey at 120~MHz should be able to detect about
-$600$ clusters hosting RHs, considering the hadronic
-component only (see \citealp{2010A&A...509A..68C,2012arXiv1210.1020C}
-for predictions for giant halos in the turbulent reacceleration scenario)}. The precise number 
-of detections depends strongly on the underlying assumptions. There are two main uncertainties
+$600$ clusters hosting radio giant and mini halos, considering the hadronic 
+component only. We refer the reader to \cite{2010A&A...509A..68C} 
+for predictions for giant halos in the turbulent 
+re-acceleration scenario. We note that those are at a complementary,
+and higher, mass scale with respect to ours which are limited by the
+volume of the MultiDark simulation (see Paper~I).}
+
+The precise number of detections depends strongly on the 
+underlying assumptions. There are two main uncertainties
 in our model: the fraction of radio-loud to radio-quiet clusters and the
@@
 the radio-loud fraction is of minor importance for the detectable numbers,
-instead the opposite is the case. Because of the fixed flux limit, only the most
+instead the opposite is the case. Because of the flux limit, only the most
 luminous clusters at each redshift are observable so that the total number of
@@
 the hadronic contribution to the total radio emission of merging clusters. 
-{\bf In particular, the comparison with the predictions of, e.g., the turbulent reaccelerating 
+{\bf In particular, the comparison with the predictions of the turbulent reaccelerating 
 scenario by \cite{2010A&A...509A..68C,2012arXiv1210.1020C}, where a significantly
-smaller number of RHs is expected, will eventually help in disentangling different 
+smaller number of objects is expected, will eventually help in disentangling different 
 models and in identifying the importance of the hadronic component in galaxy clusters.}
@@
 the Coma halo at low frequencies \citep{2012arXiv1207.3025B}. This calls for a
-revision of purely hadronic models for giant radio halos that we propose in this
-work.
+revision of purely hadronic models for giant radio halos.
 
@@
 to be in conflict with the observation that giant radio halos are hosted by merging
-{\em turbulent} clusters\footnote{{\bf Note however that \cite{2013arXiv1303.4746W} 
+{\em turbulent} clusters.\footnote{{\bf Note, however, that \cite{2013arXiv1303.4746W} 
    arrive at a different conclusion finding that the increase of turbulence promotes 
    outward streaming more than inward advection, therefore allowing flat CR 
-   distributions in turbulent clusters.}}. 
+   distributions in turbulent clusters.}} 
 {\bf Moreover, the hadronic model fails to explain the emission in the outer parts of the 
@@
   emission component to a dominantly leptonic emission component in the outer
-  halo that is due to Fermi I or II reacceleration of fossil or hadronically
+  halo that is due to Fermi I or II re-acceleration of fossil or hadronically
   produced electrons.
@@
 leptonically dominated emission regions because of the intermittency and
-relative inefficiency of the corresponding reacceleration processes (Fermi I
+relative inefficiency of the corresponding re-acceleration processes (Fermi I
 acceleration at weak intra-cluster shocks or Fermi II acceleration at plasma
@@
 to a cosmologically complete mock cluster catalog built from the MultiDark
-$N$-body simulation in a companion paper (Paper~1).} We select a representative 
+$N$-body simulation in a companion paper (Paper~I).} We select a representative 
 realization of our extended CR model and compare it with existing radio scaling relations. 
@@
 
-{\bf We show how a possible leptonic component in an hybrid scenario could affect 
-the population of high-mass radio-loud NCCCs, bringing its scaling relations in agreement 
-with the the available observational samples. However, due to the nature of our approach, 
-i.e., the use of an $N$-body simulation which is volume-limited, only few tens of objects 
+{\bf We introduce a phenomenological realization of the additional leptonic component in an hybrid scenario,
+and show how this can affect the population of high-mass radio-loud NCCCs (radio giant halos), bringing 
+its scaling relations in agreement with the the available observational samples. However, due to the nature of 
+our approach, i.e., the use of an $N$-body simulation which is volume-limited, only few tens of objects 
 would be affected by such a correction. These are not statistically significant against our 
@@
 
-Assuming a {\bf constant} fraction of 10\% radio-loud clusters, we demonstrate that our 
+Assuming a {\bf redshift-independent} fraction of 10\% radio-loud clusters, we demonstrate that our 
 model matches the NVSS RH luminosity function (RLF). However, the
@@
 120~MHz to detect about $600\times\rmn{\emph{loud~fraction}[\%]/10}$ 
-hadronically-generated RHs.} 
+hadronically-generated radio giant and mini halos.} 
 We caution that the precise number depends strongly on the underling assumptions. 
@@
 
-To summarize, we have constructed a model for the ICM (in Paper~I) and CR distributions 
+We have constructed a model for the ICM (in Paper~I) and CR distributions 
 in galaxy clusters that enables us to provide a cosmologically complete multi-frequency mock 
@@
 We thank Anders Pinzke for many useful discussions. We thank Lawrence Rudnick
-and Shea Brown for a reanalysis of their 352~MHz radio map of Coma, and for useful discussions. 
-We thank Matteo Murgia for kindly providing the radio surface brightness profiles of Ophiuchucs
-and Abell~2163 that have been recomputed with respect to the Reiprich \& B\"{o}ringher (2002) cluster 
-positions, and Wolfgang Reich for providing the 1.4~GHz radio map of Coma.  
-We also thank Harald Ebeling, Stefan Gottl{\"o}berg, Anatoly Klypin, Andrey Kravtsov, Adam Mantz, 
-Frazer Pearce, Miguel-Angel Perez Torres, Huub R{\"o}ttgering, Jos\'e Alberto Rubi\~no, and Gustavo 
-Yepes, for the useful discussions and advices.  Finally, we thank the MultiDark database
-people, in particular Adrian Partl and Kristin Riebe. 
+and Shea Brown for a reanalysis of their 352~MHz radio map of Coma, and for useful 
+discussions. We thank Matteo Murgia for kindly providing the radio surface brightness 
+profiles of Ophiuchucs and Abell~2163 that have been recomputed with respect to the 
+Reiprich \& B\"{o}ringher (2002) cluster positions, and Wolfgang Reich for providing the 
+1.4~GHz radio map of Coma.  We also thank Miguel-Angel Perez Torres and Huub 
+R{\"o}ttgering for the useful discussions and advices.  Finally, we thank the MultiDark 
+database people, in particular Adrian Partl and Kristin Riebe. 
 F.Z.{\ }acknowledges the CSIC financial support as a JAE-Predoc grant of the 
@@
 fraction of radio loud clusters obtained from different samples is one clear
-indicator of the large uncertainty in the RLF. {\bf Note that, as explained in 
+indicator of the large uncertainty in the RLF.
+
+{\bf Note that, as explained in 
 Section~\ref{sec:5}, we refrain from use the newly published results of \cite{2013arXiv1306.3102K} 

### 2013-09-20 paper2.tex
Last Fabio Version

@@
 %  origin, (ii) giant halos experience a transition from central hadronic
-%  emission to peripheral leptonic emission due to Fermi I or II reacceleration
+%  emission to peripheral leptonic emission due to Fermi I or II re-acceleration
 %  of fossil or hadronically produced electrons, and (iii) steep spectrum radio
@@
 \begin{keywords}
-  Galaxies: clusters - Radio continuum - Gamma rays - X-rays: galaxies: clusters
+  Galaxies: clusters - Radio continuum - Gamma rays
 \end{keywords}
@@
 by \cite{2013arXiv1303.4746W}. In particular, they show that when considering turbulent
-damping, CRs can stream at super-Alfvenic velocities, which is crucial
-in order to have appreciable CR transport.} 
+damping, CRs can stream at super-Alfvenic velocities.} 
 Note that these phenomena were not considered in earlier analytical works 
@@
 
-Recently, \cite{2012MNRAS.421L.112B} presented the first scaling relations
+\cite{2012MNRAS.421L.112B} presented the first scaling relations
 between RH luminosity and Sunyaev-Zel'dovich (SZ) flux measurements, using the
@@
 responsible in maintaining the radio emission in either model (that accounts for
-microscopic CR transport). {\bf This has been confirmed by \cite{2013arXiv1307.3049S}
-and \cite{2013arXiv1306.4379C}.}
+microscopic CR transport). {\bf This has been recently confirmed by 
+\cite{2013arXiv1307.3049S} and \cite{2013arXiv1306.4379C}.}
 
@@
 
-{\bf The main scope of this work is to improve the classical hadronic model with
+{\bf The main scope of this work is to upgrade the classical hadronic model with
 the inclusion of possible CR transport phenomena, and to make predictions for
@@
 scaling relations to current observations and show how they vary for different
-choices of our CR and magnetic parametrization. In Section~\ref{sec:5}, we show
+choices of our CR and magnetic field parametrizations. In Section~\ref{sec:5}, we show
 the radio luminosity functions, compare them to current observational
-constraints and provide predictions of the hadronically-generated
+constraints, and provide predictions of the hadronically-generated
 RHs for the LOFAR cluster survey. Finally, in Section~\ref{sec:6}, we present 
@@
 
-The spatial CR distribution within a galaxy cluster is governed by an interplay
+The spatial CR distribution $C(R)$ within a galaxy cluster is governed by an interplay
 of CR advection, streaming, and diffusion. The advection of CRs by turbulent gas
@@
 
-Recently, \citet{2012arXiv1207.3025B} pointed out problems of the hadronic model
+\citet{2012arXiv1207.3025B} pointed out problems of the hadronic model
 for the limited parameter space $\alpha\gtrsim2.6$, while adopting a much
@@
 outward streaming more than inward advection, therefore allowing flat CR 
-distributions in turbulent clusters. However, this does not help in, e.g.,
+distributions in turbulent clusters. However, this does not help in
 the case of the 352~MHz data, where, as discussed above, not even a
@@
 emission component in the preceding section. Hence, by construction, we 
-neglected other (leptonic) emission components, such as re-accelerated electrons. 
+neglected other (leptonic) emission components, such as reaccelerated electrons. 
 {\bf Possible biases that may affect our previous conclusions are the following.}
@@
   to promote outward streaming more than inward advection, suggesting the 
-  possibility to substantially decrease the radio flux even in merging clusters.} 
+  possibility to substantially decrease the radio flux also in merging clusters.} 
   This should lead naturally to a bimodality of radio synchrotron emissivities due to
@@
 simulation in our Paper~I. For each object in the sample, we mainly use
-the information on its mass, radius and phenomenologically assigned 
+the information on its mass and phenomenologically assigned 
 ICM gas density to calculate the radio (and gamma-ray) emission.}
@@
 regarding the luminosity functions of next sections for two main reasons. (i) It would be present 
-only in the radio-loud merging NCCC sample, the radio (giant) halos. And (ii) it would be dominant only 
+only in the radio-loud merging NCCC sample, i.e., the radio (giant) halos. And (ii) it would be dominant only 
 at very high masses because the dissipated energy that is available for energizing fossil electrons should 
@@
 
-This represent just a phenomenological fudge aiming to reproduce what 
+We stress that this is just a phenomenological correction factor aiming to reproduce what 
 expected by turbulent re-acceleration $L_{1.4~\rmn{GHz}} \sim M_{500}^4$ 
@@
 It is tied to the underling hadronic component such that we can use as
-guidance the results obtained with the surface brightness modeling
-on the missing signal fraction. Additionally, in this way, it is tied to the
-CR and B properties of a given cluster.  
+guidance the results on the missing signal fraction obtained with the 
+surface brightness modeling. Additionally, in this way, it is tied to the
+CR and magnetic field properties of a given cluster.  
 As $L_{1.4~\rmn{GHz, had}} \sim M_{500}^{1.7}$,
-we add an additional mass scaling to reach the
+we adopt an additional mass scaling to reach the
 desired $L_{1.4~\rmn{GHz}} \sim M_{500}^4$.
 The resulting median (mean) boost is about
-32\% (47\%) of the hadronic component.\footnote{The modeling of
+32\% (47\%) of the hadronic component.\footnote{{\bf The modeling of
    Coma and Abell~2163 suggests that a boost of about 35\% to 80\%
@@
    in turbulent, merging clusters as in \cite{2013arXiv1303.4746W},
-   the required fraction of leptonic component could be smaller.} 
+   the required fraction of leptonic component could be smaller.}} 
 The boosted population is shown in both panels of Fig.~\ref{fig:PLSZ}. The 
@@
 Additionally, we do not include the possible leptonic emission 
-component in the analysis of next sections, deferring the study of its physical 
-details and correlation to the hadronic one to future work. 
+component in the analysis of next sections, deferring the study of its 
+physical details and correlation to the hadronic one to future work. 
 The mock galaxy cluster sample used here is affected by incompleteness 
@@
 luminosity maximum that indicates our formal incompleteness limit.  
-{\bf Note that the low-frequency predictions of our model suffer from 
-the uncertainty of possible intrinsic spectral features not considered
-here (e.g. spectral steepening by CR transport, SZ decrement).}
-%Note that calibrating our model to 1.4~GHz observations may cause an over- or
-%underestimate of the number of low-frequency halos as a result of intrinsic
-%spectral steepening (e.g., due to CR transport) or steeper leptonic spectra in
-%comparison to the hadronic component in the high-mass radio-loud NCCC 
-%population, respectively.
+%{\bf Note that calibrating our model to 1.4~GHz observations may cause 
+%the uncertainty of possible intrinsic spectral features not considered
+%here (e.g. spectral steepening by CR transport, SZ decrement).}
+{\bf Note that calibrating our model to 1.4~GHz observations may cause an over- or
+underestimate of the number of low-frequency halos as a result of intrinsic
+spectral steepening (e.g., due to CR transport) or steeper leptonic spectra in
+comparison to the hadronic component in the high-mass radio-loud NCCC 
+population, respectively.} %--> still not clear to me
 
@@
 which motivates our upper redshift limit. {\bf Note also that at these high redshifts, 
-the analytical model for the evolving RLF results in spurious counts due to the 
+the analytical model for the evolving RLF gives spurious counts due to the 
 non-perfect matching with simulations in this regime.}
@@
 explained above. {\bf Comparing the left and right panel of Fig.~\ref{fig:RLF_120_flux}
-elucidate the critical impact of the detection threshold on the number observable RHs.
-Indeed, a detailed characterization of the instrumental response is needed in order
+elucidates the critical impact of the detection threshold on the number observable RHs.
+A detailed characterization of the instrumental response is needed in order
 to obtain more precise estimations.}
@@
 the hadronic contribution to the total radio emission of merging clusters. 
-{\bf In particular, the comparison with the predictions of the turbulent reaccelerating 
+{\bf In particular, the comparison with the predictions of the turbulent re-acceleration 
 scenario by \cite{2010A&A...509A..68C,2012arXiv1210.1020C}, where a significantly
-smaller number of objects is expected, will eventually help in disentangling different 
-models and in identifying the importance of the hadronic component in galaxy clusters.}
+smaller number of objects is expected to be detected, will eventually help in disentangling 
+different models and in identifying the importance of the hadronic component.}
 
@@
 
-{\bf We introduce a phenomenological realization of the additional leptonic component in an hybrid scenario,
-and show how this can affect the population of high-mass radio-loud NCCCs (radio giant halos), bringing 
-its scaling relations in agreement with the the available observational samples. However, due to the nature of 
-our approach, i.e., the use of an $N$-body simulation which is volume-limited, only few tens of objects 
-would be affected by such a correction. These are not statistically significant against our 
-whole sample and, therefore, we refrain from adding this component in the analysis
-of the luminosity functions and in making predictions for future surveys.}
+{\bf We consider an example of a phenomenological correction factor representing the 
+additional leptonic component in an hybrid scenario. We show how this can affect the 
+population of high-mass radio-loud NCCCs, i.e, the giant halos, bringing its scaling relations 
+in agreement with the the available observational samples. However, due to the nature 
+of our approach, i.e., the use of an $N$-body simulation which is volume-limited, only few 
+tens of objects would be affected by such a correction. These are not statistically significant 
+against our whole sample and, therefore, we refrain from adding this component in the 
+subsequent analysis, leaving its theoretical modeling to future work.}
 
@@
 catalogs publicly and freely available on-line through the MultiDark database (www.multidark.org). 
-Those contain the quantities $\rho_{\rmn{gas}}$, $L_{\rmn{X, bol}}$, $Y_{\rmn{X}}$, $Y_{\rmn{SZ}}$,
-$L_{120~\rmn{MHz}}$, $L_{1.4~\rmn{GHz}}$ and $L_{\gamma}$ (among many others). We hope 
-that the community can make valuable use of these catalogues in
+We hope that the community can make valuable use of these catalogues in
 synergy with the future radio, X-ray and gamma-ray data.
@@
 {\bf Note that, as explained in 
-Section~\ref{sec:5}, we refrain from use the newly published results of \cite{2013arXiv1306.3102K} 
+Section~\ref{sec:5}, we refrain from using the newly published results of \cite{2013arXiv1306.3102K} 
 on an \emph{extended} GMRT survey because they find only one additional radio 

### 2013-09-27 paper2.tex

@@
 \author[F. Zandanel, C. Pfrommer and F. Prada]{
-Fabio Zandanel$^{1,2 *}$, Christoph Pfrommer$^{3 \dagger}$ and Francisco Prada$^{4,5,1 \S}$\\
-$^{1}$Instituto de Astrof\'{\i}sica de Andaluc\'{\i}a (CSIC), Glorieta de la Astronom\'{\i}a, E-18080 Granada, Spain\\
-$^{2}$now at GRAPPA Institute, University of Amsterdam, Science Park 904, 1098XH Amsterdam, Netherlands\\
-$^{3}$Heidelberg Institute for Theoretical Studies, Schloss-Wolfsbrunnenweg 35, D-69118 Heidelberg, Germany\\
+Fabio Zandanel$^{1,2}$, Christoph Pfrommer$^{3}$ and Francisco Prada$^{4,5,1}$\\
+$^{1}$GRAPPA Institute, University of Amsterdam, Science Park 904, 1098XH Amsterdam, Netherlands, f.zandanel@uva.nl\\
+$^{2}$Instituto de Astrof\'{\i}sica de Andaluc\'{\i}a (CSIC), Glorieta de la Astronom\'{\i}a, E-18080 Granada, Spain\\
+$^{3}$Heidelberg Institute for Theoretical Studies, Schloss-Wolfsbrunnenweg 35, D-69118 Heidelberg, Germany, christoph.pfrommer@h-its.org\\
 $^{4}$Campus of International Excellence UAM+CSIC, Cantoblanco, E-28049 Madrid, Spain\\
@@
 \begin{abstract}
-  The underlying physics of giant and mini radio halos in galaxy clusters is
-  still an open question, which becomes more pressing with the growing number of
-  detections. Assuming that the radio-emitting electrons are generated in
-  hadronic cosmic ray (CR) interactions with protons of the intra-cluster medium
-  explains the radio emission in mini halos (Perseus, Ophiuchus). {\bf By contrast,
-  the hadronic model either fails to explain the extended emission of giant
-  radio halos (Coma at low frequencies) or would require a flat CR profile, 
-  realized through CR streaming and diffusion (Coma and A2163 at 1.4~GHz). 
-  We suggest that a second, leptonic component could be responsible 
-  for the missing flux in giant halos within a new hybrid scenario of which 
-  we describe possible observational consequences. We then study in
-  detail the hadronic component, including an effective parameterization of CR
-  transport, using a cosmological complete mock galaxy cluster catalog built 
-  from the MultiDark $N$-body $\Lambda$CDM simulation in a companion paper.} 
-  Because of CR transport and the different scalings of the
-  X-ray luminosity, $L_{\rmn{X}}$, and the Sunyaev-Zel'dovich flux, $Y$, with
-  gas density, our model can simultaneously reproduce the observed bimodality of
+  {\bf The underlying physics of giant and mini radio halos in galaxy clusters
+    is still an open question. We find that mini halos (such as in Perseus and
+    Ophiuchus) can be explained by radio-emitting electrons that are generated
+    in hadronic cosmic ray (CR) interactions with protons of the intra-cluster
+    medium. By contrast, the hadronic model either fails to explain the extended
+    emission of giant radio halos (as in Coma at low frequencies) or would
+    require a flat CR profile, which can be realized through outward streaming
+    and diffusion of CRs (in Coma and A2163 at 1.4~GHz).  We suggest that a
+    second, leptonic component could be responsible for the missing flux in
+    giant halos within a new hybrid scenario and we describe its possible
+    observational consequences.  To study the hadronic emission component of the
+    radio halo population statistically, we use a cosmological mock galaxy
+    cluster catalog built from the MultiDark simulation. Because of the
+    properties of CR streaming and the different scalings of the X-ray
+    luminosity ($L_{\rmn{X}}$) and the Sunyaev-Zel'dovich flux ($Y$) with gas
+    density, our model can simultaneously reproduce the observed bimodality of
     radio-loud and radio-quiet clusters at the same $L_{\rmn{X}}$ as well as the
-  unimodal distribution of radio-halo luminosity versus $Y$; thereby suggesting
-  a physical solution to this apparent contradiction. {\bf Assuming a redshift-independent
-  fraction of radio-loud clusters, we demonstrate the unique 
-  prospects for low-frequency radio surveys (such as the
-  LOFAR Tier~1 survey) to detect about $600\times\rmn{\emph{loud~fraction}[\%]}/10$ 
-  hadronically-generated giant and mini radio halos. 
-  This shows the potentially of future radio surveys in determining 
-  the generation mechanism of halos and the importance of the hadronic component in 
-  galaxy clusters, particularly at low masses which are currently unexplored.}
-  We make our cosmologically complete multi-frequency mock 
-  catalogs for the (non-)thermal cluster emission at different redshifts publicly and freely 
-  available on-line through the MultiDark database.
-%  The underlying physics of giant and mini radio halos in galaxy clusters is
-%  still an open question, which becomes more pressing with the growing number of
-%  detections. Assuming that the radio-emitting electrons are generated in
-%  hadronic cosmic ray (CR) interactions with protons of the intra-cluster medium
-%  explains the radio emission in mini halos (Perseus, Ophiuchus). By contrast,
-%  the hadronic model either fails to explain the extended emission of giant
-%  radio halos (Coma at low frequencies) or would require a flat CR profile 
-%  (Coma and A2163 at 1.4~GHz). Flat CR distributions are only expected to be realized 
-%  through CR streaming in {\em relaxed} clusters---in conflict with the observation that
-%  radio halos are hosted by merging {\em turbulent} clusters. This motivates us
-%  to propose a new hybrid model, where (i) mini halos are primarily of hadronic
-%  origin, (ii) giant halos experience a transition from central hadronic
-%  emission to peripheral leptonic emission due to Fermi I or II re-acceleration
-%  of fossil or hadronically produced electrons, and (iii) steep spectrum radio
-%  sources are mainly of leptonic origin. {\bf We use a mock galaxy cluster catalog
-%  built from the MultiDark $N$-body $\Lambda$CDM simulation that matches 
-%  Sunyaev-Zel'dovich and X-ray scaling relations and luminosity function.} 
-%  Because of CR streaming and the different scalings of the
-%  X-ray luminosity, $L_{\rmn{X}}$, and the Sunyaev-Zel'dovich flux, $Y$, with
-%  gas density, our model can simultaneously reproduce the observed bimodality of
-%  radio-loud and radio-quiet clusters at the same $L_{\rmn{X}}$ as well as the
-%  unimodal distribution of radio-halo luminosity versus $Y$; thereby suggesting
-%  a physical solution to this apparent contradiction. For a plausible fraction
-%  of 10\% radio-loud clusters, our model matches the NVSS radio-halo luminosity
-%  function. Constructing an analytical radio-halo luminosity function, we
-%  demonstrate the unique prospects for low-frequency radio surveys (such as the
-%  LOFAR Tier 1 survey) to detect $\sim3500$ radio halos back to redshift two and
-%  to probe the underlying physics of radio halos. We make our cosmologically 
-%  complete multi-frequency mock catalogs for the (non-)thermal cluster emission 
-%  at different redshifts publicly and freely available on-line
-%  through the MultiDark database.
+    unimodal distribution of radio-halo luminosity versus $Y$; thereby
+    suggesting a physical solution to this apparent contradiction. We predict
+    radio halo emission down to the mass scale of galaxy groups, which
+    highlights the unique prospects for low-frequency radio surveys (such as the
+    LOFAR Tier 1 survey) to increase the number of detected radio halos by at
+    least an order of magnitude.}
 \end{abstract}
@@
 \label{sec:1}
-
-\begingroup
-\let\thefootnote\relax\footnotetext{* f.zandanel@uva.nl}
-\let\thefootnote\relax\footnotetext{$\dagger$ christoph.pfrommer@h-its.org}
-\let\thefootnote\relax\footnotetext{$\S$ fprada@iaa.es}
-\endgroup
 
@@
 %  \citealp{2010MNRAS.406.1759M}).}
+
+% original abstract:
+
+%  The underlying physics of giant and mini radio halos in galaxy clusters is
+%  still an open question, which becomes more pressing with the growing number of
+%  detections. Assuming that the radio-emitting electrons are generated in
+%  hadronic cosmic ray (CR) interactions with protons of the intra-cluster medium
+%  explains the radio emission in mini halos (Perseus, Ophiuchus). By contrast,
+%  the hadronic model either fails to explain the extended emission of giant
+%  radio halos (Coma at low frequencies) or would require a flat CR profile 
+%  (Coma and A2163 at 1.4~GHz). Flat CR distributions are only expected to be realized 
+%  through CR streaming in {\em relaxed} clusters---in conflict with the observation that
+%  radio halos are hosted by merging {\em turbulent} clusters. This motivates us
+%  to propose a new hybrid model, where (i) mini halos are primarily of hadronic
+%  origin, (ii) giant halos experience a transition from central hadronic
+%  emission to peripheral leptonic emission due to Fermi I or II re-acceleration
+%  of fossil or hadronically produced electrons, and (iii) steep spectrum radio
+%  sources are mainly of leptonic origin. {\bf We use a mock galaxy cluster catalog
+%  built from the MultiDark $N$-body $\Lambda$CDM simulation that matches 
+%  Sunyaev-Zel'dovich and X-ray scaling relations and luminosity function.} 
+%  Because of CR streaming and the different scalings of the
+%  X-ray luminosity, $L_{\rmn{X}}$, and the Sunyaev-Zel'dovich flux, $Y$, with
+%  gas density, our model can simultaneously reproduce the observed bimodality of
+%  radio-loud and radio-quiet clusters at the same $L_{\rmn{X}}$ as well as the
+%  unimodal distribution of radio-halo luminosity versus $Y$; thereby suggesting
+%  a physical solution to this apparent contradiction. For a plausible fraction
+%  of 10\% radio-loud clusters, our model matches the NVSS radio-halo luminosity
+%  function. Constructing an analytical radio-halo luminosity function, we
+%  demonstrate the unique prospects for low-frequency radio surveys (such as the
+%  LOFAR Tier 1 survey) to detect $\sim3500$ radio halos back to redshift two and
+%  to probe the underlying physics of radio halos. We make our cosmologically 
+%  complete multi-frequency mock catalogs for the (non-)thermal cluster emission 
+%  at different redshifts publicly and freely available on-line
+%  through the MultiDark database.

### 2013-09-30 paper2.tex
paper 2 corrected

@@
 
-%\newcommand{\rmn}{\mathrm}
+\usepackage{graphicx}
+\usepackage{natbib}
+\usepackage{txfonts}
+\usepackage[usenames,dvips]{color}
+\newcommand\qc[1]{{\color{red} \bf #1}}
+
 \newcommand{\CR}{\mathrm{CR}}
@@
 \newcommand{\vel}{\upsilon}
-%
-\usepackage{graphicx}
-\usepackage{natbib}
-%
-\usepackage{txfonts}
 
@@
 \author[F. Zandanel, C. Pfrommer and F. Prada]{
-Fabio Zandanel$^{1,2}$, Christoph Pfrommer$^{3}$ and Francisco Prada$^{4,5,1}$\\
+Fabio Zandanel$^{1,2}$, Christoph Pfrommer$^{3}$ and Francisco Prada$^{4,5,2}$\\
 $^{1}$GRAPPA Institute, University of Amsterdam, Science Park 904, 1098XH Amsterdam, Netherlands, f.zandanel@uva.nl\\
@@
     and diffusion of CRs (in Coma and A2163 at 1.4~GHz).  We suggest that a
-    second, leptonic component could be responsible for the missing flux in
-    giant halos within a new hybrid scenario and we describe its possible
-    observational consequences.  To study the hadronic emission component of the
-    radio halo population statistically, we use a cosmological mock galaxy
-    cluster catalog built from the MultiDark simulation. Because of the
-    properties of CR streaming and the different scalings of the X-ray
+    second, leptonic component could be responsible for the missing flux in the
+    outer parts of giant halos within a new hybrid scenario and we describe its
+    possible observational consequences.  To study the hadronic emission
+    component of the radio halo population statistically, we use a cosmological
+    mock galaxy cluster catalog built from the MultiDark simulation. Because of
+    the properties of CR streaming and the different scalings of the X-ray
     luminosity ($L_{\rmn{X}}$) and the Sunyaev-Zel'dovich flux ($Y$) with gas
@@
 
-{\bf The presence of large-scale diffuse radio synchrotron emission in clusters of
-galaxies proves the existence of relativistic electrons and magnetic fields
-permeating the intra-cluster medium (ICM). Diffuse cluster radio emission can be
-separated in two classes: radio halos and radio relics (see, e.g., 
-\citealp{2012A&ARv..20...54F}).  Radio \mbox{(mini-)}halos (RHs) are centered 
-on clusters and characterized by a regular and unpolarized morphology, resembling 
-the morphology of the thermal X-ray emission.}
+{\bf The presence of large-scale diffuse radio synchrotron emission in clusters
+  of galaxies proves the existence of relativistic electrons and magnetic fields
+  permeating the intra-cluster medium (ICM). This diffuse cluster radio emission
+  can be observationally classified into two phenomena: peripheral radio relics,
+  which show irregular morphology and polarized emission and appear to trace
+  merger and accretion shocks, as well as radio halos (see, e.g.,
+  \citealp{2012A&ARv..20...54F}).  Radio \mbox{(mini-)}halos (RHs) are
+  characterized by unpolarized radio emission, are centered on clusters and
+  show a regular morphology, resembling the morphology of the thermal X-ray
+  emission. However, the short cooling length of synchrotron-emitting electrons
+  at GHz frequencies ($\lesssim 100$~kpc) challenges theoretical model to
+  explain the large-scale radio emission that extends over several Mpcs and
+  calls for an efficient in-site acceleration process of electrons.}
 
@@
 the mass ratio and therefore can accumulate in clusters for cosmological times
-\citep{1996SSRv...75..279V}. Indeed, CR electrons suffer more severe energy
+\citep{1996SSRv...75..279V}. In contrast, CR electrons suffer more severe energy
 losses via synchrotron and inverse Compton emission at particle energies $E
@@
 RHs can be divided in two classes. Giant radio halos are typically associated
-with merging clusters and have large extensions, e.g., the Coma RH has
-an extension of about 2~Mpc. Radio mini-halos are associated with relaxed
-clusters that harbor a cool core and typically extend over a few hundred
-kilo-parsecs, e.g., the Perseus radio mini-halo has an extension of about
-0.2~Mpc.  The observed morphological similarities with the thermal X-ray
-emission suggests that RHs may be of hadronic origin. In fact, cool-core
-clusters (CCCs) are characterized by high thermal X-ray emissivities and ICM
-densities that are more peaked in comparison to (merging) non cool-core clusters
-(NCCCs) (e.g., \citealp{2008A&A...487..431C}). This distinct difference in the
-ICM density structure of CCCs and NCCCs would be reflected in the morphology 
-of the two observed classes of RHs.
+with merging clusters and have large extensions, e.g., the Coma RH has an
+extension of about 2~Mpc. Radio mini-halos are associated with relaxed clusters
+that harbor a cool core and typically extend over a few hundred kilo-parsecs,
+e.g., the Perseus radio mini-halo has an extension of about 0.2~Mpc.  The
+observed morphological similarities with the thermal X-ray emission suggests
+that RHs may be of hadronic origin. In fact, cool-core clusters (CCCs) are
+characterized by high thermal X-ray emissivities and ICM densities that are more
+peaked in comparison to non cool-core clusters (NCCCs) that often show
+signatures of cluster mergers (e.g., \citealp{2008A&A...487..431C}). This
+distinct difference in the ICM density structure of CCCs and NCCCs would be
+reflected in the morphology of the two observed classes of RHs.
 
 The RH luminosity seems to be correlated to the thermal X-ray luminosity (e.g.,
-\citealp{2009A&A...507..661B,2011A&A...527A..99E}). However, a large fraction
-of clusters does not exhibit significant diffuse synchrotron emission at current
-sensitivity limits. Instead, stacking subsamples of luminous X-ray clusters
-reveals a signal of extended diffuse radio emission that is below
-the radio upper limits on individual clusters \citep{2011ApJ...740L..28B}
-suggesting that at least a subset of apparently ``radio-quiet'' clusters shows a
-low-level diffuse emission. Galaxy clusters with the same thermal X-ray
-luminosity show an apparent bimodality with respect to their radio
-luminosity. 
-%5Either they harbor a RH or they do not have any detectable diffuse
-%radio emission \citep{2009A&A...507..661B,2011A&A...527A..99E}. 
-This suggests the existence of a switch-on/switch-off mechanism that is able to change the
-radio luminosity by more than one order of magnitude.  While such a mechanism
-could be easily realized in the framework of the re-acceleration model
+\citealp{2009A&A...507..661B,2011A&A...527A..99E}). However, a large fraction of
+clusters does not exhibit significant diffuse synchrotron emission at current
+sensitivity limits. Stacking subsamples of luminous X-ray clusters reveals a
+signal of extended diffuse radio emission that is below the radio upper limits
+on individual clusters \citep{2011ApJ...740L..28B} suggesting that at least a
+subset of apparently ``radio-quiet'' clusters shows a low-level diffuse
+emission. Galaxy clusters with the same thermal X-ray luminosity show an
+apparent bimodality with respect to their radio luminosity.  This suggests the
+existence of a switch-on/switch-off mechanism that is able to change the radio
+luminosity by more than one order of magnitude.  While such a mechanism could be
+easily realized in the framework of the re-acceleration model
 \citep{2009A&A...507..661B}, the \emph{classical} hadronic model predicts the
@@
 spectral features observed in clusters, such as the total spectral (convex)
-curvature claimed in the Coma RH or the spectral steepening observed at
-the boundary of some RHs. 
-%However, the recent report of spectral flattening with
-%frequency of the RH in A2256 \citep{2012A&A...543A..43V} could easily be
-%accommodated in the hadronic model, which naturally produces such a concave
-%spectrum \citep{2010MNRAS.409..449P}. 
-%This raises the interesting question
-%whether such a variability among different sources that are generally classified
-%as `radio halos' signals the presence of richer underlying physics---a question
-%that we will address in this paper.
-
-\cite{2011A&A...527A..99E} tried to asses these problems of the classical hadronic 
-model by analyzing CR transport processes within a cluster. While CR advection with 
-turbulently driven flows results in centrally enhanced CR profiles, the propagation in 
-form of CR streaming and diffusion produces a flattening of CR profiles. Hence, 
-different CR transport phenomena may also account for the observed bimodality 
-of the radio luminosity in the hadronic model and may also explain the spectral 
-features observed in some clusters. {\bf This has been recently confirmed 
-by \cite{2013arXiv1303.4746W}. In particular, they show that when considering turbulent
-damping, CRs can stream at super-Alfvenic velocities.} 
-Note that these phenomena were not considered in earlier analytical works 
-(e.g., \citealp{2004A&A...413...17P}) as well as in previous hydrodynamic 
-simulations (e.g., \citealp{2001ApJ...562..233M, 
-2008MNRAS.385.1211P, 2010MNRAS.409..449P}).
-{\bf A satisfactory theory of CR transport in clusters does not exist yet, 
-however CR streaming and diffusion may represent an intriguing solution
-for the issues of the classical hadronic model.}
+curvature claimed in the Coma RH or the spectral steepening observed at the
+boundary of some RHs.  However, the recent report of spectral flattening with
+frequency of the RH in A2256 \citep{2012A&A...543A..43V} could easily be
+accommodated in the hadronic model, which naturally produces such a concave
+spectrum \citep{2010MNRAS.409..449P}.  This raises the interesting question
+whether such a variability among different sources that are generally classified
+as ``radio halos'' signals the presence of richer underlying physics---a question
+that we will address in this paper.
+
+\cite{2011A&A...527A..99E} tried to asses these problems of the classical
+hadronic model by analyzing CR transport processes within a cluster. While CR
+advection with turbulently driven flows results in centrally enhanced CR
+profiles, the propagation in form of CR streaming and diffusion produces a
+flattening of CR profiles. Hence, different CR transport phenomena may also
+account for the observed bimodality of the radio luminosity in the hadronic
+model and may also explain the spectral features observed in some clusters. {\bf
+  This has been recently confirmed by \cite{2013arXiv1303.4746W}. In particular,
+  by considering turbulent damping, they show that CRs can stream at
+  super-Alfv{\'e}nic velocities.}  Note that these phenomena were not considered in
+earlier analytical works (e.g., \citealp{2004A&A...413...17P}) as well as in
+previous hydrodynamic simulations (e.g., \citealp{2001ApJ...562..233M,
+  2008MNRAS.385.1211P, 2010MNRAS.409..449P}).  {\bf A satisfactory theory of CR
+  transport in clusters does not yet exist. However, CR streaming and diffusion
+  may represent an intriguing solution for the issues of the classical hadronic
+  model.}
 
@@
 without being able to detect cluster gamma-ray emission. Current gamma-ray
-limits enable us to constrain the average CR-to-thermal pressure to be less than a few
-percent, and the maximum CR acceleration efficiency at structure formation shocks 
-to be $<50\%$. Alternatively, this may indeed suggest the presence of non-negligible 
-CR transport processes into the outer cluster regions. 
-%significant constraints on the relative CR pressure contribution. 
-%The long observational campaign of the Perseus galaxy cluster
-%performed by the Major Atmospheric Gamma-ray Cherenkov (MAGIC) telescopes
-%constrains the cluster average CR-to-thermal pressure to be less than a few
-%percent \citep{2010ApJ...710..634A,2011arXiv1111.5544M}. Comparing the
-%corresponding upper limits to predictions of simulations by
-%\cite{2010MNRAS.409..449P} constrains the maximum CR acceleration efficiency at
-%structure formation shocks to be $<50\%$.  Alternatively, this may indeed
-%suggest the presence of non-negligible CR transport processes into the outer
-%cluster regions as suggested by \cite{2011A&A...527A..99E}.  Constraints at the
-%same level are confirmed by the \emph{Fermi}-Large Area Telescope (LAT) data on
-%the Coma cluster \citep{2011arXiv1105.3240P,2012AAS...21920701Z,
-%2012...VERITAS,2012arXiv1207.6749H}. To summarize, gamma-ray observations are 
-%not yet sensitive enough to severely challenge hadronic models of RHs.
+limits enable us to constrain the average CR-to-thermal pressure to be less than
+a couple percent, and the maximum CR acceleration efficiency at structure
+formation shocks to be $<50$ per cent. Alternatively, this may indeed suggest the
+presence of non-negligible CR transport processes into the outer cluster
+regions.
 
@@
 question of the RH frequency in clusters \citep{1999NewA....4..141G,
-  VenturiGMRT_2,2013arXiv1306.3102K}. Since the number of RHs in such X-ray flux-limited samples is
-small with typically a few RHs, the conclusions on the underlying physical
-mechanisms of RHs are not very robust. Fortunately, this is expected to change
-thanks to the next-generation of low-frequency radio observatories such as the
-Low Frequency Array (LOFAR).\footnote{www.lofar.org} In fact, a deep cluster
-survey is part of the LOFAR science key projects and expected to provide a large
-number of radio-emitting galaxy clusters up to redshift $z\approx1$
-\citep{2012JApA..tmp...34R}. This will hopefully permit
-to clearly determine the RH phenomenology with respect to cluster properties
-such as the fractions of radio-loud/quiet, non cool-core/cool-core, and
+  VenturiGMRT_2,2013arXiv1306.3102K}. Since the number of RHs in such X-ray
+flux-limited samples is small with typically a few RHs, the conclusions on the
+underlying physical mechanisms of RHs are not very robust. Fortunately, this is
+expected to change thanks to the next-generation of low-frequency radio
+observatories such as the Low Frequency Array (LOFAR).\footnote{www.lofar.org}
+In fact, a deep cluster survey is part of the LOFAR science key projects and
+expected to provide a large number of radio-emitting galaxy clusters up to
+redshift $z\approx1$ \citep{2012JApA..tmp...34R}. This will hopefully permit to
+clearly determine the RH phenomenology with respect to cluster properties such
+as the fractions of radio-loud/quiet, non cool-core/cool-core, and
 non-merging/merging clusters, and to explore the role of different parameters
@@
 
-{\bf The main scope of this work is to upgrade the classical hadronic model with
-the inclusion of possible CR transport phenomena, and to make predictions for
-future radio surveys. The outline is as follows. In Section~\ref{sec:2.3}, we 
-construct a model for the CR proton distribution in clusters that merges results 
-of hydrodynamic cluster simulations and an analytical model for microscopic 
-CR transport processes. In Section~\ref{sec:3}, we model observed surface 
-brightness profiles of individual RHs within the hadronic scenario and explore the 
-allowable parameter space for CRs and magnetic fields. Motivated by immanent 
-challenges to explain the extent of giant radio halos within the hadronic model, 
-we suggest a new hybrid leptonic/hadronic scenario meant to unify the apparently 
-distinct classes of giant radio halos, mini halos, and steep spectrum radio sources in 
-Section~\ref{sec:discussion_hadronic}. In Section~\ref{sec:4}, we apply our
-extended hadronic model to a cosmologically complete mock galaxy cluster 
-catalog built from the MultiDark $N$-body $\Lambda$CDM simulation
-in \cite{paper1}, hereafter Paper~I. 
-We compare the resulting modeled radio-to-X-ray and radio-to-SZ
-scaling relations to current observations and show how they vary for different
-choices of our CR and magnetic field parametrizations. In Section~\ref{sec:5}, we show
-the radio luminosity functions, compare them to current observational
-constraints, and provide predictions of the hadronically-generated
-RHs for the LOFAR cluster survey. Finally, in Section~\ref{sec:6}, we present 
-our conclusions.} In this work, the cluster mass
-$M_{\Delta}$ and radius $R_{\Delta}$ are defined with respect to a density that
-is $\Delta=200$ or $\Delta=500$ times the \emph{critical} density of the
-Universe. We adopt density parameters of $\Omega_{\rmn{m}}=0.3$,
-$\Omega_{\Lambda}=0.7$ and today's Hubble constant of $H_0 = 100 \times
-h_{70}$~km~s$^{-1}$~Mpc$^{-1}$ where $h_{70} = 0.7$.
+{\bf The main scope of this work is to account for CR transport processes in the
+  classical hadronic model and to provide forecasts for future radio
+  surveys. The outline is as follows. In Section~\ref{sec:2.3}, we construct a
+  model for the CR proton distribution in clusters that merges results of
+  hydrodynamic cluster simulations and an analytical model for microscopic CR
+  transport processes. In Section~\ref{sec:3}, we model observed surface
+  brightness profiles of individual RHs within the hadronic scenario and explore
+  the allowable parameter space for CRs and magnetic fields. Motivated by
+  immanent challenges to explain the extent of giant radio halos within the
+  hadronic model, we suggest a new hybrid leptonic/hadronic scenario meant to
+  unify the apparently distinct classes of giant radio halos, mini halos, and
+  steep spectrum radio sources in Section~\ref{sec:discussion_hadronic}. In
+  Section~\ref{sec:4}, we apply our extended hadronic model to a cosmologically
+  complete mock galaxy cluster catalog built from the MultiDark $N$-body
+  $\Lambda$CDM simulation in \cite{paper1}, hereafter Paper~I.  We compare the
+  resulting modeled radio-to-X-ray and radio-to-SZ scaling relations to current
+  observations and show how they vary for different choices of our CR and
+  magnetic field parametrizations. In Section~\ref{sec:5}, we show the radio
+  luminosity functions, compare them to current observational constraints, and
+  provide predictions of the hadronically-generated RHs for the LOFAR cluster
+  survey. Finally, in Section~\ref{sec:6}, we present our conclusions.} In this
+work, the cluster mass $M_{\Delta}$ and radius $R_{\Delta}$ are defined with
+respect to a density that is $\Delta=200$ or $500$ times the
+\emph{critical} density of the Universe. We adopt density parameters of
+$\Omega_{\rmn{m}}=0.3$, $\Omega_{\Lambda}=0.7$ and today's Hubble constant of
+$H_0 = 100 \, h_{70}$~km~s$^{-1}$~Mpc$^{-1}$ where $h_{70} = 0.7$.
 
@@
 p=C(R) p^{-\alpha} \dd p$, which is the effective one-dimensional momentum
-distribution (assuming isotropy in momentum space). {\bf We are interested 
-in calculating the radio synchrotron and gamma-ray emission resulting from 
-secondaries of hadronic CR interactions with protons of the ICM (see
-Appendix~\ref{app:A} and Appendix~\ref{app:C} for the details).}
-
-The spatial CR distribution $C(R)$ within a galaxy cluster is governed by an interplay
-of CR advection, streaming, and diffusion. The advection of CRs by turbulent gas
-motions is dominated by the largest eddy turnover time $\tau_{\rmn{tu}}\sim
-L_{\rmn{tu}}/ \vel_{\rmn{tu}}$. Here, $L_{\rmn{tu}}$ denotes the turbulent
-injection scale (typically of order the core radius) and $\vel_{\rmn{tu}}$ is
-the associated turbulent velocity that approaches the sound speed
-$\vel_{\rmn{s}}$ for transsonic turbulence after a cluster merger and relaxes to
-small velocities afterwards. As a result of advection into the dense cluster
-atmosphere, CRs are adiabatically compressed and experience a stratified
-distribution in the cluster potential. The gradient of the CR number density
-leads to a net CR streaming motion towards the cluster outskirts. Streaming CRs
-excite Alfv{\'e}n waves on which they resonantly scatter
-\citep{1969ApJ...156..445K}. This isotropizes the CRs' pitch angles, and thereby
-reduces the CR bulk speed. Balancing the growth rate of the CR Alfv{\'e}n wave
-instability with the wave damping rate due to non-linear Landau damping yields a
-CR streaming speed of order the Alfv{\'e}n speed \citep{2001ApJ...553..198F}.
-This increases considerably when balancing it with the turbulent damping rate,
-which implies an inverse scaling with the CR number density \citep{2013arXiv1303.4746W}.
-Once CR streaming depletes the CR number density, this causes a
-run-away process with a rapidly increasing streaming speed that even surpasses
-the sound speed because the smaller CR number density drives the CR Alfv{\'e}n
-wave instability less efficiently. Hence, the crossing time of streaming CRs
-over $L_{\rmn{tu}}$ is $\tau_{\rmn{st}}\sim \chi_B\,L_{\rmn{tu}}/
-\vel_{\rmn{st}}$ with the streaming velocity given by $\vel_{\rmn{st}}\sim
-\vel_{\rmn{s}}$ and $\chi_B\lesssim 1$ parametrizes the magnetic bending scale.
-Magnetic bottlenecks for the macroscopic, diffusive CR transport, are critical
-in lowering the microscopic streaming velocity of CR by some finite
-factor. Therefore, we can define a turbulent propagation parameter
+distribution (assuming isotropy in momentum space). The spatial CR distribution
+$C(R)$ within a galaxy cluster is governed by an interplay of CR advection,
+streaming, and diffusion. The advection of CRs by turbulent gas motions is
+dominated by the largest eddy turnover time $\tau_{\rmn{tu}}\sim L_{\rmn{tu}}/
+\vel_{\rmn{tu}}$. Here, $L_{\rmn{tu}}$ denotes the turbulent injection scale
+(typically of order the core radius) and $\vel_{\rmn{tu}}$ is the associated
+turbulent velocity that approaches the sound speed $\vel_{\rmn{s}}$ for
+transsonic turbulence after a cluster merger and relaxes to small velocities
+afterwards. As a result of advection into the dense cluster atmosphere, CRs are
+adiabatically compressed and experience a stratified distribution in the cluster
+potential. The gradient of the CR number density leads to a net CR streaming
+motion towards the cluster outskirts. Streaming CRs excite Alfv{\'e}n waves on
+which they resonantly scatter \citep{1969ApJ...156..445K}. This isotropizes the
+CRs' pitch angles, and thereby reduces the CR bulk speed. Balancing the growth
+rate of the CR Alfv{\'e}n wave instability with the wave damping rate due to
+non-linear Landau damping yields a CR streaming speed of order the Alfv{\'e}n
+speed \citep{2001ApJ...553..198F}.  This increases considerably when balancing
+it with the turbulent damping rate, which implies an inverse scaling with the CR
+number density \citep{2013arXiv1303.4746W}.  Once CR streaming depletes the CR
+number density, this causes a run-away process with a rapidly increasing
+streaming speed that even surpasses the sound speed because the smaller CR
+number density drives the CR Alfv{\'e}n wave instability less
+efficiently. Hence, the crossing time of streaming CRs over $L_{\rmn{tu}}$ is
+$\tau_{\rmn{st}}\sim \chi_B\,L_{\rmn{tu}}/ \vel_{\rmn{st}}$ with the streaming
+velocity given by $\vel_{\rmn{st}}\sim \vel_{\rmn{s}}$ and $\chi_B\lesssim 1$
+parametrizes the magnetic bending scale.  Magnetic bottlenecks for the
+macroscopic, diffusive CR transport, are critical in lowering the microscopic
+streaming velocity of CR by some finite factor. Therefore, we can define a
+turbulent propagation parameter
 \begin{equation}
@@
 cosmological hydrodynamical simulation of clusters \citep{2010MNRAS.409..449P},
-which however did not account for CR transport. {\bf To include the latter, we adapt 
-the analytical formalism from \citet{2011A&A...527A..99E}. This yields a model that includes 
-the necessary CR transport physics and is able to predict radio and gamma-ray 
-emission. Note that this approach is not fully self-consistent and points to
-the necessity of future hydrodynamical simulations to include the effect of CR
-streaming and diffusion on the CR spectrum.}
+which however did not account for CR transport. {\bf To include the latter, we
+  adapt the analytical formalism of \citet{2011A&A...527A..99E}. This results in
+  a model that includes the necessary CR transport physics and is able to
+  predict radio and gamma-ray emission. Note that this approach is not fully
+  self-consistent and points to the necessity of future hydrodynamical
+  simulations to include the effect of CR streaming and diffusion on the CR
+  spectrum.}
 
@@
 {\bf To construct such a model, we have to generalize the approach proposed by
-\citet{2011A&A...527A..99E}, which uses a $\beta$-profile gas parameterization, 
-in order to account for different kind of ICM gas profiles, such as our generalized 
-Navarro-Frank-White (GNFW) ICM profiles derived in Paper~I from X-ray observations.} 
-We also have to include the cluster mass-scaling of the
-CR normalization obtained from simulations \citep{2010MNRAS.409..449P}. While
-details are given in Appendix~\ref{app:B}, we show below the main steps. When
-turbulent advection completely dominates the CR transport, the CR normalization
-can be written as \citep{2011A&A...527A..99E}
+  \citet{2011A&A...527A..99E}, which uses a $\beta$-profile gas
+  parametrisation, in order to account for different ICM gas profiles, such as
+  our generalized Navarro-Frank-White (GNFW) ICM profiles derived in Paper~I
+  from X-ray observations.}  We also have to include the cluster mass-scaling of
+the CR normalization obtained from simulations
+\citep{2010MNRAS.409..449P}. While details are given in Appendix~\ref{app:B}, we
+summarize below the main steps. When turbulent advection completely dominates the CR
+transport, the CR normalization can be written as \citep{2011A&A...527A..99E}
 \begin{equation}
@@
 \end{equation} 
-Here, $\rho_{\rmn{gas}}$ is the ICM gas density and $\tilde{C}(R)$ is the normalization 
-CR profile of equation~(22) of \cite{2010MNRAS.409..449P}. We additionally account for the 
-temperature decline toward the cluster periphery, $T(R)$, given by the fit to the universal
+Here, $\rho_{\rmn{gas}}$ is the ICM gas density and $\tilde{C}(R)$ is the
+normalization of the CR profile of equation~(22) of
+\cite{2010MNRAS.409..449P}. We additionally account for the temperature decline
+toward the cluster periphery, $T(R)$, given by the fit to the universal
 temperature profile obtained from cosmological hydrodynamical simulations
@@
 observations \citep{2005ApJ...628..655V}. Eventually, the CR profile in our
-extended model is $C(R)=C_{0}(\rho_{\rmn{CR}}(R) /
-\rho_{\rmn{CR},0})^{\beta_{\rmn{CR}}}$ within $R_{\pm}$ of
-equation~(\ref{eq:Rpm}), with $\rho_{\rmn{CR}}$ defined by
-equation~(\ref{eg:rhoCR_1}) where $C_{\rmn{extended}}$ enters through our
-redefinition of $\eta$, and $C(R) = C(R_{\pm})$ for $R > R_{+}$ and $R < R_{-}$,
-respectively.
+extended model is given by
+\begin{equation}
+C(R)=C_{0}\left(\frac{\rho_{\rmn{CR}}(R)}{\rho_{\rmn{CR},0}}\right)^{\beta_{\rmn{CR}}},
+\label{eq:Cf2}
+\end{equation} 
+which is valid within $R_{\pm}$ (equation~\ref{eq:Rpm}), with
+$\rho_{\rmn{CR}}$ defined by equation~(\ref{eg:rhoCR_1}) where
+$C_{\rmn{extended}}$ enters through our redefinition of $\eta$, and $C(R) =
+C(R_{\pm})$ for $R > R_{+}$ and $R < R_{-}$, respectively.
 
@@
 power-law CR populations with spectral indices of
-$\alpha_{i}=(2.15,2.3,2.55)$. {\bf Our formalism can be easily extended to account
-for multiple CR populations by extending the terms with a single $\alpha$ to
-sums over the three spectral indices (\citealp{2010MNRAS.409..449P}, see
-Appendix~\ref{app:A}). 
-%This extension has to be applied to $A_{\nu}$, to the factor $(\epsilon_{\rmn{B}}(R)/
-%\epsilon_{B_{\rmn{c}}})^{(\alpha-2)/4}$ of equation~(\ref{eq:jnu}), and to
-%equation~(\ref{eq:Csimple_1}). 
-%While the modifications are straight forward in
-%the first two cases (and are adopted for our extended model,
-%Appendix~\ref{app:A}), 
-However, introducing a sum over $\alpha_{i}$ in
-equation~(\ref{eq:Csimple_1}) would make impossible to solve analytically for
-$\eta(R)$ in equation~(\ref{eq:eta}).} For simplicity, we decided to only use
-$\alpha = 2.3$ in this last case.\footnote{We checked that the choice of
-  $\alpha$ in equation~(\ref{eq:Csimple_1}) has only a minor effect on the
-  results. Varying $\alpha$ within $2.15-2.55$ leaves the radial shape and the
-  normalization unchanged within $0.5\%$.} For the highly turbulent cases, i.e.,
-for $\gamma_{\rmn{tu}}=100$ (1000), we recover the radial shape and
-normalization of the semi-analytical model of \cite{2010MNRAS.409..449P} within
-$1\%$ ($0.1\%$).
+$\alpha_{i}=(2.15,2.3,2.55)$. {\bf Our formalism can be easily extended to
+  account for multiple CR populations by extending the terms with a single
+  $\alpha$ to sums over the three spectral indices
+  (\citealp{2010MNRAS.409..449P}, see Appendix~\ref{app:A}). However,
+  introducing a sum over $\alpha_{i}$ in equation~(\ref{eq:Csimple_1}) would
+  make it impossible to solve analytically for $\eta(R)$ in
+  equation~(\ref{eq:eta}).} For simplicity, we decided to only use $\alpha =
+2.3$ in this last case.\footnote{We checked that the choice of $\alpha$ in
+  equation~(\ref{eq:Csimple_1}) has only a minor effect on the results. Varying
+  $\alpha$ within $2.15-2.55$ yields a similar radial shape and normalization
+  within 0.5 per cent.} For the highly turbulent cases, i.e., for
+$\gamma_{\rmn{tu}}=100$ (1000), we recover the radial shape and normalization of
+the semi-analytical model of \cite{2010MNRAS.409..449P} within 1 per cent (0.1
+per cent).
 
@@
 In the right panel of Fig.~\ref{fig:CRFinalModel}, we compare our extended model
-profile with the semi-analytical advection-only case (adopting our GNFW gas
-profiles and the outer temperature decrease to the model proposed by
+profile with the semi-analytical {\em advection-only case} (adopting our GNFW
+gas profiles and the outer temperature decrease to the model proposed by
 \citealp{2010MNRAS.409..449P}) and with the exact analytical solution as in
@@
 for details).  The profiles are normalized at $0.1 R_{200}$. In the case of
-dominant advective CR transport, our extended model compares nicely with the
+dominant advective CR transport, our extended model is an excellent match to the
 semi-analytical model derived from cosmological cluster simulations
-\citep{2010MNRAS.409..449P}.  The main differences between our extended model (and
-the semi-analytical model) on the one side and the analytical solution on the
-other side is the inclusion of the simulation-based ``reference'' profile
+\citep{2010MNRAS.409..449P}.  The main differences between our extended model
+(and the semi-analytical model) on the one side and the analytical solution on
+the other side is the inclusion of the simulation-based ``reference'' profile
 $\tilde{C}$ for the advection-only case and the universally observed temperature
@@
 In this section, we apply our model to reproduce the emission characteristics of
-four well-observed RHs.
-%
-{\bf We provide the synchrotron emissivity $j_{\nu}$, at frequency $\nu$ and 
-per steradian, in Appendix~\ref{app:A}.
-% 
-The radio surface brightness $S_{\nu}(R_{\perp})$ (in the small-angle approximation) and
+four well-observed RHs.  {\bf We provide the synchrotron emissivity $j_{\nu}$,
+  at frequency $\nu$ and per steradian, in Appendix~\ref{app:A}.  The radio
+  surface brightness $S_{\nu}(R_{\perp})$ (in the small-angle approximation) and
   luminosity $L_{\nu}$, at a given frequency $\nu$, are given by
@@
 
-For the purpose of this section, we adopt the
-measured gas and temperature profiles derived from X-ray observations of each cluster.  
-Our extended model includes an overall normalization $g_{\rmn{CR}}$ of the CR
-distribution function and the hadronically-induced non-thermal emission 
-(Appendix~\ref{app:A}). Note that
-this parameter can be interpreted as a functional that depends on the
-\emph{maximum CR acceleration efficiency}, $g(\zeta_{\rmn{p,max}})$,
-but \emph{only} for $\gamma_{\rmn{tu}}\gtrsim100$ \citep{2010MNRAS.409..449P}.
+For the purpose of this section, we adopt the measured gas and temperature
+profiles derived from X-ray observations of each cluster.  Our extended model
+includes an overall normalization $g_{\rmn{CR}}$ of the CR distribution function
+and the hadronically-induced non-thermal emission (Appendix~\ref{app:A}). Note
+that this parameter can be interpreted as a functional that depends on the
+\emph{maximum CR acceleration efficiency}, $g(\zeta_{\rmn{p,max}})$, but
+\emph{only} for $\gamma_{\rmn{tu}}\gtrsim100$ \citep{2010MNRAS.409..449P}. We
+will additionally study the CR-to-thermal pressure $X_{\rmn{CR}}=
+P_{\rmn{CR}}/P_{\rmn{th}}$, where the CR pressure is given by
+\begin{equation}
+  \label{eq:PCR}
+  P_{\rmn{CR}}=\frac{g_{\rmn{CR}} C m_{\rmn{p}} c^{2}}{6}
+  \sum_{i=1}^{3} \Delta_{i} \mathcal{B}_{1/(1+q^2)} \left(
+    \frac{\alpha_{i}-1}{2},\frac{3-\alpha_{i}}{2} \right).
+\end{equation}
+Here, $c$ is the speed of light, $\mathcal{B}_x(a,b)$ denotes the incomplete beta
+function, $q=0.8$ is the low-momentum cutoff of the CR distribution, and the
+normalization factors of the individual CR populations are given by $\Delta_{i}
+= (0.767, 0.143, 0.0975)$ \citep[][see also
+Appendix~\ref{app:A}]{2010MNRAS.409..449P}.
 
@@
 \citep[][and references therein]{2010A&A...513A..30B, 2011A&A...529A..13K}.}
-
-We will additionally study the CR-to-thermal
-pressure $X_{\rmn{CR}}=P_{\rmn{CR}}/P_{\rmn{th}}$, where the CR pressure is
-given by
-\begin{equation}
-  \label{eq:PCR}
-  P_{\rmn{CR}}=\frac{g_{\rmn{CR}} C m_{\rmn{p}} c^{2}}{6}
-  \sum_{i=1}^{3} \Delta_{i} \mathcal{B}_{1/(1+q^2)} \left(
-    \frac{\alpha_{i}-1}{2},\frac{3-\alpha_{i}}{2} \right).
-\end{equation}
-Here, $c$ is the speed of light, $q=0.8$ is the low-momentum cutoff of the CR
-distribution, and the normalization factors of the individual CR populations are
-given by $\Delta_{i} = (0.767, 0.143, 0.0975)$ \citep[][see also
-Appendix~\ref{app:A}]{2010MNRAS.409..449P}.
 
@@
 To assess the ability of our extended hadronic model to fit the observed surface
-brightness profiles, we scan our physically motivated parameter space. {\bf The free 
-parameters are the magnetic field ($B_0$, $ \alpha_{\rmn{B}}$), 
-$\gamma_{\rmn{tu}}$, and the CR acceleration efficiency.} Generally, the normalization 
-of the magnetic profile, $B_0$, and the CR acceleration efficiency function, $g_{\rmn{CR}}$, 
-determine the overall normalization of the emission. The radial decline of the magnetic field,
-$ \alpha_{\rmn{B}}$, and the turbulent CR propagation parameter, $\gamma_{\rmn{tu}}$, both
-determine the shape of the radio profile and, hence, are also degenerate. 
-%By scanning the allowed parameter space and asserting Bayesian priors that rely on
-%observational constraints and theoretical considerations about likely parameter
-%combinations for certain classes (mini halos versus giant halos), we will draw
-%conclusions on the applicability of the hadronic model for RHs.  
-In Fig.~\ref{fig:SBmodeling}, we show the surface brightness and CR-to-thermal
-pressure profiles of each cluster together with the allowed $\gamma_{\rmn{tu}}-\alpha_{B}$ parameter space. 
-All these clusters are modeled at 1.4~GHz and within $R_{200}$, unless differently specified.
+brightness profiles, we scan our physically motivated parameter space. {\bf The
+  free parameters are the magnetic field (parametrized by $B_0$ and $
+  \alpha_{\rmn{B}}$), the turbulent CR propagation parameter
+  ($\gamma_{\rmn{tu}}$) and the CR acceleration efficiency.} Generally, the
+normalization of the magnetic profile ($B_0$) and the CR acceleration efficiency
+function ($g_{\rmn{CR}}$) determine the overall normalization of the
+emission. The radial decline of the magnetic field ($ \alpha_{\rmn{B}}$) and
+$\gamma_{\rmn{tu}}$, both determine the shape of the radio profile and, hence,
+are also degenerate.  By scanning the allowed parameter space and asserting
+Bayesian priors that rely on observational constraints and theoretical
+considerations about likely parameter combinations for certain classes (mini
+halos versus giant halos), we will draw conclusions on the applicability of the
+hadronic model for RHs.  In Fig.~\ref{fig:SBmodeling}, we show the surface
+brightness and CR-to-thermal pressure profiles of each cluster together with the
+allowed $\gamma_{\rmn{tu}}-\alpha_{B}$ parameter space.  All these clusters are
+modeled at 1.4~GHz and within $R_{200}$, unless differently specified.
 
@@
   of our model fits to the data in the $\gamma_{\rmn{tu}}-\alpha_{B}$ parameter
-  space. (For Coma, it refers to the 1.4~GHz case only.)  Regions of parameter
-  space with reduced-$\chi^2$ values substantially larger than unity are
-  excluded by the data while values much smaller than unity may point to an
-  overestimate of the uncertainty intervals. Note that different parameter
-  values that yield almost the same surface brightness profile may result in
-  very different $X_{\rmn{CR}}$ profiles. In the case of Abell~2163 and
-  Ophiuchus, we adopt a $10\%$ uncertainty range instead of the errors reported
-  by \citet{2009A&A...499..679M} to account for additional systematic
-  uncertainties, e.g., residual point source contamination. For Perseus, we show
-  the mini-halo data only for the range that is unaffected by residual point
-  sources \citep{1990MNRAS.246..477P} and adopt $10\%$ uncertainty budget.}
+  space.  Regions of parameter space with reduced-$\chi^2$ values substantially
+  larger than unity are excluded by the data while values much smaller than
+  unity may point to an overestimate of the uncertainty intervals. Note that
+  different parameter values that yield almost the same surface brightness
+  profiles may result in very different $X_{\rmn{CR}}$ profiles. In the case of
+  Abell~2163 and Ophiuchus, we adopt a 10 per cent uncertainty range instead of
+  the errors reported by \citet{2009A&A...499..679M} to account for additional
+  systematic uncertainties, e.g., residual point source contamination. For
+  Perseus, we show the mini-halo data only for the range that is unaffected by
+  residual point sources \citep{1990MNRAS.246..477P} and adopt a 10 per cent
+  uncertainty budget.}
 \label{fig:SBmodeling}
 \end{figure*}
-
-\del{ We adopt a $10\%$ uncertainty range for the inner points of the Coma
-  $352$~MHz data.}
 
@@
 beam is $0.156$~deg \citep{1997A&A...321...55D}, almost two orders of magnitude
-larger than the X-ray observation of \cite{1992A&A...259L..31B}.\footnote{The
-  apparent displacement of the radio and X-ray peak of about $0.05$~deg is well
-  within the angular resolution of the radio observation and hence negligible
-  for the modeling.}  Thus, we apply a Gaussian smoothing to our theoretical
-surface brightness of equation~(\ref{eq:surf}) with $\sigma_{\rmn{smoothing}} =
+larger than the angular resolution of the X-ray observation of
+\cite{1992A&A...259L..31B}.\footnote{The apparent displacement of the radio and
+  X-ray peak of about $0.05$~deg is well within the angular resolution of the
+  radio observation and hence negligible for the modeling.}  Thus, we apply a
+Gaussian smoothing to our theoretical surface brightness of
+equation~(\ref{eq:surf}) with $\sigma_{\rmn{smoothing}} =
 FWHM_{\rmn{radio}}/2.355$.
@@
 and $\alpha_{\rmn{B}}=0.5$ (top left panel). Values as high as
-$\gamma_{\rmn{tu}} \approx 4$ still provide a good fit, however, at the expense
+$\gamma_{\rmn{tu}} \approx 4$ still provide an acceptable fit, however, at the expense
 of a shallower decline of the magnetic field profile (smaller $ \alpha_{\rmn{B}}$) as a
@@
 of the radio surface brightness as well as the total radio luminosity with a
-maximal relative deviation of about $25\%$.
+maximal relative deviation of about 25 per cent.
 
@@
 above 100~MeV (100~GeV) is $F_{\gamma} = 2.4 \times 10^{-9}$ ($8.7 \times
-10^{-13}$) cm$^{-2}$~s$^{-1}$. 
-{\bf We can compare our $F_{\gamma} (>500~\rmn{MeV}) = 6.9 \times10^{-10}$~cm$^{-2}$~s$^{-1}$
-to the upper limit recently set with the \emph{Fermi} data of $F_{\gamma, UL} (>500~\rmn{MeV}) 
-= 4 \times 10^{-10}$~cm$^{-2}$~s$^{-1}$ \citep{2013arXiv1308.5654T}.  
-However, we note that the latter has been obtained using the \cite{2010MNRAS.409..449P}
-model which is significantly more peaked than the $\gamma_{\rmn{tu}} = 2$ case
-and, therefore, is too stringent for a proper comparison.}
-Note also that for slightly higher values of $\gamma_{\rmn{tu}}$, i.e., a more centrally
+10^{-13}$) cm$^{-2}$~s$^{-1}$.  {\bf We note that our modeled gamma-ray flux
+  $F_{\gamma} (>500~\rmn{MeV}) = 6.9 \times10^{-10}$~cm$^{-2}$~s$^{-1}$ formally
+  violates the upper limit recently set with the \emph{Fermi}-LAT data of
+  $F_{\gamma, UL} (>500~\rmn{MeV}) = 4 \times 10^{-10}$~cm$^{-2}$~s$^{-1}$
+  \citep{2013arXiv1308.5654T}.  However, this upper limit has been obtained for
+  the {\em advection-only} case \citep{2010MNRAS.409..449P}, which is
+  significantly more peaked than the streaming-dominated $\gamma_{\rmn{tu}} = 2$
+  case considered here and , thus, it is not directly applicable.}  Note also
+that for slightly higher values of $\gamma_{\rmn{tu}}$, i.e., a more centrally
 concentrated CR distribution, the radio and gamma-ray yield would be increased
@@
 $g_{\rmn{CR}}$). This causes the associated gamma-ray flux also to be reduced to
-a level that is low enough to easily circumvent the gamma-ray constraints. 
-{\bf E.g., for the parameter combination $\gamma_{\rmn{tu}} = 3$ and
-$\alpha_{\rmn{B}}=0.4$, we obtain $F_{\gamma} = 1.3 \times 10^{-9}, 3.9 \times 10^{-10}$,
-and $4.9 \times 10^{-13}$~cm$^{-2}$~s$^{-1}$ for energies above 100~MeV, 500~MeV,
-and 100~GeV, respectively.}  We caution that in principle, CR streaming
-should cause the CR spectrum to steepen \citep{2013arXiv1303.4746W}.  
-This may then considerably weaken these constraints as a result of the convex spectral 
-curvature since the gamma-ray emission probes the high-energy tail of the CR distribution 
-that is suppressed in this picture in comparison to the lower-energy protons that the
-radio emission is sensitive to \citep[see][for an extended discussion of this
-point]{2011arXiv1111.5544M}.
+a level that is low enough to easily circumvent the gamma-ray constraints.  {\bf
+  E.g., for the parameter combination $\gamma_{\rmn{tu}} = 3$ and
+  $\alpha_{\rmn{B}}=0.4$, we obtain $F_{\gamma} = 1.3 \times 10^{-9}, 3.9 \times
+  10^{-10}$, and $4.9 \times 10^{-13}$~cm$^{-2}$~s$^{-1}$ for energies above
+  100~MeV, 500~MeV, and 100~GeV, respectively.}  In principle, CR streaming
+should cause the CR spectrum to steepen \citep{2013arXiv1303.4746W}.  This may
+then considerably weaken these constraints as a result of the convex spectral
+curvature since the gamma-ray emission probes the high-energy tail of the CR
+distribution that is suppressed in this picture in comparison to the
+lower-energy protons that the radio emission is sensitive to \citep[see][for an
+extended discussion of this point]{2011arXiv1111.5544M}.
 
@@
 emission in the outer halo parts and would need a secondary component to fill in
-the `missing' hadronic radio emission. This is exemplified in the lower plot of
+the ``missing'' hadronic radio emission. This is exemplified in the lower plot of
 the top left panel of Fig.~\ref{fig:SBmodeling}, which shows the fraction of
 missing surface brightness as a function of radius and accumulates to a total
-missing power of about 35\%.
-
-\citet{2012arXiv1207.3025B} pointed out problems of the hadronic model
-for the limited parameter space $\alpha\gtrsim2.6$, while adopting a much
-more extended azimuthally averaged RH profile at 352~MHz
-\citep{2011MNRAS.412....2B} than the one used in the present study so far
-\citep{1997A&A...321...55D}. The problem of reproducing the spectral steepening
-claimed in the Coma RH is somewhat mitigated when considering the negative flux
-bowl due to the SZ effect that causes the measured RH spectrum to experience a
-sharp cutoff towards high frequencies \citep[][which both use X-ray inferred
-pseudo-pressure profiles and assume an accretion shock radius to estimate the
-Compton-$y$ parameter of Coma]{2002A&A...396L..17E, 2004A&A...413...17P}. To
-overcome this uncertainty, we use the observed SZ decrement of the Coma cluster
-by the \citet{2012arXiv1208.3611P}. We obtain the total SZ flux by integrating
-the Compton-$y$ profile up to the RH's radial extent at 352~MHz of about
-$1.3$~$h_{0.7}^{-1}$~Mpc \citep[][which provide the most sensitive observation
-of the Coma RH to date]{2011MNRAS.412....2B}. We show the resulting SZ decrement
-in Fig.~\ref{fig:SZ_Coma} together with the Coma RH flux at different
-frequencies \citep{2003A&A...397...53T}. An intrinsic power-law radio spectrum,
-$(\nu/\nu_{0})^{-\alpha/2}$, exhibits a sharp cutoff at frequencies around 3-5
-GHz due to the negative flux contribution of the SZ effect. Hence, we fit the
-resulting RH spectrum with different spectral indices, $2.1\lesssim
-\alpha\lesssim2.9$. We allow the normalization and $\nu_{0}$ to vary freely and
-impose a lower floor to the reported uncertainties of 10\% to account for
-possible systematics. The resulting reduced-$\chi^{2}$ values (shown in the
-legend of Fig.{\ }\ref{fig:SZ_Coma}) underline the discrepancy between RH flux
-measurements at different frequencies---in particular for interferometric
-measurements that have to reconstruct a large fraction of the flux due to the
-``missing zero spacing'' problem. At $\sim5$~GHz, the SZ decrement is comparable
-to the measured RH flux. {\bf Recently, \cite{2013arXiv1309.1820B}, using the
-correlation between $Y_{\rmn{SZ}}$ and the low-frequency radio-halo 
-brightness \citep{2011MNRAS.412....2B,2012arXiv1208.3611P}, 
-found that the SZ decrement at $\sim5$~GHz is below 10\%.
-This is clearly in contrast with the results from our simplified approach,
-at least for $\alpha \ge 2.7$. However, as pointed out by \cite{2013arXiv1309.1820B}, 
-the low-frequency observations by \cite{2011MNRAS.412....2B} imply that the Coma
-radio halo is significantly larger than what thought before. This could dramatically
-impact the estimations regarding the SZ decrement and more sensitive
-observations are needed to better clarify this issue. On this, we want to stress once more 
-that CR streaming can also cause spectral steepening \citep{2013arXiv1303.4746W}.
-}
-
-%This demonstrates that the magnitude of the SZ effect
-%is higher than assumed by \cite{2004JKAS...37..493B}, \cite{2004A&A...424..773R}, 
-%and \cite{2010MNRAS.401...47D}, while it is lower than the models of 
-%\cite{2002A&A...396L..17E} and \cite{2004A&A...413...17P}.
-
-{\bf The much more extended RH profile at 352~MHz represents a serious
-challenge for our extended hadronic model. We complement our RH modeling at high
-frequencies (1.4 GHz) with modeling of the new data at 352~MHz
-\citep{2011MNRAS.412....2B}. To this end, we use a {\em novel} $352$~MHz surface
-brightness profile that was corrected for residual point-source contamination by
-applying the multi-resolution filtering technique described in
-\citet{2002PASP..114..427R} as well as adopting the X-ray center for the RH
-profile (Rudnick, priv.{\ }comm.). The resulting profile (shown in blue in
-Fig.~\ref{fig:SBmodeling}) declines at a slightly faster rate towards the outskirts
-than the profile used by \citet{2012arXiv1207.3025B}. More
-importantly, there is considerable azimuthal variation in the halo profile 
-(see Fig.{\ }4 of \citealp{2011MNRAS.412....2B} and also our discussion about 
-RH asphericity in the next section), which would eventually have to
-be modeled through hydrodynamical cluster simulations but which is beyond the
-scope of this work.}  
-%Interestingly, as shown in Fig.~\ref{fig:SB_Coma}, the 1.4
-%GHz profile can be brought into agreement with the low-frequency profile by
-%choosing a lower zero level (Rudnick, priv. comm.; see also
-%\citealp{2012arXiv1208.3611P}), however at the expense of emerging super-cluster
-%emission from the Coma region on scales much more extended than the RH
-%\citep{2007ApJ...659..267K}. Conversely, by increasing the zero level of the 352
-%MHz data \citep{2011MNRAS.412....2B} reconciles that profile with the narrower
-%profile of \citet{1997A&A...321...55D} (Fig.~\ref{fig:SB_Coma}), possibly at the
-%expense of an implausibly high zero level, judging from the more sensitive 352
-%MHz data (Rudnick, priv.{\ }comm.).  Assuming for a moment that the choices of
-%zero level at both frequencies were indeed correct, this would imply a larger
-%extent of the RH at lower frequencies. A combination of better data at 1.4 GHz,
-%careful cleaning of the emission of tailed radio galaxies, and a full accounting
-%of the resulting systematic uncertainties into the total error budget are
-%certainly needed to fully clarify the observational situation.
-%
-\begin{figure} 
-\centering
-\includegraphics[width=\columnwidth]{figures/SZ_Coma.eps}
-\caption{Observed RH fluxes of the Coma cluster as compiled by
-  \citet{2003A&A...397...53T}. Intrinsic power-law radio spectra are modified at
-  high frequencies by means of the SZ decrement (dotted), which we estimate from
-  observations by the \citet{2012arXiv1208.3611P} and integrate within the
-  radial extend of the RH at 352 MHz. We fit the data points with SZ-modified
-  power-law spectra with different spectral indices $\alpha$ and impose a lower
-  floor to the reported uncertainties of 10\% to account for possible
-  systematics. The corresponding reduced-$\chi^{2}$ values demonstrate the
-  discrepancy between RH flux measurements at different frequencies.}
-\label{fig:SZ_Coma}
-\end{figure}
-
-%\begin{figure} 
-%\centering
-%\includegraphics[width=\columnwidth]{figures/SB_Coma_norm_band.eps}
-%\caption{Surface brightness profiles of the Coma RH, normalized at 300 kpc.  We
-% show a 352 MHz profile that was corrected for residual point-source
-%  contamination by applying the multi-resolution filtering technique as well as
-%  adopting the X-ray center for the RH profile (blue, Rudnick,
-%  priv. comm.). This profile declines at a slightly faster rate towards the
-%  outskirts than the profile used by \citet[][black
-%  squares]{2012arXiv1207.3025B}. Increasing the zero level of the (more
-%  sensitive) 352 MHz data (blue open squares) to the level of 1.4 GHz halo data
-%  \citep[red filled circles,][]{1997A&A...321...55D} brings those data into
-%  agreement. Alternatively, lowering the zero level of the 1.4 GHz data (red
-%  open circles, Rudnick, priv. comm.) allows to match the much larger radial
-%  extend of the low-frequency data. Those systematic uncertainties need to be
-%  carefully addressed in future observations and accounted for in the error
-%  budget that currently only account for statistical uncertainties (grey shaded
-%  band, \citealp{2012arXiv1207.3025B}).}
-%\label{fig:SB_Coma}
-%\end{figure}
+missing power of about 35 per cent.
+
+{\bf The much more extended RH profile at 352~MHz represents a serious challenge
+  for our extended hadronic model \citep{2012arXiv1207.3025B}. We complement our
+  RH modeling at high frequencies (1.4 GHz) with modeling of the new data at
+  352~MHz \citep{2011MNRAS.412....2B}. To this end, we use a {\em novel}
+  $352$~MHz surface brightness profile that was corrected for residual
+  point-source contamination by applying the multi-resolution filtering
+  technique described in \citet{2002PASP..114..427R} as well as adopting the
+  X-ray center for the RH profile (Rudnick, priv.{\ }comm.). The resulting
+  profile (shown in blue in Fig.~\ref{fig:SBmodeling}) declines at a slightly
+  faster rate towards the outskirts than the profile used by
+  \citet{2012arXiv1207.3025B}. More importantly, there is considerable azimuthal
+  variation in the halo profile (see Fig.{\ }4 of \citealp{2011MNRAS.412....2B}
+  and also our discussion about RH asphericity in the next section), which would
+  eventually have to be modeled through hydrodynamical cluster simulations but
+  which is beyond the scope of this work.}
 
@@
 agreement with the findings of \citet{2012arXiv1207.3025B}. At the same time,
-our analysis at 1.4~GHz confirms the result by \citet{2012...VERITAS} who also
-conclude that the hadronic model for the Coma RH is a viable explanation for
-magnetic field estimates inferred by Faraday rotation measure studies
+our analysis at 1.4~GHz confirms the result by the \citet{2012...VERITAS} who
+also conclude that the hadronic model for the Coma RH is a viable explanation
+for magnetic field estimates inferred by Faraday rotation measure studies
 \citep{2010A&A...513A..30B} and is not challenged by {\em Fermi} upper limits on
@@
 (i.e., {\em high} $\gamma_{\rmn{tu}}$ values) as proposed by
-\citet{2011A&A...527A..99E}. {\bf Note that \cite{2013arXiv1303.4746W} 
-arrive at a different conclusion finding that the increase of turbulence promotes 
-outward streaming more than inward advection, therefore allowing flat CR 
-distributions in turbulent clusters. However, this does not help in
-the case of the 352~MHz data, where, as discussed above, not even a
-flat CR profile is enough to explain the observed emission within the
-hadronic scenario.} These finding hint at the necessity of a second,
-leptonic component (within the general framework of the hadronic model) that
-fills in the patchier emission in the peripheral, low-surface brightness regions
-of the halo, in particular at low frequencies \cite[see Fig.~3
+\citet{2011A&A...527A..99E}. {\bf Note that \cite{2013arXiv1303.4746W} arrive at
+  a different conclusion and find that the increase of turbulence promotes
+  outward streaming more than inward advection, thus enabling flat CR
+  distributions in turbulent clusters. However, this does not help in the case
+  of the 352~MHz data, where, as discussed above, not even a flat CR profile
+  would suffice to explain the observed emission within the hadronic scenario.}
+These finding hint at the necessity of a second, leptonic component (within the
+general framework of the hadronic model) that fills in the patchier emission in
+the peripheral, low-surface brightness regions of the halo
+\citep{2008MNRAS.385.1211P}, in particular at low frequencies \cite[see Fig.~3
 of][]{2011MNRAS.412....2B}. We will return to this point in
@@
 The morphology of the giant radio halo in Abell~2163 is also closely correlated
-to the cluster's thermal X-ray structure. As in Coma, the radio emission declines
-towards the cluster outskirts at a slower rate in comparison to the thermal
-X-ray emission \citep{2001A&A...373..106F}. The morphological appearance is
-non-spherical, with an elongation in the East-West direction. We use the surface
-brightness map provided by \citet{2009A&A...499..679M} for which the synthesized
-radio beam can be approximated by a circular Gaussian with
+to the cluster's thermal X-ray structure. As in Coma, the radio emission
+declines towards the cluster outskirts at a slower rate in comparison to the
+thermal X-ray emission \citep{2001A&A...373..106F}. The morphological appearance
+is non-spherical, with an elongation in the East-West direction. We use the
+surface brightness map provided by \citet{2009A&A...499..679M} for which the
+synthesized radio beam can be approximated by a circular Gaussian with
 $FWHM_{\rmn{radio}}=62\arcsec$.  Again, $FWHM_{\rmn{radio}}$ is larger than the
-resolution of the \emph{ROSAT} observation and the corresponding gas density
-profile. Converted to physical scale, $\sigma_{\rmn{smoothing}}$ is of the order
-of that in Coma because of the larger distance of Abell~2163. Hence, we also apply
-Gaussian smoothing.
+angular resolution of the \emph{ROSAT} observation and the corresponding gas
+density profile. Converted to physical scale, $\sigma_{\rmn{smoothing}}$ is of
+the order of that of Coma because of the larger distance of Abell~2163. Hence,
+we also apply Gaussian smoothing.
 
@@
 brightness. With this choice of parameters, we recover the emission shape and
-the total luminosity within about $15\%$.  The corresponding gamma-ray flux
+the total luminosity within about 15 per cent.  The corresponding gamma-ray flux
 within $R_{200}$ is $F_{\gamma} (>100~\rmn{MeV}) = 4.2
@@
 
-%As for Coma, such low values of $\gamma_{\rmn{tu}}$ appear to be in conflict
-%with our understanding of giant radio halos that are expected to be
-%turbulent. 
 As for Coma, in Fig.~\ref{fig:SBmodeling}, we show the model surface brightness
@@
 $\alpha_{\rmn{B}}=0.5$. {\bf The corresponding gamma-ray flux above 100~MeV
-(100~GeV) is $F_{\gamma} = 5.9 \times 10^{-11}$ ($2.2 \times
-10^{-14}$) cm$^{-2}$~s$^{-1}$.} The lower panel shows the fraction
-of missing surface brightness of our model to explain the data as a function of
-radius. That fraction accumulates to a total missing power of about 80\% for the
-giant radio halo.
+  (100~GeV) is $F_{\gamma} = 5.9 \times 10^{-11}$ ($2.2 \times 10^{-14}$)
+  cm$^{-2}$~s$^{-1}$.} The lower panel shows the fraction of missing surface
+brightness of our model to explain the data as a function of radius. That
+fraction accumulates to a total missing power of about 80 per cent for the giant
+radio halo.
 
@@
 is among the best studied clusters in X-rays
-(e.g.,~\citealp{2003ApJ...590..225C,2006MNRAS.366..417F,2011arXiv1105.5025F}). Also
-the Perseus radio morphology resembles that in the X-rays. We proceed as before,
-but now adopt a higher central magnetic field strength of
-$B_{0}=10$~$\mu$G. Such a larger $B_0$ is expected in a CCC with its higher
-central gas density, implying a larger adiabatic compression factor of the
-magnetic field during the condensation of the cool core
-(\citealp{2010ApJ...710..634A,2011arXiv1111.5544M} for a discussion on the
+(e.g.,~\citealp{2003ApJ...590..225C,2006MNRAS.366..417F,2011arXiv1105.5025F}). As
+for the two radio halos, the Perseus radio morphology resembles that in the
+X-rays. We proceed as before, but now adopt a higher central magnetic field
+strength of $B_{0}=10$~$\mu$G. Such a larger $B_0$ is expected in a CCC with its
+higher central gas density, implying a larger adiabatic compression factor of
+the magnetic field during the condensation of the cool core (see the
+\citealp{2010ApJ...710..634A,2011arXiv1111.5544M}, for a discussion on the
 Perseus magnetic field).
@@
 $\alpha_{\rmn{B}}=0.3$). Both model realizations nicely recover the surface
-brightness profile and the total luminosity within $10\%$.  The gamma-ray flux
-within $R_{200}$ for the $\gamma_{\rmn{tu}}=3$ case and for energies above
+brightness profile and the total luminosity within 10 per cent.  The gamma-ray
+flux within $R_{200}$ for the $\gamma_{\rmn{tu}}=3$ case and for energies above
 100~MeV (100~GeV) is $F_{\gamma} = 1.4 \times 10^{-8}$ ($5.1 \times 10^{-12}$)
-cm$^{-2}$~s$^{-1}$. Adopting $\gamma_{\rmn{tu}}=100$ and $ \alpha_{\rmn{B}}=0.3$, the
-corresponding gamma-ray flux above 100~MeV (100~GeV) is $F_{\gamma} = 4.9 \times
-10^{-9}$ ($1.8 \times 10^{-12}$) cm$^{-2}$~s$^{-1}$. Note that the gamma-ray
-flux above 100~MeV of the central galaxy NGC~1275 as measured by \emph{Fermi} is
-$2 \times 10^{-7}$~cm$^{-2}$~s$^{-1}$ \citep{2009arXiv0904.1904T}, well above
-our model predictions due to hadronically produced diffuse gamma-ray emission
-that is expected to mostly glow from the core region of the cluster.
+cm$^{-2}$~s$^{-1}$. Adopting $\gamma_{\rmn{tu}}=100$ and $
+\alpha_{\rmn{B}}=0.3$, the corresponding gamma-ray flux above 100~MeV (100~GeV)
+is $F_{\gamma} = 4.9 \times 10^{-9}$ ($1.8 \times 10^{-12}$)
+cm$^{-2}$~s$^{-1}$. Note that \emph{Fermi}-LAT measured the gamma-ray flux above
+100~MeV of the central galaxy NGC~1275 to $2 \times 10^{-7}$~cm$^{-2}$~s$^{-1}$
+\citep{2009arXiv0904.1904T}, well above our model predictions due to
+hadronically produced diffuse gamma-ray emission that is expected to mostly glow
+from the core region of the cluster.
 
 We can compare these predictions with the upper limit above 1~TeV, and for a
-region within $0.15$~deg around the cluster center, recently obtained by
+region within $0.15$~deg around the cluster center, recently obtained by the
 \cite{2011arXiv1111.5544M}. For $\gamma_{\rmn{tu}}=3$ ($\gamma_{\rmn{tu}}=100$),
@@
 simplify modeling, we neglect the small central temperature dip for radii
-$r<30\,h_{70}^{-1}$~kpc and adopt a constant central temperature (due to its
+$r<30\,h_{70}^{-1}$~kpc and adopt a constant central temperature. (Owing to its
 small size, the cool core region has no influence on the resulting radio surface
-brightness).  The radio mini-halo morphology displays similarities with the
-thermal X-ray emission. For our modeling we use the surface brightness profile
-provided by \cite{2009A&A...499..679M}.
+brightness.) Again, the radio mini-halo morphology displays similarities with
+the thermal X-ray emission. For our modeling, we use the surface brightness
+profile provided by \cite{2009A&A...499..679M}.
 
@@
 favored, as expected for mini-halos. However, large regions of the parameter
-space provide nice fits to the data.  In Fig.~\ref{fig:SBmodeling}, we show the
+space provide excellent fits to the data.  In Fig.~\ref{fig:SBmodeling}, we show the
 two parameter combinations ($\gamma_{\rmn{tu}}=3$, $ \alpha_{\rmn{B}}=0.4$) and
 ($\gamma_{\rmn{tu}}=100$, $ \alpha_{\rmn{B}}=0.3$).  For those, we recover the surface
-brightness profile and the total luminosity within $20\%$. The gamma-ray flux
+brightness profile and the total luminosity within 20 per cent. The gamma-ray flux
 within $R_{200}$ for the $\gamma_{\rmn{tu}}=3$ case and for energies above
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\subsection{Possible biases in the modeling of individual radio halos}
-%\subsection{Discussion}
-\section{Discussion: an hybrid scenario for Giant and Mini Radio Halos?}
+
+\section{Discussion: a hybrid scenario for Giant and Mini Radio Halos?}
 \label{sec:discussion_hadronic}
@@
 In order to cleanly assess the possibility of the hadronic model to alone
-explain the RH data, we only considered the hadronically-induced radio 
-emission component in the preceding section. Hence, by construction, we 
-neglected other (leptonic) emission components, such as reaccelerated electrons. 
-{\bf Possible biases that may affect our previous conclusions are the following.}
-
-%\begin{enumerate} 
-%\item 
+explain the RH data, we only considered the hadronically-induced radio emission
+component in the preceding section. Hence, by construction, we neglected other
+(leptonic) emission components, such as reaccelerated electrons.  {\bf We now
+  address possible biases that may have affected our previous conclusions.}
+
+\subsection{Biases of the hadronic model of  radio halos}
+
 (i) Merging clusters are not spherically symmetric as can be seen in Coma and
-  Abell~2163, requiring inherently non-spherical modeling. In order to
-  reproduce the more extended radio emission relative to the thermal X-ray
-  emission, the non-thermal clumping factor, $C_{\rmn{non-th}}$, needs to be
-  larger than its thermal analogue, $C_{\rmn{th}}$, in concentric spherical
-  shells, where we defined those statistics by
+Abell~2163, requiring inherently non-spherical modeling. In order to reproduce
+the more extended radio emission relative to the thermal X-ray emission, the
+non-thermal clumping factor, $C_{\rmn{non-th}}$, needs to be larger than its
+thermal analogue, $C_{\rmn{th}}$, in concentric spherical shells, where we
+defined those statistics by
 \begin{eqnarray}
@@
 phenomenological modeling, we allow for those deviations by means of the
-  parameters $\gamma_{\rmn{tu}}$ and $ \alpha_{\rmn{B}}$ for the CRs and magnetic fields,
-  respectively. 
-  %While this approach is well suited to describe large-scale
-  %anisotropies, it may be inadequate to model small-scale inhomogeneities such
-  %as CR trapping in magnetic mirrors through the second adiabatic invariant and
-  %needs to be carefully quantified in future work.
-
-%\item 
+parameters $\gamma_{\rmn{tu}}$ and $ \alpha_{\rmn{B}}$ for the CRs and
+magnetic fields, respectively.  While this approach is well suited to describe
+large-scale anisotropies, it may be inadequate to model small-scale
+inhomogeneities such as CR trapping in magnetic mirrors through the second
+adiabatic invariant and needs to be carefully quantified in future work.
+
 (ii) Adopting the simulation-derived $\tilde{C}$ profile
@@
 the formation of the cooling core. Hence, the resulting values of
-  $\gamma_{\rmn{tu}}$ are then biased low in comparison to a potentially
-  shallower slope of the inner CR profile. To quantify the last point, we try to
-  reproduce the Coma surface brightness at 1.4 GHz using a model without
-  $\tilde{C}$. We find that values as high as $\gamma_{\rmn{tu}} \approx 8$ can
-  be accommodated. However, $\gamma_{\rmn{tu}}=1$ still represents the best
-  match to the data, demonstrating that the problem can be weakened but not
-  circumvented even in this case of a cored CR profile.
-
-%\item 
+$\gamma_{\rmn{tu}}$ are then biased low in comparison to a potentially shallower
+slope of the inner CR profile. To quantify the last point, we try to reproduce
+the Coma surface brightness at 1.4 GHz using a model without $\tilde{C}$. We
+find that values as high as $\gamma_{\rmn{tu}} \approx 8$ can be
+accommodated. However, $\gamma_{\rmn{tu}}=1$ still represents the best match to
+the data, demonstrating that the problem can be weakened but not circumvented
+even in this case of a cored CR profile.
+
 (iii) Considering the case of advection-dominated CR transport
@@
 \cite{2010MNRAS.409..449P}. If the cluster CR population is mainly accelerated
-  in cosmological structure formation shocks, then this value should depend on
-  the mass accretion history and should be approximately universal, i.e.,
-  similar for all clusters. We find $g_{\rmn{CR, Perseus}} = 0.52$ and
-  $g_{\rmn{CR, Ophiuchus}} = 0.014$, because we fixed $B_{0}=10$~$\mu$G in both
-  cases and used $g_{\rmn{CR}}$ as normalization. This discrepancy can be
-  resolved by increasing/lowering the central magnetic field in
-  Perseus/Ophiuchus to $B_{0,\rmn{Perseus}}\approx20$~$\mu$G and
+in cosmological structure formation shocks, then this value should depend on the
+mass accretion history and should be approximately universal, i.e., similar for
+all clusters. We find $g_{\rmn{CR, Perseus}} = 0.52$ and $g_{\rmn{CR,
+    Ophiuchus}} = 0.014$, because we fixed $B_{0}=10$~$\mu$G in both cases and
+used $g_{\rmn{CR}}$ as normalization. This discrepancy can be resolved by
+increasing/lowering the central magnetic field in Perseus/Ophiuchus to
+$B_{0,\rmn{Perseus}}\approx20$~$\mu$G and
 $B_{0,\rmn{Ophiuchus}}\approx1$~$\mu$G. We note, however, that without the
-  guidance of cosmological cluster simulations that include CR transport, the
-  data does not yet constrain $\gamma_{\rmn{tu}}$.
-%\end{enumerate}
-
-The small cluster sample analyzed here is only meant to serve as a proof
-of concept and to show the viability of matching observed representative 
-RH data with our extended hadronic model. {\bf Despite the available
-observational input on the magnetic field in clusters ($B_0$, $ \alpha_{\rmn{B}}$), 
-which is, however, very limited, the parameter space that the physics modeled here 
-demands is quite large encompassing also $\gamma_{\rmn{tu}}$ and the CR acceleration 
-efficiency function. Particularly, a large region of the ($\gamma_{\rmn{tu}}$,
-$\alpha_{\rmn{B}}$) parameter space is available for the analyzed radio
-mini-halos (note also that the parameters $\gamma_{\rmn{tu}}$ and
-$\alpha_{\rmn{B}}$ are degenerate). Future work on all known RHs may 
-provide better insight.}
-% 
-%This is in especially
-%true because of the comparably large parameter space that the physics modeled
-%here demands and which encompasses our parametrization of the magnetic field
-%($B_0$, $ \alpha_{\rmn{B}}$), $\gamma_{\rmn{tu}}$, and the CR acceleration efficiency
-%function. Particularly, a large region of the ($\gamma_{\rmn{tu}}$,
-%$\alpha_{\rmn{B}}$) parameter space is available for the analyzed radio
-%mini-halos (note also that the parameters $\gamma_{\rmn{tu}}$ and
-%$\alpha_{\rmn{B}}$ are degenerate). Future work on all known RHs may provide
-%better insight, but is beyond the scope of this work.
-%
-However, it seems unlikely that the biases discussed above severely affect our findings
-that the extended hadronic model successfully reproduces the main morphological
-characteristics of radio mini-halos with a wide range of possible values for
-$\gamma_{\rmn{tu}}$ and without violating gamma-ray constraints. In contrast, it
-appears to fail in the outskirts of the Coma RH at low frequencies and
-require a flat CR distribution both in Coma and in A2163 at 1.4~GHz. {\bf This motivates 
-us to consider a modification of this purely hadronic model in explaining RHs.} 
-%which 
-%we will then scrutinize statistically in the following Sections, namely by investigating the
-%radio-to-X-ray and radio-to-SZ scaling relations as well as RH
-%luminosity functions.}
-
-%\section{A Model for Giant and Mini Radio Halos}
-%\label{sec:discussion_hadronic}
+guidance of cosmological cluster simulations that include CR transport, the data
+does not yet constrain $\gamma_{\rmn{tu}}$.
+
+The small cluster sample analyzed here is only meant to serve as a proof of
+concept and to show the viability of matching observed representative RH data
+with our extended hadronic model. However, it seems unlikely that the biases
+discussed above severely affect our findings that the extended hadronic model
+successfully reproduces the main morphological characteristics of radio
+mini-halos with a wide range of possible values for $\gamma_{\rmn{tu}}$ and
+without violating gamma-ray constraints. In contrast, the hadronic model appears
+to fail in explaining the radio emission in the outskirts of the Coma RH at low
+frequencies and requires a flat CR distribution both in Coma and in A2163 at
+1.4~GHz. {\bf This motivates us to consider a modification of this purely
+  hadronic model in explaining RHs.}
 
@@
 
-{\bf Within the hadronic scenario, there emerges a plausible physical solution to
-this observational challenge. We suggest that the rich phenomenology of RHs may be a
-consequence of two different radio emission components---one of which is induced
-by hadronic interactions and the other is of leptonic origin. 
-%While we leave the origin of the leptonic component unspecified, 
-There are a number of plausible processes for the latter.     
-These includes turbulent re-acceleration of primary or secondary (hadronic)
-electrons \citep{2010arXiv1008.0184B} or re-acceleration of fossil electrons by
-means of diffusive shock acceleration \citep{kang11,kang12,pinzke13}.
-%The fossil electron population may stem from the time-integrated and successively
-%cooled population of directly injected electrons at strong structure formation
-%shocks trough the Lagrangian history. Alternatively, a seed population of
-%relativistic electrons could be provided by the time-integrated action of AGN
-%feedback or by supernova-driven galactic winds. 
-Depending on relative strength of the different components, this scenario would imply 
+{\bf Within the hadronic scenario, there emerges a plausible physical solution
+  to this observational challenge. We suggest that the rich phenomenology of RHs
+  may be a consequence of two different radio emission components---one of which
+  is induced by hadronic interactions and the other is of leptonic origin
+  \citep{2008MNRAS.385.1211P}.  There are a number of plausible processes for
+  the latter.  These includes turbulent re-acceleration of primary or secondary
+  (hadronically produced) electrons \citep{2010arXiv1008.0184B} or
+  re-acceleration of fossil electrons by means of diffusive shock acceleration
+  \citep{kang11,kang12,pinzke13}. The fossil electron population may originate
+  from the time-integrated and successively cooled population of directly
+  injected electrons at strong structure formation shocks that the gas
+  experienced trough it cosmic accretion history. Alternatively, a seed
+  population of relativistic electrons could be provided by the time-integrated
+  action of AGN feedback or by supernova-driven galactic winds.  Depending on
+  relative strength of the different components, this scenario would imply
   various halo phenomena:}
@@
     2008MNRAS.385.1211P, 2008ApJ...689.1063S, 2009MNRAS.395.1333V}. Depending on
-  the merger geometry and dynamical stage, as well as the electron acceleration
-  efficiencies at these non-equilibrium processes and realized CR streaming
-  speeds, we would expect the development of a (fuzzy) transition region between
-  hadronic and leptonic component. This generalizes the simulation-inspired
-  model by \cite{2008MNRAS.385.1211P} who propose that primary electron
-  substantially contribute to the peripheral RH emission.
+  the merger geometry and dynamical stage, as well as on the electron
+  acceleration efficiencies of these non-equilibrium processes and the CR
+  streaming speeds, we would expect the development of a (fuzzy) transition
+  region between hadronic and leptonic component. This generalizes the
+  simulation-inspired model by \cite{2008MNRAS.385.1211P} who propose that
+  primary electron substantially contribute to the peripheral RH emission.
 \end{enumerate}
 
-{\bf A detailed implementation of this hybrid scenario would depend very much
-on the precise characterization of a given cluster. This goes beyond the scope of the 
-present work which is mainly to explore the possible observational consequences of the 
-hadronic component, through our extended model, for future radio surveys. Nevertheless, 
-we sketch possible observational implications of an hybrid hadronic-leptonic scenario in the 
-following subsection.}
-
-%\subsection{What are the observational implications of this picture?}
-\subsection{Possible observational implications}
+{\bf A detailed implementation of this hybrid scenario would depend very much on
+  the precise characterization of a given cluster. This goes beyond the scope of
+  the present work, which mainly explores the possible observational
+  consequences of the hadronic component for future radio surveys that are
+  implied by our extended model. Nevertheless, we sketch possible observational
+  implications of a hybrid hadronic-leptonic scenario in the following
+  subsection.}
+
+\subsection{Observational implications}
 
 \subsubsection{Spectral and morphological variability}
-  In mini-halos and in the
-  centers of giant halos, where the hadronic component dominates in our picture,
-  we would naively expect at most modest spectral variations. This is because
-  these regions average over sufficiently many fluid elements that each
-  experienced its characteristic shock history during the cluster assembly, but
-  which produces a CR population that has on average a nearly universal spectrum
+In mini-halos and in the centers of giant halos, where the hadronic component
+dominates in our picture, we would naively expect at most modest spectral
+variations. This is because these regions average over sufficiently many fluid
+elements, each of which experienced its characteristic shock history during the
+cluster assembly. However, when averaged over the ensemble, this produces a CR
+population that has a nearly universal spectrum
 \citep{2010MNRAS.409..449P}. However, CR streaming and diffusive transport may
 cause a possible spectral steepening in the cluster core region because more
-  energetic CRs diffuse/stream faster. This would
-  then imply spatial variations of the CR spectral index and, hence, spatially
-  varying radio emission throughout the cluster (core region) when taking the CR
-  advection effects into account, which would mix regions of different CR
-  spectral properties. In regions where the leptonic component dominates (such
-  as the outer regions of giant halos or steep spectrum halo sources), we expect
-  substantial spectral and morphological variations in the radio maps. This is
-  because of the intermittency of the acceleration process (acceleration at
-  discrete weak shocks or turbulent acceleration), the expected distribution of
-  Mach numbers or CR momentum diffusion coefficient, respectively, and the
-  comparably short electron cooling time ($\sim100$~Myr). Interestingly, this
-  compares well with the large azimuthal scatter of different sector profiles of
-  the Coma halo, Fig.~4 of \cite{2011MNRAS.412....2B}, and fronts (primarily
-  towards the West) in their high-resolution surface brightness map, which may
-  indicate the transition from the hadronic to the leptonic emission
-  component. In particular, the relative inefficiency of shock acceleration at
-  weak shocks or turbulent acceleration generates steeper radio spectra in the
-  leptonically dominated regions. Hence, this would naturally imply a radial
-  spectral steepening and cause substantial morphological and spectral variation
-  in the outer regions of giant halos. The increasing fraction of the leptonic
-  component towards lower frequencies may then imply a larger halo size
-  with decreasing observational frequency.
-
-\subsubsection{Halo switch-on/-off mechanism and the radio-X-ray bimodality.}
+energetic CRs diffuse/stream faster. This would then imply spatial variations of
+the CR spectral index and, hence, spatially varying radio emission throughout
+the cluster (core region) when taking the CR advection effects into account,
+which would mix regions of different CR spectral properties. In regions where
+the leptonic component dominates (such as the outer regions of giant halos or
+steep spectrum halo sources), we expect substantial spectral and morphological
+variations in the radio maps. This is because of the intermittency of the
+acceleration process (acceleration at discrete weak shocks or turbulent
+acceleration), the expected distribution of Mach numbers or CR momentum
+diffusion coefficient, respectively, and the comparably short electron cooling
+time ($\sim100$~Myr). Interestingly, this compares well with the large azimuthal
+scatter of different sector profiles of the Coma halo, Fig.~4 of
+\cite{2011MNRAS.412....2B}, and fronts (primarily towards the West) in their
+high-resolution surface brightness map, which may indicate the transition from
+the hadronic to the leptonic emission component. In particular, the relative
+inefficiency of shock acceleration at weak shocks or turbulent acceleration
+generates steeper radio spectra in the leptonically dominated regions. Hence,
+this would naturally imply a radial spectral steepening and cause substantial
+morphological and spectral variation in the outer regions of giant halos. The
+increasing fraction of the leptonic component towards lower frequencies may then
+imply a larger halo size with decreasing observational frequency.
+
+\subsubsection{Halo switch-on/-off mechanism and the radio-X-ray bimodality}
 Clearly, a cluster merger injects turbulence and shocks that could both
@@
 hand, CR advection produces centrally enhanced CR profiles because of adiabatic
-  compression of CRs for radial eddies. The energetization and transport of
-  CRs to the central halo regions implies a lightening up of the hadronic
-  emission component. For the leptonic component,
-  the halo switch off is faster or comparable to the dynamical time scale,
-  $t_{\rm dyn} \sim t_{\rm H}/\sqrt{\Delta} \sim 1 \,\rmn{Gyr}
-  \Delta_{100}^{-1/2}$, where $t_{\rm H}=10$~Gyr,
-  $\Delta_{100}=\rho/(100\bar{\rho})$. In case of diffusive shock acceleration
-  of fossil electrons, the radio emission will be shut off within a CR electron
-  cooling time ($t_\rmn{cool}\sim100$~Myr) if the acceleration source ceases,
-  i.e., when shocks have dissipated all the energy. In the case of the turbulent
-  re-acceleration model, the turbulence decays on a few eddy turnover time
-  scales on the injection scale which should take only somewhat longer. The
-  hadronic emission component is also expected to decrease substantially once
-  turbulent pumping of CRs ceases and CRs are set free to stream, which results
-  in a net CR flux towards the external cluster regions. The accompanying
-  flattening of the CR profile implies a lowering of the hadronic radio emission
-  because the CRs see a smaller target density in the outer parts. 
-  {\bf Additionally, \cite{2013arXiv1303.4746W} found that turbulence seems 
-  to promote outward streaming more than inward advection, suggesting the 
-  possibility to substantially decrease the radio flux also in merging clusters.} 
-  This should lead naturally to a bimodality of radio synchrotron emissivities due to
-  hadronic and leptonic halo components.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+compression of CRs for radial eddies. The energetization and transport of CRs to
+the central halo regions implies a lightening up of the hadronic emission
+component. For the leptonic component, the halo switch off is faster or
+comparable to the dynamical time scale, $t_{\rm dyn} \sim t_{\rm
+  H}/\sqrt{\Delta} \sim 1 \,\rmn{Gyr} \Delta_{100}^{-1/2}$, where $t_{\rm
+  H}=10$~Gyr, $\Delta_{100}=\rho/(100\bar{\rho})$. In the case of diffusive
+shock acceleration of fossil electrons, the radio emission will be shut off
+within a CR electron cooling time ($t_\rmn{cool}\sim100$~Myr) if the
+acceleration source ceases, i.e., when shocks have dissipated all the energy. In
+the case of the turbulent re-acceleration model, the turbulence decays on a few
+eddy turnover time scales on the injection scale which should take somewhat
+longer. The hadronic emission component is also expected to decrease
+substantially once turbulent pumping of CRs ceases and CRs are set free to
+stream, which results in a net CR flux towards the external cluster regions. The
+accompanying flattening of the CR profile implies a lowering of the hadronic
+radio emission because the CRs see a smaller target density in the outer parts.
+This should lead naturally to a bimodality of radio synchrotron emissivities due
+to hadronic and leptonic halo components.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \begin{figure*} 
@@
   are two separated populations for each model realization, shown with the same
-  color but different symbols. The upper sets of points (circles) correspond to the CCC 
-  population while the lower sets (triangles) correspond to NCCCs. The plot labels indicate 
-  those parameters which are kept fixed. We fix the $g_{\rmn{CR}}$-normalization parameter to 0.5
-  for all cases. See main text for details.}
+  color but different symbols. The upper sets of points (circles) correspond to
+  the CCC population while the lower sets (triangles) correspond to NCCCs. The
+  plot labels indicate those parameters which are kept fixed. We also fix the
+  $g_{\rmn{CR}}$-normalization parameter to 0.5 for all cases. See main text for
+  further details.}
 \label{fig:SR}
@@
 dividing the cluster population into radio-loud and radio-quiet clusters
-\citep{2012MNRAS.421L.112B,2013arXiv1306.4379C,2013arXiv1307.3049S}. 
-Since $Y_{\rmn{SZ}}$ correlates more tightly with
-cluster mass than $L_{\rmn{X}}$, this may indicate that the larger scatter of
-$L_{\rmn{X}}$ correlates with the scatter of the radio luminosity in such a way
-that it produces a bimodality; but as a result of a second (hidden parameter)
-rather than the fundamental cluster parameter---its mass. In this section, we 
-investigate these two scaling relations in the framework of our extended 
-hadronic scenario.
-
-{\bf In the following, we apply our model to the complete
-cosmological mock cluster catalog build from the MultiDark $N$-body 
-simulation in our Paper~I. For each object in the sample, we mainly use
-the information on its mass and phenomenologically assigned 
-ICM gas density to calculate the radio (and gamma-ray) emission.}
+\citep{2012MNRAS.421L.112B,2013arXiv1306.4379C,2013arXiv1307.3049S}.  Since
+$Y_{\rmn{SZ}}$ correlates more tightly with cluster mass than $L_{\rmn{X}}$,
+this may indicate that the larger scatter of $L_{\rmn{X}}$ correlates with the
+scatter of the radio luminosity in such a way that it produces a bimodality; but
+as a result of a second (hidden parameter) rather than the cluster mass. In this
+section, we investigate these two scaling relations in the framework of our
+extended hadronic scenario.
+
+{\bf In the following, we apply our model to the complete cosmological mock
+  cluster catalog build from the MultiDark $N$-body simulation in our
+  Paper~I. For each object in the sample, we use the cluster mass, a dynamical
+  disturbance parameter (the normalized distance of the halo center and the
+  center of mass) for sorting the cluster into the CCC/NCCC populations, and a
+  phenomenologically assigned ICM density to calculate the radio (and gamma-ray)
+  emission.}
 
@@
 the CR-normalization parameter $g_{\rmn{CR}}$ to 0.5 in all cases, ensuring an
-average CR-to-thermal pressure of $2\%$ ($0.05\%$) within $R_{500}$
+average CR-to-thermal pressure of 2 per cent (0.05 per cent) within $R_{500}$
 ($R_{500}/2$). Here, the radio luminosity is calculated at $1.4$~GHz within
 $R_{500}.$\footnote{The mean (median) difference between calculating $L_{\nu}$
-  within $R_{200}$ or $R_{500}$ is 5.3\% (5.6\%).}  In our CR model, we fix the
-CR number for $\gamma_{\rmn{tu}}=100$ using equation~(36) of
+  within $R_{200}$ or $R_{500}$ is 5.3 per cent (5.6 per cent).}  In our CR
+model, we fix the CR number for $\gamma_{\rmn{tu}}=100$ using equation~(36) of
 \cite{2011A&A...527A..99E}, integrating up to $R_{500}$. To compute the radio
 luminosity for different values of $\gamma_{\rmn{tu}}$, we employ CR number
-conservation (for CR energies $E>$~GeV where Coulomb cooling is negligible for CR
-protons).
+conservation (for CR energies $E>$~GeV where Coulomb cooling is negligible for
+CR protons).
 
@@
 when varying parameter values because we do not include any cluster
-mass-dependence in our parametrizations which is not
-constrained by current data. Closely inspecting Fig.~\ref{fig:SR}, we see that
-we obtain the largest changes in $L_{1.4~\rmn{GHz}}$ for variations in
-$1<\gamma_{\rmn{tu}}<5$ and $B_0$ over the parameter range probed, albeit with a
-stronger dependence for weaker field strengths (as expected from
-equation~(\ref{eq:jnu})).
+mass-dependence in our parametrizations which is not constrained by current
+data. Closely inspecting Fig.~\ref{fig:SR}, we see that we obtain the largest
+changes in $L_{1.4~\rmn{GHz}}$ for variations in $1<\gamma_{\rmn{tu}}<5$ and
+$B_0$ over the parameter range probed, albeit with a stronger dependence for
+weaker field strengths (as expected from the $B^2/(B^2+B_\rmn{CMB}^2)$ term of
+equation~(\ref{eq:jnu}), where $B_\rmn{CMB}\simeq 3.2\,\umu\rmn{G} (1+z)^2$ is
+the equivalent magnetic field strength of the cosmic microwave background).
 
@@
 rotation measure studies) as well as theoretical considerations on CR transport.
-
-\begin{figure*} 
-\centering
-\includegraphics[width=0.49\textwidth]{figures/PL_relation.eps}
-\includegraphics[width=0.49\textwidth]{figures/PSZ_relation.eps}
-\caption{Radio-to-X-ray and radio-to-SZ scaling relations in our extended CR model
-  (see main text for the details of the chosen parameters) compared with
-  observations.  \emph{Left.} $L_{1.4~\rmn{GHz}}-L_{\rmn{X,bol}}$ relation in
-  comparison to the observational sample taken from the literature and detailed
-  in Appendix~\ref{app:D}. We additionally show the detected signal of Mpc-scale 
-  diffuse emission in a stacked sample of radio-quiet galaxy clusters 
-  (green, \protect\citealp{2011ApJ...740L..28B}). 
-  \emph{Right.} $L_{1.4~\rmn{GHz}}-Y_{\rmn{SZ}}$ relation 
-  in comparison with
-  {\bf the PSZ(V) sample (direct integration method) 
-  of \protect\cite{2013arXiv1307.3049S}
-  together with the data points shown in their Fig.~13.}}
-\label{fig:PLSZ}
-\end{figure*}
 
@@
 and systematic uncertainties in the measurements of $L_{1.4}$ and
-$L_{\rmn{X,bol}}$. The recently detected low-luminosity mini-halos exemplify
-those uncertainties and the large intrinsic scatter of this relation. On the
-other hand, X-ray luminosities for the same object as derived by,
-e.g.,~\emph{ROSAT} and \emph{Chandra} can easily differ by a factor of a
-few.\footnote{For example, the bolometric X-ray luminosity of A2163 as measured
-  by \emph{ROSAT} is $8.65\times10^{45}$~$h_{70}^{-1}$~erg~s$^{-1}$
-  \citep{2009A&A...507..661B} while the \emph{Chandra} measurement is
+$L_{\rmn{X,bol}}$. The fact that there have been low-luminosity mini-halos found
+only recently \citep{Giacintucci} exemplifies those uncertainties and the large
+intrinsic scatter of this relation. On the other hand, X-ray luminosities for
+the same object as derived by, e.g.,~\emph{ROSAT} and \emph{Chandra} can easily
+differ by a factor of up to a few.\footnote{For example, the bolometric X-ray
+  luminosity of A2163 as measured by \emph{ROSAT} is
+  $8.65\times10^{45}$~$h_{70}^{-1}$~erg~s$^{-1}$ \citep{2009A&A...507..661B}
+  while the \emph{Chandra} measurement is
   $4.93\times10^{45}$~$h_{70}^{-1}$~erg~s$^{-1}$ (\citealp{2009ApJS..182...12C};
@@
 {\bf In order to compare our model to the observed 1.4~GHz radio-to-SZ scaling
-relation, we use the result by \cite{2013arXiv1307.3049S} that is based 
-on a sub-sample of the \emph{Planck} COSMO sample \citep{2013arXiv1303.5080P} with 
-a median redshift of $z \approx 0.22$ (we use their PSZ(V) sample), which compares favorably 
-with our MultiDark $z = 0.2$ snapshot. The same comments regarding the small sample size of RHs, 
-selection biases, and systematic uncertainties in the luminosity measurements also apply here.}
+  relation, we use the result by \cite{2013arXiv1307.3049S} that is based on a
+  sub-sample of the \emph{Planck} COSMO sample \citep{2013arXiv1303.5080P} with
+  a median redshift of $z \approx 0.22$ (we use their PSZ(V) sample), which
+  compares favorably with our MultiDark $z = 0.2$ snapshot. The same comments
+  regarding the small sample size of RHs, selection biases, and systematic
+  uncertainties in the luminosity measurements also apply here.}
+
+\begin{figure*} 
+\centering
+\includegraphics[width=0.49\textwidth]{figures/PL_relation.eps}
+\includegraphics[width=0.49\textwidth]{figures/PSZ_relation.eps}
+\caption{Radio-to-X-ray and radio-to-SZ scaling relations in our extended CR model
+  (see main text for the details of the chosen parameters) compared with
+  observations.  \emph{Left.} $L_{1.4~\rmn{GHz}}-L_{\rmn{X,bol}}$ relation in
+  comparison to the observational sample taken from the literature and detailed
+  in Appendix~\ref{app:D}. We additionally show the detected signal of Mpc-scale 
+  diffuse emission in a stacked sample of radio-quiet galaxy clusters 
+  (green, \protect\citealp{2011ApJ...740L..28B}). 
+  \emph{Right.} $L_{1.4~\rmn{GHz}}-Y_{\rmn{SZ}}$ relation 
+  in comparison with
+  {\bf the PSZ(V) sample (direct integration method) 
+  of \protect\cite{2013arXiv1307.3049S}
+  together with the data points shown in their Fig.~13.}}
+\label{fig:PLSZ}
+\end{figure*}
 
@@
 
-In order to compare with observations, we select a
-particular realization of our extended CR model. To this end, we use the MultiDark cluster
-sample at $z=0.2$, which compares well with the redshift of the observational
-samples (see above and Appendix~\ref{app:D}). We divide our cluster sample
-randomly into radio-quiet and radio-loud clusters, assuming a ratio of $10\%$ of
-the latter (see next section). We use the turbulent propagation parameter $\gamma_{\rmn{tu}}$ to
-separate both populations. In radio-quiet clusters, we assign
-$\gamma_{\rmn{tu}}=1$, and in radio-loud clusters, we adopt randomly and
-uniformly $\gamma_{\rmn{tu}}$ values in the intervals $[40,80]$ and $[1,5]$ for
-NCCCs and CCCs, respectively.
+In order to compare with observations, we select a particular realization of our
+extended CR model. To this end, we use the MultiDark cluster sample at $z=0.2$,
+which compares well with the redshift of the observational samples (see above
+and Appendix~\ref{app:D}). We divide our cluster sample randomly into
+radio-quiet and radio-loud clusters, assuming a ratio of 10 per cent of the
+latter (see next section). In our model, we use the turbulent propagation
+parameter $\gamma_{\rmn{tu}}$ to separate both populations. In radio-quiet
+clusters, we assign $\gamma_{\rmn{tu}}=1$, and in radio-loud clusters, we adopt
+randomly and uniformly $\gamma_{\rmn{tu}}$ values in the intervals $[40,80]$ and
+$[1,5]$ for NCCCs and CCCs, respectively.
 
@@
 for radio-quiet clusters, we adopt randomly and uniformly distributed values of
-the central magnetic field $B_0$ in the intervals $[2.5,5.5]$~$\mu$G and
-$[5,10]$~$\mu$G for NCCCs and CCCs, respectively. To account for the potential
+the central magnetic field $B_0$ in the intervals $[2.5,5.5]$~$\umu$G and
+$[5,10]$~$\umu$G for NCCCs and CCCs, respectively. To account for the potential
 turbulent dynamo in radio-loud objects (characterized by a higher turbulent
 transport parameter in our model), we slightly increase $B_0$ in those objects
-and chose $B_0$ intervals of $[4.5,7.5]$~$\mu$G and $[7.5,12.5]$~$\mu$G for
+and chose $B_0$ intervals of $[4.5,7.5]$~$\umu$G and $[7.5,12.5]$~$\umu$G for
 NCCCs and CCCs, respectively.
@@
 can be arbitrarily varied by changing $g_{\rmn{CR}}$ as long as the resulting
-$X_{\rmn{CR}}$ respects the current observational constraints
-and remains below a few percents. As
-explained above, our choice of $g_{CR}=0.5$ ensures an average CR-to-thermal
-pressure of $2\%$ within $R_{500}$.
-
-Our model is sufficiently flexible to either mimic a cluster radio bimodality or not, depending 
-on the parameters adopted for the populations of radio-loud and radio-quiet
-objects. However, with the given model realization as in Fig.~\ref{fig:PLSZ}, the
-separation of the radio-loud and radio-quiet populations is substantially larger in
-the $L_{1.4~\rmn{GHz}}-L_{\rmn{X,bol}}$ plane than in the
-$L_{1.4~\rmn{GHz}}-Y_{\rmn{SZ}}$ plane, which exhibits almost a continuum
-distribution from radio-loud CCCs to the radio-quiet NCCCs. This is mainly
-because the bolometric X-ray emissivity scales with $\rho_{\rmn{gas}}^2$ while
-$Y_{\rmn{SZ}}\propto\rho_{\rmn{gas}}$ (which is only strictly valid for an
-isothermal gas distribution). 
-%As a consequence, the highly peaked gas profiles
-%of CCCs have less impact on $Y_{\rmn{SZ}}$ than on $L_{\rmn{X,bol}}$. 
-This is one plausible explanation for the observed discrepancy of the presence of a
-bimodality in $L_{1.4~\rmn{GHz}}-L_{\rmn{X,bol}}$ and the apparent absence of it
-in $L_{1.4~\rmn{GHz}}-Y_{\rmn{SZ}}$.
+$X_{\rmn{CR}}$ respects the current observational constraints and remains below
+a few percents. As explained above, our choice of $g_{CR}=0.5$ ensures an
+average CR-to-thermal pressure of 2 per cent within $R_{500}$.
+
+Our model is sufficiently flexible to either mimic a cluster radio bimodality or
+not, depending on the parameters adopted for the populations of radio-loud and
+radio-quiet objects. However, with the given model realization as in
+Fig.~\ref{fig:PLSZ}, the separation of the radio-loud and radio-quiet
+populations is substantially larger in the $L_{1.4~\rmn{GHz}}-L_{\rmn{X,bol}}$
+plane than in the $L_{1.4~\rmn{GHz}}-Y_{\rmn{SZ}}$ plane, which exhibits almost
+a continuum distribution from radio-loud CCCs to the radio-quiet NCCCs. This is
+mainly because the bolometric X-ray emissivity scales with $\rho_{\rmn{gas}}^2$
+while $Y_{\rmn{SZ}}\propto\rho_{\rmn{gas}}$ (which is only strictly valid for an
+isothermal gas distribution).  This is one plausible explanation for the
+observed discrepancy of the presence of a bimodality in
+$L_{1.4~\rmn{GHz}}-L_{\rmn{X,bol}}$ and the apparent absence of it in
+$L_{1.4~\rmn{GHz}}-Y_{\rmn{SZ}}$.
 
 The slope of our model depends on the different parameter choices and,
-particularly, on the relative differences introduced for the NCCC/CCC and 
-the radio-loud/quiet populations. However, we note that our
-$L_{1.4~\rmn{GHz}}-L_{\rmn{X,bol}}$ is slightly shallower than the 
-observed relation, more similar to the \cite{2009JCAP...09..024K} prediction.
-{\bf The same apply to the $L_{1.4~\rmn{GHz}}-Y_{\rmn{SZ}}$ scaling relation. 
-Potentially, this may hint at the contribution of a second, leptonic component
-that would steepen the slope of our model scaling relation at high mass.
-In particular, the finding of \cite{2013arXiv1306.4379C} that clusters do 
-seem to show a bimodaily at very high $Y_{\rmn{SZ}}$ may also be an hint 
-of an increasingly important leptonic component.} 
-{\bf However, we do not expect this component to alter significantly our conclusions
-regarding the luminosity functions of next sections for two main reasons. (i) It would be present 
-only in the radio-loud merging NCCC sample, i.e., the radio (giant) halos. And (ii) it would be dominant only 
-at very high masses because the dissipated energy that is available for energizing fossil electrons should 
-be a fraction of the thermal energy which scales with cluster mass as $E_\rmn{th}\propto M_{200}^{5/3}$ \citep[][for 
-magneto-turbulent re-acceleration models]{2005MNRAS.357.1313C}. In fact, in the $z = 0.2$ snapshot 
-of our mock sample, only $31$ radio-loud \mbox{NCCCs} are found for $M_{200}\geq5\times10^{14}~h_{70}^{-1}$~M$_{\odot}$, 
-where, e.g., turbulent reaccelerated RHs lie according to \cite{2010A&A...509A..68C}.
-
-As an example of a possible leptonic component, we boost the total flux of these 31 radio-loud NCCCs 
-according to $L_{1.4~\rmn{GHz, boosted}} = L_{1.4~\rmn{GHz, had}} + L_{1.4~\rmn{GHz, boost}}$,
-where $L_{1.4~\rmn{GHz, had}}$ is the value coming from our extended hadronic model
-and
-
+particularly, on the relative differences introduced for the NCCC/CCC and the
+radio-loud/quiet populations. However, we note that our
+$L_{1.4~\rmn{GHz}}-L_{\rmn{X,bol}}$ and $L_{1.4~\rmn{GHz}}-Y_{\rmn{SZ}}$ scaling
+relations are somewhat shallower than the observed relation, more similar to the
+model by \cite{2009JCAP...09..024K}.  {\bf This may hint at the contribution of
+  a second, leptonic component that would steepen the slope of our model scaling
+  relation at high mass.  In particular, the finding of
+  \cite{2013arXiv1306.4379C} that clusters do seem to show a bimodality at very
+  high $Y_{\rmn{SZ}}$ may also be an hint of an increasingly important leptonic
+  component. However, we do not expect this component to significantly alter our
+  conclusions regarding the luminosity functions of the next section for the
+  following reasons. (i) The leptonic component would only be present in the
+  radio-loud merging NCCC sample, i.e., the radio (giant) halos, and (ii) it
+  would only be dominant at very high masses because the dissipated energy that
+  is available for energizing fossil electrons should be a fraction of the
+  thermal energy which scales with cluster mass as $E_\rmn{th}\propto
+  M_{200}^{5/3}$ \citep[][for magneto-turbulent re-acceleration
+  models]{2005MNRAS.357.1313C}. In fact, our $z = 0.2$ mock sample, only
+  contains $31$ radio-loud \mbox{NCCCs} with
+  $M_{200}\geq5\times10^{14}~h_{70}^{-1}$~M$_{\odot}$, which is the mass range
+  of, e.g., turbulently reaccelerated RHs \citep{2010A&A...509A..68C}.
+
+  To visualize such a possible leptonic component, we boost the total flux of
+  these 31 radio-loud NCCCs according to $L_{1.4~\rmn{GHz, boosted}} =
+  L_{1.4~\rmn{GHz, had}} + L_{1.4~\rmn{GHz, boost}}$, where $L_{1.4~\rmn{GHz,
+      had}}$ is the radio luminosity of our extended hadronic component and
 \begin{equation}
-L_{1.4~\rmn{GHz, boost}} = L_{1.4~\rmn{GHz, had}} \times \left( \frac{M_{500}}{7.5\times10^{14}~h_{70}^{-1}~\rmn{M}_{\odot}} \right)^{2.3} \sim M_{500}^4 \, .
+L_{1.4~\rmn{GHz, boost}} = L_{1.4~\rmn{GHz, had}} \times 
+\left( \frac{M_{500}}{7.5\times10^{14}~h_{70}^{-1}~\rmn{M}_{\odot}} \right)^{2.3} \propto M_{500}^4 \, .
 \label{eg:leptonic_boost}
 \end{equation}
-
-We stress that this is just a phenomenological correction factor aiming to reproduce what 
-expected by turbulent re-acceleration $L_{1.4~\rmn{GHz}} \sim M_{500}^4$ 
-\citep{2007MNRAS.378.1565C,2013arXiv1306.4379C}.
-It is tied to the underling hadronic component such that we can use as
-guidance the results on the missing signal fraction obtained with the 
-surface brightness modeling. Additionally, in this way, it is tied to the
-CR and magnetic field properties of a given cluster.  
-As $L_{1.4~\rmn{GHz, had}} \sim M_{500}^{1.7}$,
-we adopt an additional mass scaling to reach the
-desired $L_{1.4~\rmn{GHz}} \sim M_{500}^4$.
-The resulting median (mean) boost is about
-32\% (47\%) of the hadronic component.\footnote{{\bf The modeling of
-   Coma and Abell~2163 suggests that a boost of about 35\% to 80\%
-   may be necessary. Note however that if we would allow flat CR profiles 
-   in turbulent, merging clusters as in \cite{2013arXiv1303.4746W},
-   the required fraction of leptonic component could be smaller.}} 
-The boosted population is shown in both panels of Fig.~\ref{fig:PLSZ}. The 
-corresponding scaling relations have slopes close to the ones of 
-the $L_{1.4~\rmn{GHz}}-L_{\rmn{X,bol}}$ and $L_{1.4~\rmn{GHz}}-Y_{\rmn{SZ}}$ 
-observational samples, respectively.}
+We consider this to be a phenomenological correction factor that aims at
+reproducing the observed relation $L_{1.4~\rmn{GHz}} \propto M_{500}^4$
+\citep{2007MNRAS.378.1565C,2013arXiv1306.4379C}. Possible physical realizations
+include turbulent re-acceleration of primary or secondary (hadronically
+produced) electrons \citep{2010arXiv1008.0184B} or re-acceleration of fossil
+electrons by means of diffusive shock acceleration
+\citep{kang11,kang12,pinzke13}. Here we tie the leptonic component to our
+modeling of the magnetic field and the hadronic emission component, which
+provides guidance for the missing signal fraction that we require by our surface
+brightness modeling. As $L_{1.4~\rmn{GHz, had}} \propto M_{500}^{1.7}$, we adopt
+an additional mass scaling to reach the desired $L_{1.4~\rmn{GHz}} \propto
+M_{500}^4$.  The resulting median (mean) boost is about 32 per cent (47 per
+cent) of the hadronic component.\footnote{{\bf The modeling of Coma and
+    Abell~2163 suggests that a boost of about 35 per cent to 80 per cent may be
+    necessary. However, if we allowed for flatter CR profiles in turbulent,
+    merging clusters as in \cite{2013arXiv1303.4746W}, the required fraction of
+    leptonic component could be smaller.}}  The boosted population is shown in
+both panels of Fig.~\ref{fig:PLSZ}. The corresponding scaling relations have
+slopes close to the ones of the $L_{1.4~\rmn{GHz}}-L_{\rmn{X,bol}}$ and
+$L_{1.4~\rmn{GHz}}-Y_{\rmn{SZ}}$ observational samples, respectively.}
+
+{\bf At low SZ fluxes, there are a considerable number of radio loud radio mini
+  halos visible in CCCs that fall above the observed
+  $L_{1.4~\rmn{GHz}}-Y_{\rmn{SZ}}$ relation by
+  \citet{2013arXiv1307.3049S}. However, this does not challenge our model
+  because (i) in order to characterize the radio halo emission,
+  \citet{2013arXiv1307.3049S} apply a low-pass filter to the radio data, which
+  minimizes any flux contribution from radio mini-halos that are comparable or
+  smaller than the chosen filter size and (ii) the radio mini-halo population in
+  the literature suffers from incompleteness effects \citep{Giacintucci}.}
 
@@
 and modeling at this stage, we do not attempt to fine-tune our model to the
-observations. {\bf In particular, we refrain to introduce any 
-mass-dependance in our free parameters at this stage.
-Additionally, we do not include the possible leptonic emission 
-component in the analysis of next sections, deferring the study of its 
-physical details and correlation to the hadronic one to future work. 
-The mock galaxy cluster sample used here is affected by incompleteness 
-in the highest-mass range because of the limited volume of the MultiDark simulation 
-(Paper~I). Only a small number of objects, lying in this mass range, would be affected 
-by such a correction, as shown above and in Fig.~\ref{fig:PLSZ}. These are not statistically 
-significant compared to the numbers we are going to discuss. Therefore, we prefer to point the 
-reader to the turbulent re-acceleration model predictions by \cite{2010A&A...509A..68C, 
-2012arXiv1210.1020C} for comparison, and to get a flavor of how an additional leptonic 
-component would change our predictions at that complementary mass scale.}
-
-As a final remark, we note that, interestingly, the detected signal of Mpc-scale diffuse 
-emission in a stacked sample of radio-quiet galaxy clusters (shown in green in the
-left plot of Fig.~\ref{fig:PLSZ}, \citealp{2011ApJ...740L..28B})
-agrees with the expected signal of our radio-quiet population.
+observations. {\bf In particular, we refrain from introducing any
+  mass-dependence in our free parameters at this stage.  Additionally, we do not
+  include the possible leptonic emission component in the analysis of next
+  section, deferring the study of its physical details and correlation to the
+  hadronic component to future work.  The mock cluster sample used here is
+  affected by incompleteness in the highest-mass range because of the limited
+  volume of the MultiDark simulation (Paper~I). Only a small number of objects
+  that lie in this mass range would be affected by such a correction, as
+  discussed above and shown in Fig.~\ref{fig:PLSZ}. These are not statistically
+  significant in comparison to the RH abundances that we will find in the next
+  section.}  Interestingly, the detected signal of Mpc-scale diffuse emission in
+a stacked sample of radio-quiet galaxy clusters (shown in green in the left plot
+of Fig.~\ref{fig:PLSZ}, \citealp{2011ApJ...740L..28B}) agrees with the expected
+signal of our radio-quiet population.
 
@@
 \includegraphics[width=0.85\textwidth]{figures/RLFs_1.4.eps}
-\caption{RH luminosity function (RLF) at 1.4~GHz. The top left panel shows
-  the RLF of our extended CR model (see main text for the details of the chosen
+\caption{RH luminosity function (RLF) at 1.4~GHz. The top left panel shows the
+  RLF of our extended CR model (see main text for the details of the chosen
   parameters) for different fractions of radio-loud clusters. Additionally shown
   is the contribution of radio-quiet and radio-loud populations to the total RLF
-  (assuming a fraction of $25\%$ and $1\%$ of radio-loud objects). The top right
-  panel shows the RLF obtained by applying the observed
+  (assuming a fraction of 25 per cent and 1 per cent of radio-loud objects). The
+  top right panel shows the RLF obtained by applying the observed
   $L_{1.4~\rmn{GHz}}-L_{\rmn{X,bol}}$ relation to the MultiDark clusters at $z =
@@
   $L_{1.4~\rmn{GHz}}-Y_{\rmn{SZ}, 500}$ relation to the MultiDark clusters at $z
-  = 0.2$, using $Y_{\rmn{SZ}, 500}$ of our our phenomenological gas model
-  for each cluster. The bottom right panel shows the comparison between the
-  three approaches for 10\% of radio-loud clusters. In all panels, we show the
-  NVSS survey RLF \citep{1999NewA....4..141G} with a median redshift of 
-  $z\approx 0.18$, corrected for the sample incompleteness and survey sky coverage. 
-  Horizontal error bars represent the mass bins while the vertical error bars are Poissonian 
-  uncertainties. The light gray line marked by the arrow estimates the incompleteness limit owing
-  to the adopted low-mass cut (in the construction of the mock cluster catalog, see Paper~I)
-  and the scatter in the halo luminosities.}
+  = 0.2$, using $Y_{\rmn{SZ}, 500}$ of our our phenomenological gas model for
+  each cluster. The bottom right panel shows the comparison between the three
+  approaches for 10 per cent of radio-loud clusters. In all panels, we show the NVSS
+  survey RLF \citep{1999NewA....4..141G} with a median redshift of $z\approx
+  0.18$, corrected for the sample incompleteness and survey sky coverage.
+  Horizontal error bars represent the mass bins while the vertical error bars
+  are Poissonian uncertainties. The light gray line marked by the arrow
+  estimates the incompleteness limit owing to the adopted low-mass cut (in the
+  construction of the mock cluster catalog, see Paper~I) and the scatter in the
+  halo luminosities.}
 \label{fig:RLF_1.4}
@@
 for a representative realization of our extended CR model (as in
-Section~\ref{sec:4}), and compare it with observational results. 
-The RLF is completely determined by the cluster mass function and the radio
+Section~\ref{sec:4}), and compare it with observational results.  The RLF is
+completely determined by the cluster mass function and the radio
 luminosity-to-mass relation, through $L_{1.4~\rmn{GHz}}-L_{ \rmn{X,bol}}$ or
 $L_{1.4~\rmn{GHz}}-Y_{\rmn{SZ}}$ in combination with our phenomenological gas
-model (see Paper~I). However, in the radio band there is the additional uncertainty of the
-fraction of radio-loud clusters. Thus, in Fig.~\ref{fig:RLF_1.4}, we also show
-the RLFs obtained by applying the $L_{1.4~\rmn{GHz}}-L_{\rmn{X,bol}}$ and
-$L_{1.4~\rmn{GHz}}-Y_{\rmn{SZ}}$ relations to simulated clusters of the
-MultiDark snapshot at $z = 0.2$, using our phenomenological gas model for
-$L_{\rmn{X,bol}}$ and $Y_{\rmn{SZ}, 500}$ of each cluster, respectively. Note
-that this procedure is {\em only} applied to halos defined as radio-loud
-clusters (which are by definition accounted for in the $L_{1.4~\rmn{GHz}}$
-scaling relations) and we assume a fraction of 100\%, 25\%, 10\%, 5\% and 1\% of
-radio-loud clusters. As evident from Fig.~\ref{fig:RLF_1.4}, this is different
-from our model for the radio luminosity: there we define a fraction of
-radio-loud clusters too, but the radio-quiet population also contributes to the
-RLF with an increasing fraction at low luminosities. This is exemplified in the
-top left plot of Fig.~\ref{fig:RLF_1.4}, which shows the contribution of
-radio-quiet and loud populations to the total RLF, assuming a fraction of $25\%$
-and $1\%$ of radio-loud objects.
+model (see Paper~I). However, in the radio band there is the additional
+uncertainty of the fraction of radio-loud clusters. Thus, in
+Fig.~\ref{fig:RLF_1.4}, we also show the RLFs obtained by applying the
+$L_{1.4~\rmn{GHz}}-L_{\rmn{X,bol}}$ and $L_{1.4~\rmn{GHz}}-Y_{\rmn{SZ}}$
+relations to our $z = 0.2$ mock catalog, which employs our phenomenological gas
+model for $L_{\rmn{X,bol}}$ and $Y_{\rmn{SZ}, 500}$ of each cluster,
+respectively. Note that this procedure is {\em only} applied to halos defined as
+radio-loud clusters (which are by definition accounted for in the
+$L_{1.4~\rmn{GHz}}$ scaling relations) and we assume a fraction of 1, 0.25, 0.1,
+0.05 and 0.01 of radio-loud clusters. As evident from Fig.~\ref{fig:RLF_1.4},
+this differs for our model scaling relations: there we also define a fraction of
+radio-loud clusters, but the radio-quiet population also contributes to the RLF
+with an increasing fraction at low luminosities. This is exemplified in the top
+left plot of Fig.~\ref{fig:RLF_1.4}, which shows the contribution of radio-quiet
+and loud populations to the total RLF, assuming a fraction of 0.25 and 0.01 of
+radio-loud objects.
 
 In Appendix~\ref{app:D}, we make an attempt to construct an RLF from existing
-X-ray flux-limited radio surveys. Few such studies exist, in particular, the cluster
-radio survey done with the National Radio Astronomy Observatory (NRAO) Very
-Large Array (VLA) sky survey (NVSS) at $1.4$~GHz of \cite{1999NewA....4..141G}
-and the survey with the Giant Metrewave Radio Telescope (GMRT) at $610$~MHz by
-\cite{VenturiGMRT_1,VenturiGMRT_2}. For the latter, one can also construct an RLF
-at 1.4~GHz using the corresponding RH follow-up measurements. The fractions of
-radio-loud clusters are about 6\%, 18\% and 24\% for the NVSS 1.4~GHz, GMRT
-610~MHz and GMRT 1.4~GHz samples, respectively. As explained in
-Appendix~\ref{app:D}, we use the 1.4~GHz NVSS RLF (with a median redshift of $z
-\approx 0.18$) as observational reference for our comparisons. We conclude that
-the observational determinations of the RLF is not very robust at this stage;
-the very different fractions of radio-loud clusters found in the different
-studies is one indicator of this. {\bf Recently, \cite{2013arXiv1306.3102K} published
-the results for an \emph{extended} GMRT survey where only one additional radio 
-mini-halo is found. This does not increase significantly the statistic for RLF 
-studies with respect to \cite{VenturiGMRT_1,VenturiGMRT_2}. We therefore decide to 
-stick with the 1.4~GHz NVSS RLF as reference in this work.}
+X-ray flux-limited radio surveys. Of the few existing studies, we select the
+cluster radio survey done with the National Radio Astronomy Observatory (NRAO)
+Very Large Array (VLA) sky survey (NVSS) at $1.4$~GHz of
+\cite{1999NewA....4..141G} and the survey with the Giant Metrewave Radio
+Telescope (GMRT) at $610$~MHz by \cite{VenturiGMRT_1,VenturiGMRT_2}. For the
+latter, we can also construct an RLF at 1.4~GHz using the corresponding RH
+follow-up measurements. The fractions of radio-loud clusters are about 0.06,
+0.18 and 0.24 for the NVSS 1.4~GHz, GMRT 610~MHz and GMRT 1.4~GHz samples,
+respectively. As explained in Appendix~\ref{app:D}, we use the 1.4~GHz NVSS RLF
+(with a median redshift of $z \approx 0.18$) as observational reference for our
+comparisons. We conclude that the observational determinations of the RLF is not
+very robust at this stage; the very different fractions of radio-loud clusters
+found in the different studies is one indicator of this. {\bf Recently,
+  \cite{2013arXiv1306.3102K} found only one additional radio mini-halo in an
+  \emph{extended} GMRT survey. This does not significantly increase the
+  statistics of RLF studies with respect to the sample of
+  \cite{VenturiGMRT_1,VenturiGMRT_2}. We therefore decided to keep the 1.4~GHz
+  NVSS RLF as our observational reference.}
 
@@
 and the RLFs based on observational scaling relations, particularly for
-radio-loud fractions between 10\% and 1\%. In particular, we verified that the
-cumulative number of RHs above a certain flux limit of the NVSS survey is well
-matched by our 10\%-loud fraction case, which will be used in the following
-section.  The RLF obtained from the $L_{1.4~\rmn{GHz}}-L_{\rmn{X,bol}}$ relation
-differs from the NVSS RLF at high luminosities, presumably caused by the large
-observed scatter.  On the other side, the RLF obtained from the
-$L_{1.4~\rmn{GHz}}-Y_{\rmn{SZ}}$ relation matches the NVSS result better. These
-results need to be consolidated by RLFs corrected for flux-incompleteness and
-simulations of larger cosmological volumes that are more complete at the
-high-mass end. Figure~\ref{fig:RLF_1.4} shows that it will be difficult to
-discriminate between different scenarios at high radio luminosities (or
-equivalently masses). Indeed, in the bottom right panel of
-Fig.~\ref{fig:RLF_1.4} we compare our RLF and the RLFs based on observational
-scaling relations for a 10\% fraction of radio-loud clusters to the NVSS
-RLF. This suggests that the low-luminosity (low-mass) clusters will be the most
-useful in disentangling between different models. This emphasizes the importance
-of conducting homogeneous, well controlled surveys of RHs with the
-Jansky VLA, ASKAP \citep{2011PASA...28..215N} and APERTIF
-\citep{2012JApA..tmp...34R} at 1.4 GHz and LOFAR at lower frequencies. Since the
-latter has already started to take data, it is extremely timely to present RLF
-predictions in this wavelength regime for our extended hadronic model, which 
-we will do next.
+radio-loud fractions between 10 per cent and 1 per cent. In particular, we
+verified that the cumulative number of RHs above a certain flux limit of the
+NVSS survey is well matched by the case of a radio-loud fraction of 10 per cent,
+which will be used in the following section.  The RLF obtained from the
+$L_{1.4~\rmn{GHz}}-L_{\rmn{X,bol}}$ relation differs from the NVSS RLF at high
+luminosities, presumably caused by the large observed scatter.  On the other
+side, the RLF obtained from the $L_{1.4~\rmn{GHz}}-Y_{\rmn{SZ}}$ relation
+matches the NVSS result better. These results need to be consolidated by RLFs
+corrected for flux-incompleteness and simulations of larger cosmological volumes
+that are more complete at the high-mass end. Figure~\ref{fig:RLF_1.4}
+demonstrates that it will be difficult to discriminate between different
+scenarios at high radio luminosities (or equivalently masses). Indeed, in the
+bottom right panel of Fig.~\ref{fig:RLF_1.4} we compare our RLF and the RLFs
+based on observational scaling relations for a 10 per cent fraction of
+radio-loud clusters to the NVSS RLF. This suggests that the low-luminosity
+(low-mass) clusters will be the most useful in disentangling between different
+models. This emphasizes the importance of conducting homogeneous, well
+controlled surveys of RHs with the Jansky VLA, ASKAP \citep{2011PASA...28..215N}
+and APERTIF \citep{2012JApA..tmp...34R} at 1.4 GHz and LOFAR at lower
+frequencies. Since the latter has already started to take data, it is extremely
+timely to present RLF predictions in this wavelength regime for our extended
+hadronic model, which we will do next.
 
@@
 with the same representative realization of our model as in Section~\ref{sec:4},
-with 10\% radio-loud clusters {\bf at all redshifts}. We show both the differential RLF (top left
-panel) and the cumulative number density (bottom left panel) at different
-redshifts (corresponding to different the MultiDark snapshots in Table~1 of Paper~I).  
-We note that the redshift evolution is almost entirely due to the
-$1/(\epsilon_{\rmn{B}}+\epsilon_{\rmn{CMB}})$ factor of equation~(\ref{eq:jnu})
-since $\epsilon_\rmn{CMB}\propto (1+z)^4$.  Our imposed mass cutoff of
-$M_{200}=10^{14}\,h^{-1}\,M_\odot$, which has been adopted to reliably model the
-cluster gas distribution (Paper~I), translates into a luminosity cutoff. This causes the
-differential luminosity function to turn over at the low-luminosity end and may
-artificially flatten the slope already at sightly higher luminosities than the
-luminosity maximum that indicates our formal incompleteness limit.  
-%{\bf Note that calibrating our model to 1.4~GHz observations may cause 
-%the uncertainty of possible intrinsic spectral features not considered
-%here (e.g. spectral steepening by CR transport, SZ decrement).}
-{\bf Note that calibrating our model to 1.4~GHz observations may cause an over- or
-underestimate of the number of low-frequency halos as a result of intrinsic
-spectral steepening (e.g., due to CR transport) or steeper leptonic spectra in
+with 10 per cent radio-loud clusters {\bf at all redshifts}. We show both the
+differential RLF (top left panel) and the cumulative number density (bottom left
+panel) at different redshifts (corresponding to different the MultiDark
+snapshots in Table~1 of Paper~I).  We note that the redshift evolution is almost
+entirely due to the $B^2/(B^2+B_{\rmn{CMB}}^2)$ factor of
+equation~(\ref{eq:jnu}) since $B_\rmn{CMB}\propto (1+z)^2$.  Our imposed mass
+cutoff of $M_{200}=10^{14}\,h^{-1}\,M_\odot$, which has been adopted to reliably
+model the cluster gas distribution (Paper~I), translates into a luminosity
+cutoff. This causes the differential luminosity function to turn over at the
+low-luminosity end and artificially flattens the slope already at sightly higher
+luminosities than the luminosity maximum that indicates our formal
+incompleteness limit.  {\bf Note that calibrating our model to 1.4~GHz
+  observations may cause an over- or underestimate of the number of
+  low-frequency halos as a result of intrinsic spectral flattening towards low
+  frequencies (e.g., due to CR transport) or steeper leptonic spectra in
   comparison to the hadronic component in the high-mass radio-loud NCCC
-population, respectively.} %--> still not clear to me
+  population, respectively.}
 
@@
   number density of RHs  $n(>L,z)$ (bottom left panel) at different redshifts $z$ (color
-  coded) for the model realization described in Section~\ref{sec:4} with a 10\%
+  coded) for the model realization described in Section~\ref{sec:4} with a 10 per cent
   fraction of radio-loud clusters. To obtain an analytical model for $n(L,z)$,
@@
 \emph{point-source} flux limit of $F_{5\sigma}^{\rmn{PS}}=0.5$~mJy
-\citep{2012JApA..tmp...34R} converted to a luminosity limit at a few representative
-redshifts. This flux limit is clearly an underestimate for nearby RHs, which
-extend over angular scales $\sim1$~deg, as e.g., in the case of the Coma radio
-halo. {\bf In order to make more reliable predictions, in the following, we will
+\citep{2012JApA..tmp...34R} converted to a luminosity limit at a few
+representative redshifts. This flux limit is clearly an underestimate for nearby
+RHs, which extend over angular scales $\sim1$~deg, as e.g., in the case of the
+Coma radio halo. {\bf In order to make more reliable predictions, we will
   calculate the RH flux limit with equation~(10) of \cite{2010A&A...509A..68C}
-based on the assumption that RHs emit about half of their total radio flux within 
-their half radius. In our sample, the typical radius within which half of the
-radio flux is emitted is $R_{500}/4$, and we require that the flux within it is
-higher than $F_{5\sigma}^{\rmn{PS}}$. The median $R_{500}$ of our sample 
-is about $0.8$~$h_{70}^{-1}$~Mpc at all redshifts. This translates to a flux limit 
-of about $48, 14, 3.5$ and $2.5$~mJy at $z = 0.1, 0.2, 0.6$ and $1$, respectively.}
+  that is based on the assumption that RHs emit about half of their total radio
+  flux within their half radius. In our sample, the typical radius within which
+  half of the radio flux is emitted is $R_{500}/4$, and we require that the flux
+  within this radius is higher than $F_{5\sigma}^{\rmn{PS}}$. The median
+  $R_{500}$ of our sample is about $0.8$~$h_{70}^{-1}$~Mpc at all
+  redshifts. This translates to a flux limit of about $48, 14, 3.5$ and
+  $2.5$~mJy at $z = 0.1, 0.2, 0.6$ and $1$, respectively.}
 
@@
   survey at 120~MHz. We show the result of the model realization described in
-  Section~\ref{sec:4} using all clusters and adopting a fraction of 10\% of
+  Section~\ref{sec:4} using all clusters and adopting a fraction of 10 per cent of
   radio-loud clusters (black solid line). Additionally, we show the result
-  obtained by using the 10\% radio-loud clusters \emph{only} (black dashed
+  obtained by using the 10 per cent radio-loud clusters \emph{only} (black dashed
   line). We also show the differential contribution to the RLF in redshift
@@
 Fig.~\ref{fig:RLF_120_flux} for the model realization described in
-Section~\ref{sec:4} with a 10\% fraction of radio-loud clusters (black solid
+Section~\ref{sec:4} with a 10 per cent fraction of radio-loud clusters (black solid
 line). We limit the integral to luminosities $\log_{10} L_{120~\rmn{MHz}}
@@
 about diffuse radio emission on group scales in particularly at these redshifts,
-which motivates our upper redshift limit. {\bf Note also that at these high redshifts, 
+which motivates our upper redshift limit. \qc{\bf Note also that at these high redshifts, 
 the analytical model for the evolving RLF gives spurious counts due to the 
@@
 slices to the total flux function. We contrast this to the flux function using
-\emph{only} the subsample of 10\% radio-loud clusters (black dashed line). This
+\emph{only} the subsample of 10 per cent radio-loud clusters (black dashed line). This
 was obtained by constructing the corresponding RLF and repeating the steps above
@@
 
-{\bf The LOFAR Tier~1 survey at 120~MHz should be able to detect about
-$600$ clusters hosting radio giant and mini halos, considering the hadronic 
-component only. We refer the reader to \cite{2010A&A...509A..68C} 
-for predictions for giant halos in the turbulent 
-re-acceleration scenario. We note that those are at a complementary,
-and higher, mass scale with respect to ours which are limited by the
-volume of the MultiDark simulation (see Paper~I).}
-
-The precise number of detections depends strongly on the 
-underlying assumptions. There are two main uncertainties
-in our model: the fraction of radio-loud to radio-quiet clusters and the
-corresponding luminosities as well as our assumed RH modeling in low-mass
-clusters (which are not yet known to host RHs). The fraction of radio-loud to
-radio-quiet clusters is determined from a given (degenerate) set of model
-parameters that include $\gamma_{\rmn{th}}$, $B_{0}$, $\alpha_{B}$,
-$g_{\rmn{CR}}$, or equivalently $X_{CR}$. The fraction of radio-loud clusters
-mostly affects the number of medium-to-high luminosity RHs (as can be seen from
-the 1.4~GHz RLFs in the top left panel of Fig.~\ref{fig:RLF_1.4}). The total
-number of RHs is dominated by low-luminosity RHs. While this may suggest that
-the radio-loud fraction is of minor importance for the detectable numbers,
-instead the opposite is the case. Because of the flux limit, only the most
-luminous clusters at each redshift are observable so that the total number of
-detectable RHs scales almost linearly with the radio-loud fraction.
-
-%We asses the second uncertainty by comparing
-%the total result of our model (black solid line) with the RLF obtained only from
-%the radio-loud population (black dashed line). Their difference somehow shows
-%the uncertainty in the modeling for a fixed fraction of radio-loud clusters as
-%all the configuration between the solid and dashed lines can be virtually
-%realized changing the relative normalization of the loud and quiet populations.
+{\bf The LOFAR Tier~1 survey at 120~MHz should be able to detect about $600$
+  clusters hosting radio giant and mini halos, considering the hadronic
+  component only. We refer the reader to \cite{2010A&A...509A..68C} for
+  predictions for giant halos in the turbulent re-acceleration scenario. We note
+  that those are complementary, because they address a larger mass scale with
+  respect to ours, which are limited by the volume of the MultiDark simulation
+  (see Paper~I).}
+
+The precise number of detections depends strongly on the underlying
+assumptions. There are two main uncertainties in our model: the fraction of
+radio-loud to radio-quiet clusters and the corresponding luminosities as well as
+our assumed RH modeling in low-mass clusters (which are not yet known to host
+RHs). The fraction of radio-loud to radio-quiet clusters is determined from a
+given (degenerate) set of model parameters that include $\gamma_{\rmn{th}}$,
+$B_{0}$, $\alpha_{B}$, $g_{\rmn{CR}}$, or equivalently $X_{CR}$. The fraction of
+radio-loud clusters mostly affects the number of medium-to-high luminosity RHs
+(as can be seen from the 1.4~GHz RLFs in the top left panel of
+Fig.~\ref{fig:RLF_1.4}). The total number of RHs is dominated by low-luminosity
+RHs. While this may suggest that the radio-loud fraction is of minor importance
+for the number of detectable RHs, the opposite is the case. Because of the flux
+limit, only the most luminous clusters at each redshift are observable so that
+the total number of detectable RHs scales almost linearly with the radio-loud
+fraction.
 
@@
 The reason for this lies in the steep halo mass function which ensures that that
-clusters above a given cutoff (that is either physically motivated or
+clusters above a given cutoff (which is either physically motivated or
 observationally realized through a survey flux limit) dominate the total number
@@
 realized through CR streaming transport in {\em relaxed} clusters, which appears
-to be in conflict with the observation that giant radio halos are hosted by merging
-{\em turbulent} clusters.\footnote{{\bf Note, however, that \cite{2013arXiv1303.4746W} 
-   arrive at a different conclusion finding that the increase of turbulence promotes 
-   outward streaming more than inward advection, therefore allowing flat CR 
-   distributions in turbulent clusters.}} 
-{\bf Moreover, the hadronic model fails to explain the emission in the outer parts of the 
-Coma halo at 352~MHz where not even the extreme case of
-a flat CR profile is enough to explain the emission as of purely hadronic origin.} 
-This motivates us to suggest the following new \emph{hybrid} hadronic-leptonic scenario.
+to be in conflict with the observation that giant radio halos are hosted by
+merging {\em turbulent} clusters.\footnote{{\bf Note, however, that
+    \cite{2013arXiv1303.4746W} arrive at a different conclusion finding that the
+    increase of turbulence promotes outward streaming more than inward
+    advection, therefore allowing flat CR distributions in turbulent clusters.}}
+{\bf Moreover, the hadronic model fails to explain the emission in the outer
+  parts of the Coma halo at 352~MHz where not even the extreme case of a flat CR
+  profile is sufficient to explain the emission as of purely hadronic origin.}
+This motivates us to suggest the following new \emph{hybrid} hadronic-leptonic
+scenario.
 \begin{enumerate}
@@
 
-{\bf We consider an example of a phenomenological correction factor representing the 
-additional leptonic component in an hybrid scenario. We show how this can affect the 
-population of high-mass radio-loud NCCCs, i.e, the giant halos, bringing its scaling relations 
-in agreement with the the available observational samples. However, due to the nature 
-of our approach, i.e., the use of an $N$-body simulation which is volume-limited, only few 
-tens of objects would be affected by such a correction. These are not statistically significant 
-against our whole sample and, therefore, we refrain from adding this component in the 
-subsequent analysis, leaving its theoretical modeling to future work.}
-
-Assuming a {\bf redshift-independent} fraction of 10\% radio-loud clusters, we demonstrate that our 
-model matches the NVSS RH luminosity function (RLF). However, the
-high-luminosity tail of our model RLF is subject to cosmic variance because of
-the comparably small simulation volume of $1
-h^{-3}\,\rmn{Gpc}^3$. Interestingly, the RLF derived from the
+Assuming a {\bf redshift-independent} fraction of 10 per cent radio-loud
+clusters, we demonstrate that our model matches the NVSS RH luminosity function
+(RLF). However, the high-luminosity tail of our model RLF is subject to cosmic
+variance because of the comparably small simulation volume of $1 h^{-3}
+\,\rmn{Gpc}^3$. Interestingly, the RLF derived from the
 $L_{1.4~\rmn{GHz}}-L_{\rmn{X,bol}}$ relation differs at high radio luminosities
@@
 density. {\bf Given our assumptions, we would expect the LOFAR Tier~1 survey at
-120~MHz to detect about $600\times\rmn{\emph{loud~fraction}[\%]/10}$ 
+120~MHz to detect about $600\times (\rmn{\emph{radio-loud~fraction}/0.1})$ 
 hadronically-generated radio giant and mini halos.} 
@@
 This demonstrates the potential of LOFAR, and other next-generation
-low-sensitivity radio instruments such as APERTIF, ASKAP, EVLA and SKA, in
+high-sensitivity radio instruments such as APERTIF, ASKAP, EVLA and SKA, in
 determining the RLF properties. In combination with future X-ray missions like
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{acknowledgements}
 \section*{Acknowledgments}
@@
 1.4~GHz radio map of Coma.  We also thank Miguel-Angel Perez Torres and Huub 
-R{\"o}ttgering for the useful discussions and advices.  Finally, we thank the MultiDark 
+R{\"o}ttgering for the useful discussions.  Finally, we thank the MultiDark 
 database people, in particular Adrian Partl and Kristin Riebe. 
@@
 Ames Research Center.
-%\end{acknowledgements}
 
@@
   identical for the exact solution and its approximation, while there is a small
-  difference of about 9\% in the NCCC case. We adopt $\alpha=2.3$.}
+  difference of about 9 per cent in the NCCC case. We adopt $\alpha=2.3$.}
 \label{fig:REXexactVSfake}
@@
 energy density, and $B_{\rmn{c}} = \sqrt{ 8 \pi
-  \epsilon_{B_{\rmn{c}}}} \simeq 31 \left( \nu/\rmn{GHz} \right)~\mu$G. 
+  \epsilon_{B_{\rmn{c}}}} \simeq 31 \left( \nu/\rmn{GHz} \right)~\umu$G. 
 %
@@
 uncertainties for X-ray and radio luminosities are not reported, we adopt a
-$10\%$ uncertainty. Our final RH sample has a median redshift of
+10 per cent uncertainty. Our final RH sample has a median redshift of
 $z\approx0.18$. In the left panel of Fig.~\ref{fig:PLSZ}, we show the
@@
 is composed by 50 clusters and we can also build a corresponding RLF at 1.4~GHz
-using the 12 present RHs. The fraction of radio-loud clusters is about 6\%, 18\%
-and 24\% for the NVSS 1.4~GHz, GMRT 610~MHz and GMRT 1.4~GHz sample,
+using the 12 present RHs. The fraction of radio-loud clusters is about 0.06, 0.18
+and 0.24 for the NVSS 1.4~GHz, GMRT 610~MHz and GMRT 1.4~GHz sample,
 respectively. The corresponding median redshift is 0.18, 0.26 and 0.25. We
@@
 indicator of the large uncertainty in the RLF.
-
-{\bf Note that, as explained in 
-Section~\ref{sec:5}, we refrain from using the newly published results of \cite{2013arXiv1306.3102K} 
-on an \emph{extended} GMRT survey because they find only one additional radio 
-mini-halo with respect to \cite{VenturiGMRT_1,VenturiGMRT_2}.}
 
@@
 %  through the MultiDark database.
+
+Coma story:
+
+\citet{2012arXiv1207.3025B} pointed out problems of the hadronic model
+for the limited parameter space $\alpha\gtrsim2.6$, while adopting a much
+more extended azimuthally averaged RH profile at 352~MHz
+\citep{2011MNRAS.412....2B} than the one used in the present study so far
+\citep{1997A&A...321...55D}. The problem of reproducing the spectral steepening
+claimed in the Coma RH is somewhat mitigated when considering the negative flux
+bowl due to the SZ effect that causes the measured RH spectrum to experience a
+sharp cutoff towards high frequencies \citep[][which both use X-ray inferred
+pseudo-pressure profiles and assume an accretion shock radius to estimate the
+Compton-$y$ parameter of Coma]{2002A&A...396L..17E, 2004A&A...413...17P}. To
+overcome this uncertainty, we use the observed SZ decrement of the Coma cluster
+by the \citet{2012arXiv1208.3611P}. We obtain the total SZ flux by integrating
+the Compton-$y$ profile up to the RH's radial extent at 352~MHz of about
+$1.3$~$h_{0.7}^{-1}$~Mpc \citep[][which provide the most sensitive observation
+of the Coma RH to date]{2011MNRAS.412....2B}. We show the resulting SZ decrement
+in Fig.~\ref{fig:SZ_Coma} together with the Coma RH flux at different
+frequencies \citep{2003A&A...397...53T}. An intrinsic power-law radio spectrum,
+$(\nu/\nu_{0})^{-\alpha/2}$, exhibits a sharp cutoff at frequencies around 3-5
+GHz due to the negative flux contribution of the SZ effect. Hence, we fit the
+resulting RH spectrum with different spectral indices, $2.1\lesssim
+\alpha\lesssim2.9$. We allow the normalization and $\nu_{0}$ to vary freely and
+impose a lower floor to the reported uncertainties of 10 per cent to account for
+possible systematics. The resulting reduced-$\chi^{2}$ values (shown in the
+legend of Fig.{\ }\ref{fig:SZ_Coma}) underline the discrepancy between RH flux
+measurements at different frequencies---in particular for interferometric
+measurements that have to reconstruct a large fraction of the flux due to the
+``missing zero spacing'' problem. At $\sim5$~GHz, the SZ decrement is comparable
+to the measured RH flux. {\bf Recently, \cite{2013arXiv1309.1820B}, using the
+correlation between $Y_{\rmn{SZ}}$ and the low-frequency radio-halo 
+brightness \citep{2011MNRAS.412....2B,2012arXiv1208.3611P}, 
+found that the SZ decrement at $\sim5$~GHz is below 10 per cent.
+This is clearly in contrast with the results from our simplified approach,
+at least for $\alpha \ge 2.7$. However, as pointed out by \cite{2013arXiv1309.1820B}, 
+the low-frequency observations by \cite{2011MNRAS.412....2B} imply that the Coma
+radio halo is significantly larger than what thought before. This could dramatically
+impact the estimations regarding the SZ decrement and more sensitive
+observations are needed to better clarify this issue. On this, we want to stress once more 
+that CR streaming can also cause spectral steepening \citep{2013arXiv1303.4746W}.
+}
+
+\begin{figure} 
+\centering
+\includegraphics[width=\columnwidth]{figures/SZ_Coma.eps}
+\caption{Observed RH fluxes of the Coma cluster as compiled by
+  \citet{2003A&A...397...53T}. Intrinsic power-law radio spectra are modified at
+  high frequencies by means of the SZ decrement (dotted), which we estimate from
+  observations by the \citet{2012arXiv1208.3611P} and integrate within the
+  radial extend of the RH at 352 MHz. We fit the data points with SZ-modified
+  power-law spectra with different spectral indices $\alpha$ and impose a lower
+  floor to the reported uncertainties of 10\% to account for possible
+  systematics. The corresponding reduced-$\chi^{2}$ values demonstrate the
+  discrepancy between RH flux measurements at different frequencies.}
+\label{fig:SZ_Coma}
+\end{figure}
+
+ %Interestingly, as shown in Fig.~\ref{fig:SB_Coma}, the 1.4
+%GHz profile can be brought into agreement with the low-frequency profile by
+%choosing a lower zero level (Rudnick, priv. comm.; see also
+%\citealp{2012arXiv1208.3611P}), however at the expense of emerging super-cluster
+%emission from the Coma region on scales much more extended than the RH
+%\citep{2007ApJ...659..267K}. Conversely, by increasing the zero level of the 352
+%MHz data \citep{2011MNRAS.412....2B} reconciles that profile with the narrower
+%profile of \citet{1997A&A...321...55D} (Fig.~\ref{fig:SB_Coma}), possibly at the
+%expense of an implausibly high zero level, judging from the more sensitive 352
+%MHz data (Rudnick, priv.{\ }comm.).  Assuming for a moment that the choices of
+%zero level at both frequencies were indeed correct, this would imply a larger
+%extent of the RH at lower frequencies. A combination of better data at 1.4 GHz,
+%careful cleaning of the emission of tailed radio galaxies, and a full accounting
+%of the resulting systematic uncertainties into the total error budget are
+%certainly needed to fully clarify the observational situation.
+%
+
+%\begin{figure} 
+%\centering
+%\includegraphics[width=\columnwidth]{figures/SB_Coma_norm_band.eps}
+%\caption{Surface brightness profiles of the Coma RH, normalized at 300 kpc.  We
+% show a 352 MHz profile that was corrected for residual point-source
+%  contamination by applying the multi-resolution filtering technique as well as
+%  adopting the X-ray center for the RH profile (blue, Rudnick,
+%  priv. comm.). This profile declines at a slightly faster rate towards the
+%  outskirts than the profile used by \citet[][black
+%  squares]{2012arXiv1207.3025B}. Increasing the zero level of the (more
+%  sensitive) 352 MHz data (blue open squares) to the level of 1.4 GHz halo data
+%  \citep[red filled circles,][]{1997A&A...321...55D} brings those data into
+%  agreement. Alternatively, lowering the zero level of the 1.4 GHz data (red
+%  open circles, Rudnick, priv. comm.) allows to match the much larger radial
+%  extend of the low-frequency data. Those systematic uncertainties need to be
+%  carefully addressed in future observations and accounted for in the error
+%  budget that currently only account for statistical uncertainties (grey shaded
+%  band, \citealp{2012arXiv1207.3025B}).}
+%\label{fig:SB_Coma}
+%\end{figure}
+
+ {\bf Despite the available
+observational input on the magnetic field in clusters ($B_0$, $ \alpha_{\rmn{B}}$), 
+which is, however, very limited, the parameter space that the physics modeled here 
+demands is quite large encompassing also $\gamma_{\rmn{tu}}$ and the CR acceleration 
+efficiency function. Particularly, a large region of the ($\gamma_{\rmn{tu}}$,
+$\alpha_{\rmn{B}}$) parameter space is available for the analyzed radio
+mini-halos (note also that the parameters $\gamma_{\rmn{tu}}$ and
+$\alpha_{\rmn{B}}$ are degenerate). Future work on all known RHs may 
+provide better insight.}
+% 
+%This is in especially
+%true because of the comparably large parameter space that the physics modeled
+%here demands and which encompasses our parametrization of the magnetic field
+%($B_0$, $ \alpha_{\rmn{B}}$), $\gamma_{\rmn{tu}}$, and the CR acceleration efficiency
+%function. Particularly, a large region of the ($\gamma_{\rmn{tu}}$,
+%$\alpha_{\rmn{B}}$) parameter space is available for the analyzed radio
+%mini-halos (note also that the parameters $\gamma_{\rmn{tu}}$ and
+%$\alpha_{\rmn{B}}$ are degenerate). Future work on all known RHs may provide
+%better insight, but is beyond the scope of this work.
+%
+
+{\bf We consider an example of a phenomenological correction factor representing the 
+additional leptonic component in an hybrid scenario. We show how this can affect the 
+population of high-mass radio-loud NCCCs, i.e, the giant halos, bringing its scaling relations 
+in agreement with the the available observational samples. However, due to the nature 
+of our approach, i.e., the use of an $N$-body simulation which is volume-limited, only few 
+tens of objects would be affected by such a correction. These are not statistically significant 
+against our whole sample and, therefore, we refrain from adding this component in the 
+subsequent analysis, leaving its theoretical modeling to future work.}
+
+{\bf Note that, as explained in 
+Section~\ref{sec:5}, we refrain from using the newly published results of \cite{2013arXiv1306.3102K} 
+on an \emph{extended} GMRT survey because they find only one additional radio 
+mini-halo with respect to \cite{VenturiGMRT_1,VenturiGMRT_2}.}

### 2013-09-30 paper2.tex

@@
   emission. However, the short cooling length of synchrotron-emitting electrons
-  at GHz frequencies ($\lesssim 100$~kpc) challenges theoretical model to
+  at GHz frequencies ($\lesssim 100$~kpc) challenges theoretical models to
   explain the large-scale radio emission that extends over several Mpcs and
@@
 \section*{Acknowledgments}
-We thank Anders Pinzke for many useful discussions. We thank Lawrence Rudnick
-and Shea Brown for a reanalysis of their 352~MHz radio map of Coma, and for useful 
-discussions. We thank Matteo Murgia for kindly providing the radio surface brightness 
-profiles of Ophiuchucs and Abell~2163 that have been recomputed with respect to the 
-Reiprich \& B\"{o}ringher (2002) cluster positions, and Wolfgang Reich for providing the 
-1.4~GHz radio map of Coma.  We also thank Miguel-Angel Perez Torres and Huub 
-R{\"o}ttgering for the useful discussions.  Finally, we thank the MultiDark 
-database people, in particular Adrian Partl and Kristin Riebe. 
-F.Z.{\ }acknowledges the CSIC financial support as a JAE-Predoc grant of the 
-program ``Junta para la Ampliaci\'on de Estudios'' co-financed by the FSE. 
+We thank Anders Pinzke for many useful discussions and Lawrence Rudnick and Shea
+Brown for a reanalysis of their 352~MHz radio map of Coma, and for useful
+discussions. We thank Matteo Murgia for kindly providing the radio surface
+brightness profiles of Ophiuchucs and Abell~2163 that have been recomputed with
+respect to the Reiprich \& B\"{o}ringher (2002) cluster positions, and Wolfgang
+Reich for providing the 1.4~GHz radio map of Coma.  We also thank Miguel-Angel
+Perez Torres and Huub R{\"o}ttgering for the useful discussions.  Finally, we
+thank the MultiDark database people, in particular Adrian Partl and Kristin
+Riebe.  F.Z.{\ }acknowledges the CSIC financial support as a JAE-Predoc grant of
+the program ``Junta para la Ampliaci\'on de Estudios'' co-financed by the FSE.
 F.Z.{\ }acknowledges the hospitality of the Leiden Observatory during his stay.
-F.Z.{\ }and F.P.{\ } thank the support of the Spanish MICINN's Consolider-Ingenio 2010 Programme 
-under grant MultiDark CSD2009-00064. C.P.{\ }gratefully acknowledges financial support
-of the Klaus Tschira Foundation. The MultiDark Database used in this paper and
-the web application providing online access to it were constructed as part of
-the activities of the German Astrophysical Virtual Observatory as result of a
-collaboration between the Leibniz-Institute for Astrophysics Potsdam (AIP) and
-the Spanish MultiDark Consolider Project CSD2009-00064. The Bolshoi and
-MultiDark simulations were run on the NASA's Pleiades supercomputer at the NASA
-Ames Research Center.
+F.Z.{\ }and F.P.{\ } thank the support of the Spanish MICINN's
+Consolider-Ingenio 2010 Programme under grant MultiDark CSD2009-00064. C.P.{\
+}gratefully acknowledges financial support of the Klaus Tschira Foundation. The
+MultiDark Database used in this paper and the web application providing online
+access to it were constructed as part of the activities of the German
+Astrophysical Virtual Observatory as result of a collaboration between the
+Leibniz-Institute for Astrophysics Potsdam (AIP) and the Spanish MultiDark
+Consolider Project CSD2009-00064. The Bolshoi and MultiDark simulations were run
+on the NASA's Pleiades supercomputer at the NASA Ames Research Center.
 
@@
 \bibliographystyle{mn2e}
-%\bibliographystyle{aa}
 \bibliography{bib_file}

### 2013-10-01 paper2.tex

@@
 Fig.~\ref{fig:RLF_120_flux} for the model realization described in
-Section~\ref{sec:4} with a 10 per cent fraction of radio-loud clusters (black solid
-line). We limit the integral to luminosities $\log_{10} L_{120~\rmn{MHz}}
+Section~\ref{sec:4} with a 10 per cent fraction of radio-loud clusters (black
+solid line). We limit the integral to luminosities $\log_{10} L_{120~\rmn{MHz}}
 \geq 29.25$. Our redshift integration extends from $z_{1} = 0.018$, the redshift
 of the closest known RH in Perseus, to $z_{2} = 2$. As shown in
-Fig.~\ref{fig:RLF_120_flux}, already redshifts $z\gtrsim1$ do not
-significantly contribute to the flux function. Additionally, there are large
-theoretical uncertainties since our gas model is not calibrated for these
-redshifts (and implied low-mass range) and very little is observationally known
-about diffuse radio emission on group scales in particularly at these redshifts,
-which motivates our upper redshift limit. \qc{\bf Note also that at these high redshifts, 
-the analytical model for the evolving RLF gives spurious counts due to the 
-non-perfect matching with simulations in this regime.}
+Fig.~\ref{fig:RLF_120_flux}, already redshifts $z\gtrsim1$ do not significantly
+contribute to the flux function. Additionally, there are large theoretical
+uncertainties since our gas model is not calibrated for these redshifts (and
+implied low-mass range) and very little is observationally known about diffuse
+radio emission on group scales in particularly at these redshifts, which
+motivates our upper redshift limit. {\bf Note also that at these high redshifts,
+  the analytical fit to the evolving RLF slightly overproduces the simulation
+  number counts.}
 

### 2013-10-03 paper2.tex
last Fabio

@@
 \emph{critical} density of the Universe. We adopt density parameters of
-$\Omega_{\rmn{m}}=0.3$, $\Omega_{\Lambda}=0.7$ and today's Hubble constant of
+$\Omega_{\rmn{m}}=0.27$, $\Omega_{\Lambda}=0.73$ and today's Hubble constant of
 $H_0 = 100 \, h_{70}$~km~s$^{-1}$~Mpc$^{-1}$ where $h_{70} = 0.7$.
@@
   comparison of the RLF fits (top) and the cumulative number density of the
-  MultiDark samples (bottom) to the constrained analytical model. The bottom panels of these
-  two panels show the relative differences $\Delta n / n =
-  (n_{\rmn{analytical}} - n_{\rmn{fit}})/n_{\rmn{fit}}$. Additionally shown is
-  the LOFAR Tier~1 \emph{point-source} flux limit of
+  MultiDark samples (bottom) to the constrained analytical model.  \qc{The bottom panels 
+  of these two panels show the relative differences $\Delta n / n =
+  (n_{\rmn{analytical}} - n_{\rmn{fit}})/n_{\rmn{fit}}$ (top) and
+  $\Delta n / n = (n_{\rmn{analytical}} - n_{\rmn{simulation}})/n_{\rmn{simulation}}$ (bottom).} 
+  Additionally shown is the LOFAR Tier~1 \emph{point-source} flux limit of
   $F_{5\sigma}^{\rmn{PS}}=0.5$~mJy \citep{2012JApA..tmp...34R} converted to a
@@
 
-%\begin{figure*}[t!]
-%\centering
-%\includegraphics[width=0.99\textwidth]{figures/CR_profiles_simple_comparison.eps}
-%\caption{Comparison of different CR profiles.
-The left plot shows the \emph{simple} advective $C_{\rmn{adv}}$ of equation~(\ref{eq:Csimple_1}) for the Coma and Perseus cases both neglecting the temperature dependence ($\rho$) and considering it ($P$).
-The temperature profile of Coma has been modified so that it follows the characteristic decline toward the cluster periphery.
-Perseus is a CCC and it is characterized by a central dip in the temperature profile which may importantly affect the final CR profile, so we adopt the temperature profile as given in \cite{2003ApJ...590..225C} ($P_{1}$).
-We also show the case where we only apply the characteristic decline toward the cluster periphery ($P_{2}$).
-The other two right plots show the \emph{transport} case of equation~(\ref{eq:Ctransport}) for Coma and Perseus for different values of $\gamma_{\rmn{tu}}$ in comparison with the \emph{simple} case.
-Additionally shown is the result in case of $C(R)=C_{\rmn{semi-analytical}}(R)=\tilde{C}(R)\rho_{\rmn{gas}}(R)/m_{\rmn{p}}$ where $\tilde{C}(R)$ is the mass-dependent universal normalization CR profile found in cosmological simulations \citep{2010MNRAS.409..449P}.
-The \emph{simple} and \emph{semi-analytical} profiles are normalized at $C_{0}=C(0)$.
-In the transport case, we fix the CR number for $\gamma_{\rmn{tu}}=100$ using equation~(36) of \cite{2011A&A...527A..99E}, while integrating the cluster volume within $R_{200}$, and require CR number conservation during CR streaming.
-We adopt $\alpha=2.3$.}
-%\label{fig:simpleVStransport}
-%\end{figure*}
-%
-%
-%In Fig.~\ref{fig:simpleVStransport}, we show a comparison between $C_{\rmn{adv}}$ of 
-%equation~(\ref{eq:Csimple_1}) and $C$ of equation~(\ref{eq:Ctransport}) considering the 
-%NCCC Coma and CCC Perseus cases. While for Coma we adopt the $\beta$-profile of 
-%\citet{1992A&A...259L..31B}, Perseus needs a double-$\beta$ profile. We adopt both the 
-%approximation $P(R)/P_{0}=n_{\rmn{e}}(R)/n_{0}$ and the proper Perseus pressure profile 
-%(X-ray data from \citealp{2003ApJ...590..225C}). Note that the \cite{2011A&A...527A..99E} 
-%formalism is exact only for the approximation $P(R)/P_{0}=n_{\rmn{e}}(R)/n_{0}$ where $n_{\rmn{e}}$ 
-%is a $\beta$-profile. Nevertheless, we adopt the above formulae also for Perseus as a good approximation, 
-%i.e., we adopt $C(R)=C_{0}(\rho_{\rmn{CR}}(R)/\rho_{\rmn{CR},0})^{\beta_{\rmn{CR}}}$
-%within $R_{\pm}$ of equation~(\ref{eq:Rpm}), and $C(R) = C(R_{\pm})$ for $R > R_{+}$ 
-%and $R < R_{-}$, respectively; we take $R_{\rmn{c}}$ in equation~(\ref{eq:Rpm}) to be equal to the Perseus 
-%double-$\beta$ profile outer core radius and fix $\beta_{\rmn{cl}}=0.8$. The relevant 
-%parameters are $\gamma_{\rmn{tu}}$ and the exponential factor of equation~(\ref{eg:rhoCR_1}). 
-%In fact, as we will see in the following, the two radii $R_{\pm}$ are not critically affected 
-%by the detail of $\eta(R)$. Therefore, despite the approximation, this approach captures the 
-%main CR transport effects also for the Perseus case. 
-%
-%In Fig.~\ref{fig:simpleVStransport}, we additionally show the result in case 
-%$C(R)=C_{\rmn{semi-analytical}}(R)=\tilde{C}(R)\rho_{\rmn{\rmn{gas}}}(R)/m_{\rmn{p}}$ 
-%where $\tilde{C}(R)$ is the universal normalization CR profile found in cosmological 
-%simulations \citep{2010MNRAS.409..449P}. As expected, the CR profile driven by 
-%simulations is characterized by a more centrally peaked profile with respect to the 
-%analytical case. Note also the flatter profile of Coma with respect to Perseus, which 
-%reflects their NCCC and CCC classification, respectively. Finally, the effect of varying 
-%the turbulent cluster state by means of $\gamma_{\rmn{tu}}$ can be clearly appreciated.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 We exclude RXCJ1314.4-2515 and Z7160 because they lack bolometric X-ray measurements. 
-%and A2626 because its X-ray luminosity is very low placing it as an extreme outlier. 
 We add to our sample the clusters Ophiuchus, A2029 and A1835
@@
 
-%Finally, in Fig.~\ref{fig:RLF1.4_fluxNVSS}, we compare the cumulative number of RHs above a certain flux limit at 1.4~GHz obtained by our model realization described in Section~\ref{sec:4}, adopting a fraction of 10\% of radio-loud clusters, with the NVSS survey result (data is taken from \citealp{2010A&A...509A..68C}).
-We repeat the steps done in Section~5.2 in order to obtain an analytical model describing the number of RHs expected in our model per unit luminosity and per unit comoving volume.
-We then use equationx~(\ref{eq:NtotRH}) to calculate the cumulative number of RHs above a given flux.
-The luminosity integration is limited to $\log_{10} L_{1.4~\rmn{120MHz}} \geq 28$ to exclude the turn-over at low luminosities caused by incompleteness, while the redshift integration is limited to the range covered by the NVSS survey of $0.044 \leq z \leq 0.2$ \citep{1999NewA....4..141G}.
-We find a agreement comparison between our model and the observational result of the NVSS survey.
-
-%\begin{figure} 
-%\centering
-%\includegraphics[width=0.48\textwidth]{figures/RLF_1.4_flux_NVSS.eps}
-%\caption{Cumulative number of RHs above a certain flux limit in an all-sky
-%  survey at 1.4~GHz for $0.044 \leq z \leq 0.2$. The black line shows the result 
-%  obtained with the model realization described in Section~\ref{sec:4}, adopting 
-%  a fraction of 10\% of radio-loud clusters, integrating within the redshift range covered 
-%  by the NVSS survey (black data points).}
-%\label{fig:RLF1.4_fluxNVSS}
-%\end{figure}
-
 \end{appendix}
@@
 \end{document}
-
-%\del{In comparing with observations, we take as reference
-%  \cite{2010MNRAS.406.1773M}. There are however many other works on this scaling
-%  relation, in particularly we recall the HIghest X-ray FLUx Galaxy Cluster
-%  Sample (HIFLUGCS; \citealp{2002ApJ...567..716R}), the REXCESS
-%  \citep{2009A&A...498..361P} sample, and the 115 \emph{Chandra} cluster sample
-%  of \cite{2007ApJ...668..772M}. The results on the slopes of the $L-M$ relation
-%  can vary significantly between different samples. While the slope of
-%  \cite{2010MNRAS.406.1773M} is $1.63\pm0.06$,
-%  \cite{2002ApJ...567..716R}\footnote[8]{Note that we are quoting the
-%    $L_{\rmn{bol}}-M_{200}$ results of \cite{2002ApJ...567..716R}.} found values
-%  between $1.72\pm0.09$ and $1.89\pm0.08$ (depending on the fit procedure, which
-%  also can affect the final result), \cite{2009A&A...498..361P} found
-%  $2.08\pm0.13$ and \cite{2007ApJ...668..772M} found
-%  $1.96\pm0.10$. Discrepancies can come from many different sources but likely
-%  are to be charged to the selection criteria of the different samples as
-%  recently pointed out also by \cite{2011arXiv1109.3708R}. Samples which differ
-%  in, e.g., redshift distribution, mass range, fitting procedure and biases
-%  treatment, and, of course, the used instrument, can give and actually gave
-%  different results. Therefore we decided to take as reference the
-%  \cite{2010MNRAS.406.1773M} work because it is very recent, their sample is
-%  composed by a high number (238) of objects, and, more importantly, their
-%  analysis takes self-consistently into account all selection effects,
-%  covariances, systematic uncertainties and the cluster mass function (see also
-%  \citealp{2010MNRAS.406.1759M}).}
-
-% original abstract:
-
-%  The underlying physics of giant and mini radio halos in galaxy clusters is
-%  still an open question, which becomes more pressing with the growing number of
-%  detections. Assuming that the radio-emitting electrons are generated in
-%  hadronic cosmic ray (CR) interactions with protons of the intra-cluster medium
-%  explains the radio emission in mini halos (Perseus, Ophiuchus). By contrast,
-%  the hadronic model either fails to explain the extended emission of giant
-%  radio halos (Coma at low frequencies) or would require a flat CR profile 
-%  (Coma and A2163 at 1.4~GHz). Flat CR distributions are only expected to be realized 
-%  through CR streaming in {\em relaxed} clusters---in conflict with the observation that
-%  radio halos are hosted by merging {\em turbulent} clusters. This motivates us
-%  to propose a new hybrid model, where (i) mini halos are primarily of hadronic
-%  origin, (ii) giant halos experience a transition from central hadronic
-%  emission to peripheral leptonic emission due to Fermi I or II re-acceleration
-%  of fossil or hadronically produced electrons, and (iii) steep spectrum radio
-%  sources are mainly of leptonic origin. {\bf We use a mock galaxy cluster catalog
-%  built from the MultiDark $N$-body $\Lambda$CDM simulation that matches 
-%  Sunyaev-Zel'dovich and X-ray scaling relations and luminosity function.} 
-%  Because of CR streaming and the different scalings of the
-%  X-ray luminosity, $L_{\rmn{X}}$, and the Sunyaev-Zel'dovich flux, $Y$, with
-%  gas density, our model can simultaneously reproduce the observed bimodality of
-%  radio-loud and radio-quiet clusters at the same $L_{\rmn{X}}$ as well as the
-%  unimodal distribution of radio-halo luminosity versus $Y$; thereby suggesting
-%  a physical solution to this apparent contradiction. For a plausible fraction
-%  of 10\% radio-loud clusters, our model matches the NVSS radio-halo luminosity
-%  function. Constructing an analytical radio-halo luminosity function, we
-%  demonstrate the unique prospects for low-frequency radio surveys (such as the
-%  LOFAR Tier 1 survey) to detect $\sim3500$ radio halos back to redshift two and
-%  to probe the underlying physics of radio halos. We make our cosmologically 
-%  complete multi-frequency mock catalogs for the (non-)thermal cluster emission 
-%  at different redshifts publicly and freely available on-line
-%  through the MultiDark database.
-
-Coma story:
-
-\citet{2012arXiv1207.3025B} pointed out problems of the hadronic model
-for the limited parameter space $\alpha\gtrsim2.6$, while adopting a much
-more extended azimuthally averaged RH profile at 352~MHz
-\citep{2011MNRAS.412....2B} than the one used in the present study so far
-\citep{1997A&A...321...55D}. The problem of reproducing the spectral steepening
-claimed in the Coma RH is somewhat mitigated when considering the negative flux
-bowl due to the SZ effect that causes the measured RH spectrum to experience a
-sharp cutoff towards high frequencies \citep[][which both use X-ray inferred
-pseudo-pressure profiles and assume an accretion shock radius to estimate the
-Compton-$y$ parameter of Coma]{2002A&A...396L..17E, 2004A&A...413...17P}. To
-overcome this uncertainty, we use the observed SZ decrement of the Coma cluster
-by the \citet{2012arXiv1208.3611P}. We obtain the total SZ flux by integrating
-the Compton-$y$ profile up to the RH's radial extent at 352~MHz of about
-$1.3$~$h_{0.7}^{-1}$~Mpc \citep[][which provide the most sensitive observation
-of the Coma RH to date]{2011MNRAS.412....2B}. We show the resulting SZ decrement
-in Fig.~\ref{fig:SZ_Coma} together with the Coma RH flux at different
-frequencies \citep{2003A&A...397...53T}. An intrinsic power-law radio spectrum,
-$(\nu/\nu_{0})^{-\alpha/2}$, exhibits a sharp cutoff at frequencies around 3-5
-GHz due to the negative flux contribution of the SZ effect. Hence, we fit the
-resulting RH spectrum with different spectral indices, $2.1\lesssim
-\alpha\lesssim2.9$. We allow the normalization and $\nu_{0}$ to vary freely and
-impose a lower floor to the reported uncertainties of 10 per cent to account for
-possible systematics. The resulting reduced-$\chi^{2}$ values (shown in the
-legend of Fig.{\ }\ref{fig:SZ_Coma}) underline the discrepancy between RH flux
-measurements at different frequencies---in particular for interferometric
-measurements that have to reconstruct a large fraction of the flux due to the
-``missing zero spacing'' problem. At $\sim5$~GHz, the SZ decrement is comparable
-to the measured RH flux. {\bf Recently, \cite{2013arXiv1309.1820B}, using the
-correlation between $Y_{\rmn{SZ}}$ and the low-frequency radio-halo 
-brightness \citep{2011MNRAS.412....2B,2012arXiv1208.3611P}, 
-found that the SZ decrement at $\sim5$~GHz is below 10 per cent.
-This is clearly in contrast with the results from our simplified approach,
-at least for $\alpha \ge 2.7$. However, as pointed out by \cite{2013arXiv1309.1820B}, 
-the low-frequency observations by \cite{2011MNRAS.412....2B} imply that the Coma
-radio halo is significantly larger than what thought before. This could dramatically
-impact the estimations regarding the SZ decrement and more sensitive
-observations are needed to better clarify this issue. On this, we want to stress once more 
-that CR streaming can also cause spectral steepening \citep{2013arXiv1303.4746W}.
-}
-
-\begin{figure} 
-\centering
-\includegraphics[width=\columnwidth]{figures/SZ_Coma.eps}
-\caption{Observed RH fluxes of the Coma cluster as compiled by
-  \citet{2003A&A...397...53T}. Intrinsic power-law radio spectra are modified at
-  high frequencies by means of the SZ decrement (dotted), which we estimate from
-  observations by the \citet{2012arXiv1208.3611P} and integrate within the
-  radial extend of the RH at 352 MHz. We fit the data points with SZ-modified
-  power-law spectra with different spectral indices $\alpha$ and impose a lower
-  floor to the reported uncertainties of 10\% to account for possible
-  systematics. The corresponding reduced-$\chi^{2}$ values demonstrate the
-  discrepancy between RH flux measurements at different frequencies.}
-\label{fig:SZ_Coma}
-\end{figure}
-
- %Interestingly, as shown in Fig.~\ref{fig:SB_Coma}, the 1.4
-%GHz profile can be brought into agreement with the low-frequency profile by
-%choosing a lower zero level (Rudnick, priv. comm.; see also
-%\citealp{2012arXiv1208.3611P}), however at the expense of emerging super-cluster
-%emission from the Coma region on scales much more extended than the RH
-%\citep{2007ApJ...659..267K}. Conversely, by increasing the zero level of the 352
-%MHz data \citep{2011MNRAS.412....2B} reconciles that profile with the narrower
-%profile of \citet{1997A&A...321...55D} (Fig.~\ref{fig:SB_Coma}), possibly at the
-%expense of an implausibly high zero level, judging from the more sensitive 352
-%MHz data (Rudnick, priv.{\ }comm.).  Assuming for a moment that the choices of
-%zero level at both frequencies were indeed correct, this would imply a larger
-%extent of the RH at lower frequencies. A combination of better data at 1.4 GHz,
-%careful cleaning of the emission of tailed radio galaxies, and a full accounting
-%of the resulting systematic uncertainties into the total error budget are
-%certainly needed to fully clarify the observational situation.
-%
-
-%\begin{figure} 
-%\centering
-%\includegraphics[width=\columnwidth]{figures/SB_Coma_norm_band.eps}
-%\caption{Surface brightness profiles of the Coma RH, normalized at 300 kpc.  We
-% show a 352 MHz profile that was corrected for residual point-source
-%  contamination by applying the multi-resolution filtering technique as well as
-%  adopting the X-ray center for the RH profile (blue, Rudnick,
-%  priv. comm.). This profile declines at a slightly faster rate towards the
-%  outskirts than the profile used by \citet[][black
-%  squares]{2012arXiv1207.3025B}. Increasing the zero level of the (more
-%  sensitive) 352 MHz data (blue open squares) to the level of 1.4 GHz halo data
-%  \citep[red filled circles,][]{1997A&A...321...55D} brings those data into
-%  agreement. Alternatively, lowering the zero level of the 1.4 GHz data (red
-%  open circles, Rudnick, priv. comm.) allows to match the much larger radial
-%  extend of the low-frequency data. Those systematic uncertainties need to be
-%  carefully addressed in future observations and accounted for in the error
-%  budget that currently only account for statistical uncertainties (grey shaded
-%  band, \citealp{2012arXiv1207.3025B}).}
-%\label{fig:SB_Coma}
-%\end{figure}
-
- {\bf Despite the available
-observational input on the magnetic field in clusters ($B_0$, $ \alpha_{\rmn{B}}$), 
-which is, however, very limited, the parameter space that the physics modeled here 
-demands is quite large encompassing also $\gamma_{\rmn{tu}}$ and the CR acceleration 
-efficiency function. Particularly, a large region of the ($\gamma_{\rmn{tu}}$,
-$\alpha_{\rmn{B}}$) parameter space is available for the analyzed radio
-mini-halos (note also that the parameters $\gamma_{\rmn{tu}}$ and
-$\alpha_{\rmn{B}}$ are degenerate). Future work on all known RHs may 
-provide better insight.}
-% 
-%This is in especially
-%true because of the comparably large parameter space that the physics modeled
-%here demands and which encompasses our parametrization of the magnetic field
-%($B_0$, $ \alpha_{\rmn{B}}$), $\gamma_{\rmn{tu}}$, and the CR acceleration efficiency
-%function. Particularly, a large region of the ($\gamma_{\rmn{tu}}$,
-%$\alpha_{\rmn{B}}$) parameter space is available for the analyzed radio
-%mini-halos (note also that the parameters $\gamma_{\rmn{tu}}$ and
-%$\alpha_{\rmn{B}}$ are degenerate). Future work on all known RHs may provide
-%better insight, but is beyond the scope of this work.
-%
-
-{\bf We consider an example of a phenomenological correction factor representing the 
-additional leptonic component in an hybrid scenario. We show how this can affect the 
-population of high-mass radio-loud NCCCs, i.e, the giant halos, bringing its scaling relations 
-in agreement with the the available observational samples. However, due to the nature 
-of our approach, i.e., the use of an $N$-body simulation which is volume-limited, only few 
-tens of objects would be affected by such a correction. These are not statistically significant 
-against our whole sample and, therefore, we refrain from adding this component in the 
-subsequent analysis, leaving its theoretical modeling to future work.}
-
-{\bf Note that, as explained in 
-Section~\ref{sec:5}, we refrain from using the newly published results of \cite{2013arXiv1306.3102K} 
-on an \emph{extended} GMRT survey because they find only one additional radio 
-mini-halo with respect to \cite{VenturiGMRT_1,VenturiGMRT_2}.}

### 2013-10-03 paper2.tex
text corrected and dereddened

@@
 \includegraphics[width=0.47\textwidth,height=0.3\textheight]{figures/CumDensityL_LOFAR_1.eps}
-\caption{RH luminosity function $n(L,z)$ at 120~MHz (top left panel) and cumulative
-  number density of RHs  $n(>L,z)$ (bottom left panel) at different redshifts $z$ (color
-  coded) for the model realization described in Section~\ref{sec:4} with a 10 per cent
-  fraction of radio-loud clusters. To obtain an analytical model for $n(L,z)$,
-  we fit the logarithm of the RLF at each $z$ with a second-order polynomial and
-  constrain the evolution of the three free parameters to follow a linear
-  function in $1+z$ (see main text for details). The right panels show the
-  comparison of the RLF fits (top) and the cumulative number density of the
-  MultiDark samples (bottom) to the constrained analytical model.  \qc{The bottom panels 
-  of these two panels show the relative differences $\Delta n / n =
-  (n_{\rmn{analytical}} - n_{\rmn{fit}})/n_{\rmn{fit}}$ (top) and
-  $\Delta n / n = (n_{\rmn{analytical}} - n_{\rmn{simulation}})/n_{\rmn{simulation}}$ (bottom).} 
-  Additionally shown is the LOFAR Tier~1 \emph{point-source} flux limit of
+\caption{RH luminosity function $n(L,z)$ at 120~MHz (top left panel) and
+  cumulative number density of RHs $n(>L,z)$ (bottom left panel) at different
+  redshifts $z$ (color coded) for the model realization described in
+  Section~\ref{sec:4} with a 10 per cent fraction of radio-loud clusters. To
+  obtain an analytical model for $n(L,z)$, we fit the logarithm of the RLF at
+  each $z$ with a second-order polynomial and constrain the evolution of the
+  three free parameters to follow a linear function in $1+z$ (see main text for
+  details). The right panels show the comparison of the RLF fits (top) and the
+  cumulative number density of the MultiDark samples (bottom) to the constrained
+  analytical model.  The bottom panels on the right-hand side show the relative
+  differences $\Delta n / n = (n_{\rmn{analytical}} -
+  n_{\rmn{fit}})/n_{\rmn{fit}}$ (top) and $\Delta n / n = (n_{\rmn{analytical}}
+  - n_{\rmn{simulation}})/n_{\rmn{simulation}}$ (bottom).  Additionally shown is
+  the LOFAR Tier~1 \emph{point-source} flux limit of
   $F_{5\sigma}^{\rmn{PS}}=0.5$~mJy \citep{2012JApA..tmp...34R} converted to a
@@
   gray line marked by the arrow estimates the incompleteness limit owing to the
-  adopted low-mass cut (in the construction of the mock cluster catalog, see Paper~I)
-  and the scatter in the halo luminosities.}
+  adopted low-mass cut (in the construction of the mock cluster catalog, see
+  Paper~I) and the scatter in the halo luminosities.}
 \label{fig:RLF_120}

### 2013-10-05 paper2.tex
very last Fabio

@@
 \documentclass[useAMS,usenatbib]{mn2e}
-%
-%\def\del#1{{\bf  [deleted text] }} \def\new#1{{\bf #1}} \def\remark#1{{\bf  [remark: #1]}}
-%\def\del#1{} \def\new#1{#1} \def\remark#1{}
 
 \def\del#1{{}}
-%\def\del#1{{\bf (DELETED TEXT)}}
 \def\C#1{{\bf #1}}
-%\def\C#1{#1}
 
@@
     Ophiuchus) can be explained by radio-emitting electrons that are generated
-    in hadronic cosmic ray (CR) interactions with protons of the intra-cluster
+    in hadronic cosmic ray (CR) interactions with protons of the intracluster
     medium. By contrast, the hadronic model either fails to explain the extended
@@
   of galaxies proves the existence of relativistic electrons and magnetic fields
-  permeating the intra-cluster medium (ICM). This diffuse cluster radio emission
+  permeating the intracluster medium (ICM). This diffuse cluster radio emission
   can be observationally classified into two phenomena: peripheral radio relics,
@@
 \medskip
-%\begin{tabular}{cccccccc}
-%\hline
-%\phantom{\Big|}
-%name & $z$ & $D$ & $\Delta d$ & $L_{1.4~\rmn{GHz},~\rmn{obs}}$ & model parameters & $L_{1.4~\rmn{GHz},~\rmn{model}}$ & references \\
-%\phantom{\Big|}
-%           &   & [$h_{70}^{-1}$~Mpc] & [$h_{70}^{-1}$~Mpc] & $10^{31}$ [$h_{70}^{-2}$~erg~s$^{-1}$~Hz$^{-1}$] & $\gamma_{\rmn{tu}}$, $\alpha_{\rmn{B}}$ & $10^{31}$ [$h_{70}^{-2}$~erg~s$^{-1}$~Hz$^{-1}$] & \\
-%\hline \\[-0.5em]
-%Coma           & $0.023$ & $101$ & $2.15$ & $0.72$  & 1, 0.6  & 0.86 &  [1, 2, 3]   \\
-%               &         &       &        &                        & 4, 0.3  & 0.90  &  \\
-%A2163         & $0.203$ & $962$ & $2.07$ & $15.36$     & 1, 0.3  & 13.43  &  [3, 4]  \\
-%\hline \\[-0.5em]
-%Perseus        & $0.018$ & $78$   & $0.15$ & $4.40$ & 3, 0.4   & 4.80 &  [3, 5, 6]  \\
-%               &         &        &        &                       & 100, 0.3 & 3.97 &  \\
-%Ophiuchucs     & $0.028$ & $121$  & $0.41$ & $0.19$       & 5, 0.7   & 0.19  &  [3, 4] \\
-%               &         &        &        &                       & 100, 0.3 & 0.23 &   \\[0.5em]
 \begin{tabular}{lcrrc}
@@
 \centering
-%\includegraphics[width=0.75\textwidth]{figures/SB_profiles_ALL.eps}
 %

### 2013-10-10 paper2.tex
last

@@
 \author[F. Zandanel, C. Pfrommer and F. Prada]{
-Fabio Zandanel$^{1,2}$, Christoph Pfrommer$^{3}$ and Francisco Prada$^{4,5,2}$\\
-$^{1}$GRAPPA Institute, University of Amsterdam, Science Park 904, 1098XH Amsterdam, Netherlands, f.zandanel@uva.nl\\
-$^{2}$Instituto de Astrof\'{\i}sica de Andaluc\'{\i}a (CSIC), Glorieta de la Astronom\'{\i}a, E-18080 Granada, Spain\\
+Fabio Zandanel$^{1,2}$, Christoph Pfrommer$^{3}$ and Francisco Prada$^{4,5,1}$\\
+$^{1}$Instituto de Astrof\'{\i}sica de Andaluc\'{\i}a (CSIC), Glorieta de la Astronom\'{\i}a, E-18080 Granada, Spain\\
+$^{2}$Now at GRAPPA Institute, University of Amsterdam, Science Park 904, 1098XH Amsterdam, Netherlands, f.zandanel@uva.nl\\
 $^{3}$Heidelberg Institute for Theoretical Studies, Schloss-Wolfsbrunnenweg 35, D-69118 Heidelberg, Germany, christoph.pfrommer@h-its.org\\
@@
   \sum_{i=1}^{3} \Delta_{i} \mathcal{B}_{1/(1+q^2)} \left(
-    \frac{\alpha_{i}-1}{2},\frac{3-\alpha_{i}}{2} \right).
+    \frac{\alpha_{i}-2}{2},\frac{3-\alpha_{i}}{2} \right).
 \end{equation}
@@
 F.Z.{\ }and F.P.{\ } thank the support of the Spanish MICINN's
-Consolider-Ingenio 2010 Programme under grant MultiDark CSD2009-00064. C.P.{\
-}gratefully acknowledges financial support of the Klaus Tschira Foundation. The
+Consolider-Ingenio 2010 Programme under grant MultiDark CSD2009-00064, AYA10-21231. 
+C.P.{\ }gratefully acknowledges financial support of the Klaus Tschira Foundation. The
 MultiDark Database used in this paper and the web application providing online
@@
 Leibniz-Institute for Astrophysics Potsdam (AIP) and the Spanish MultiDark
-Consolider Project CSD2009-00064. The Bolshoi and MultiDark simulations were run
-on the NASA's Pleiades supercomputer at the NASA Ames Research Center.
+Consolider Project CSD2009-00064, AYA10-21231. The Bolshoi and MultiDark simulations 
+were run on the NASA's Pleiades supercomputer at the NASA Ames Research Center.
 

### 2013-10-10 paper2.tex
last

@@
   top right panel shows the RLF obtained by applying the observed
-  $L_{1.4~\rmn{GHz}}-L_{\rmn{X,bol}}$ relation to the MultiDark clusters at $z =
+  $L_{1.4~\rmn{GHz}}-L_{\rmn{X,bol}}$ relation \qc{from in Fig.~\ref{fig:PLSZ}} to the MultiDark clusters at $z =
   0.2$, using our phenomenological gas model for $L_{\rmn{X,bol}}$ of each
@@
   left panel shows the RLF obtained by applying the observed
-  $L_{1.4~\rmn{GHz}}-Y_{\rmn{SZ}, 500}$ relation to the MultiDark clusters at $z
+  $L_{1.4~\rmn{GHz}}-Y_{\rmn{SZ}, 500}$ relation \qc{from in Fig.~\ref{fig:PLSZ}} to the MultiDark clusters at $z
   = 0.2$, using $Y_{\rmn{SZ}, 500}$ of our our phenomenological gas model for
@@
 Fig.~\ref{fig:RLF_1.4}, we also show the RLFs obtained by applying the
-$L_{1.4~\rmn{GHz}}-L_{\rmn{X,bol}}$ and $L_{1.4~\rmn{GHz}}-Y_{\rmn{SZ}}$
-relations to our $z = 0.2$ mock catalog, which employs our phenomenological gas
+\qc{observed} $L_{1.4~\rmn{GHz}}-L_{\rmn{X,bol}}$ and $L_{1.4~\rmn{GHz}}-Y_{\rmn{SZ}}$
+relations \qc{(as in Fig.~\ref{fig:PLSZ})} to our $z = 0.2$ mock catalog, which employs our phenomenological gas
 model for $L_{\rmn{X,bol}}$ and $Y_{\rmn{SZ}, 500}$ of each cluster,
@@
 (RLF). However, the high-luminosity tail of our model RLF is subject to cosmic
-variance because of the comparably small simulation volume of $1 h^{-3}
+variance because of the comparably small simulation volume of $1~h^{-3}
 \,\rmn{Gpc}^3$. Interestingly, the RLF derived from the

### 2013-10-10 paper2.tex
changed title in Appendix A
dereddened text

@@
   top right panel shows the RLF obtained by applying the observed
-  $L_{1.4~\rmn{GHz}}-L_{\rmn{X,bol}}$ relation \qc{from in Fig.~\ref{fig:PLSZ}} to the MultiDark clusters at $z =
-  0.2$, using our phenomenological gas model for $L_{\rmn{X,bol}}$ of each
-  cluster; again for different percentages of radio-loud clusters.  The bottom
-  left panel shows the RLF obtained by applying the observed
-  $L_{1.4~\rmn{GHz}}-Y_{\rmn{SZ}, 500}$ relation \qc{from in Fig.~\ref{fig:PLSZ}} to the MultiDark clusters at $z
-  = 0.2$, using $Y_{\rmn{SZ}, 500}$ of our our phenomenological gas model for
-  each cluster. The bottom right panel shows the comparison between the three
-  approaches for 10 per cent of radio-loud clusters. In all panels, we show the NVSS
-  survey RLF \citep{1999NewA....4..141G} with a median redshift of $z\approx
-  0.18$, corrected for the sample incompleteness and survey sky coverage.
-  Horizontal error bars represent the mass bins while the vertical error bars
-  are Poissonian uncertainties. The light gray line marked by the arrow
-  estimates the incompleteness limit owing to the adopted low-mass cut (in the
-  construction of the mock cluster catalog, see Paper~I) and the scatter in the
-  halo luminosities.}
+  $L_{1.4~\rmn{GHz}}-L_{\rmn{X,bol}}$ relation {\bf (see Fig.~\ref{fig:PLSZ})}
+  to the MultiDark clusters at $z = 0.2$, using our phenomenological gas model
+  for $L_{\rmn{X,bol}}$ of each cluster; again for different percentages of
+  radio-loud clusters.  The bottom left panel shows the RLF obtained by applying
+  the observed $L_{1.4~\rmn{GHz}}-Y_{\rmn{SZ}, 500}$ relation {\bf (see
+    Fig.~\ref{fig:PLSZ})} to the MultiDark clusters at $z = 0.2$, using
+  $Y_{\rmn{SZ}, 500}$ of our our phenomenological gas model for each
+  cluster. The bottom right panel shows the comparison between the three
+  approaches for 10 per cent of radio-loud clusters. In all panels, we show the
+  NVSS survey RLF \citep{1999NewA....4..141G} with a median redshift of
+  $z\approx 0.18$, corrected for the sample incompleteness and survey sky
+  coverage.  Horizontal error bars represent the mass bins while the vertical
+  error bars are Poissonian uncertainties. The light gray line marked by the
+  arrow estimates the incompleteness limit owing to the adopted low-mass cut (in
+  the construction of the mock cluster catalog, see Paper~I) and the scatter in
+  the halo luminosities.}
 \label{fig:RLF_1.4}
@@
 uncertainty of the fraction of radio-loud clusters. Thus, in
-Fig.~\ref{fig:RLF_1.4}, we also show the RLFs obtained by applying the
-\qc{observed} $L_{1.4~\rmn{GHz}}-L_{\rmn{X,bol}}$ and $L_{1.4~\rmn{GHz}}-Y_{\rmn{SZ}}$
-relations \qc{(as in Fig.~\ref{fig:PLSZ})} to our $z = 0.2$ mock catalog, which employs our phenomenological gas
-model for $L_{\rmn{X,bol}}$ and $Y_{\rmn{SZ}, 500}$ of each cluster,
-respectively. Note that this procedure is {\em only} applied to halos defined as
-radio-loud clusters (which are by definition accounted for in the
-$L_{1.4~\rmn{GHz}}$ scaling relations) and we assume a fraction of 1, 0.25, 0.1,
-0.05 and 0.01 of radio-loud clusters. As evident from Fig.~\ref{fig:RLF_1.4},
-this differs for our model scaling relations: there we also define a fraction of
-radio-loud clusters, but the radio-quiet population also contributes to the RLF
-with an increasing fraction at low luminosities. This is exemplified in the top
-left plot of Fig.~\ref{fig:RLF_1.4}, which shows the contribution of radio-quiet
-and loud populations to the total RLF, assuming a fraction of 0.25 and 0.01 of
-radio-loud objects.
+Fig.~\ref{fig:RLF_1.4}, we also show the RLFs obtained by applying the observed
+$L_{1.4~\rmn{GHz}}-L_{\rmn{X,bol}}$ and $L_{1.4~\rmn{GHz}}-Y_{\rmn{SZ}}$
+relations {\bf (as in Fig.~\ref{fig:PLSZ})} to our $z = 0.2$ mock catalog, which
+employs our phenomenological gas model for $L_{\rmn{X,bol}}$ and $Y_{\rmn{SZ},
+  500}$ of each cluster, respectively. Note that this procedure is {\em only}
+applied to halos defined as radio-loud clusters (which are by definition
+accounted for in the $L_{1.4~\rmn{GHz}}$ scaling relations) and we assume a
+fraction of 1, 0.25, 0.1, 0.05 and 0.01 of radio-loud clusters. As evident from
+Fig.~\ref{fig:RLF_1.4}, this differs for our model scaling relations: there we
+also define a fraction of radio-loud clusters, but the radio-quiet population
+also contributes to the RLF with an increasing fraction at low
+luminosities. This is exemplified in the top left plot of
+Fig.~\ref{fig:RLF_1.4}, which shows the contribution of radio-quiet and loud
+populations to the total RLF, assuming a fraction of 0.25 and 0.01 of radio-loud
+objects.
 
@@
 
-\section{Cosmic Ray Modeling Details}
+\section{Cosmic Ray Modeling}
 \label{app:B}

### 2013-10-11 paper2.tex
small changes

@@
   top right panel shows the RLF obtained by applying the observed
-  $L_{1.4~\rmn{GHz}}-L_{\rmn{X,bol}}$ relation {\bf (see Fig.~\ref{fig:PLSZ})}
-  to the MultiDark clusters at $z = 0.2$, using our phenomenological gas model
-  for $L_{\rmn{X,bol}}$ of each cluster; again for different percentages of
-  radio-loud clusters.  The bottom left panel shows the RLF obtained by applying
-  the observed $L_{1.4~\rmn{GHz}}-Y_{\rmn{SZ}, 500}$ relation {\bf (see
-    Fig.~\ref{fig:PLSZ})} to the MultiDark clusters at $z = 0.2$, using
-  $Y_{\rmn{SZ}, 500}$ of our our phenomenological gas model for each
-  cluster. The bottom right panel shows the comparison between the three
-  approaches for 10 per cent of radio-loud clusters. In all panels, we show the
-  NVSS survey RLF \citep{1999NewA....4..141G} with a median redshift of
-  $z\approx 0.18$, corrected for the sample incompleteness and survey sky
-  coverage.  Horizontal error bars represent the mass bins while the vertical
-  error bars are Poissonian uncertainties. The light gray line marked by the
-  arrow estimates the incompleteness limit owing to the adopted low-mass cut (in
-  the construction of the mock cluster catalog, see Paper~I) and the scatter in
-  the halo luminosities.}
+  $L_{1.4~\rmn{GHz}}-L_{\rmn{X,bol}}$ relation {\bf (see left panel of
+    Fig.~\ref{fig:PLSZ})} to the MultiDark clusters at $z = 0.2$, using our
+  phenomenological gas model for $L_{\rmn{X,bol}}$ of each cluster; again for
+  different percentages of radio-loud clusters.  The bottom left panel shows the
+  RLF obtained by applying the observed $L_{1.4~\rmn{GHz}}-Y_{\rmn{SZ}, 500}$
+  relation {\bf (see right panel of Fig.~\ref{fig:PLSZ})} to the MultiDark
+  clusters at $z = 0.2$, using $Y_{\rmn{SZ}, 500}$ of our our phenomenological
+  gas model for each cluster. The bottom right panel shows the comparison
+  between the three approaches for 10 per cent of radio-loud clusters. In all
+  panels, we show the NVSS survey RLF \citep{1999NewA....4..141G} with a median
+  redshift of $z\approx 0.18$, corrected for the sample incompleteness and
+  survey sky coverage.  Horizontal error bars represent the mass bins while the
+  vertical error bars are Poissonian uncertainties. The light gray line marked
+  by the arrow estimates the incompleteness limit owing to the adopted low-mass
+  cut (in the construction of the mock cluster catalog, see Paper~I) and the
+  scatter in the halo luminosities.}
 \label{fig:RLF_1.4}
